### 2021-06-21 PAPER_2/PAPER_2_REV1.tex
Add files via upload

\documentclass[review]{elsarticle}
\usepackage[utf8]{inputenc} 
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Low load investigation of a 620MWe power boiler using fast Eulerian-Eulerian CFD model}

%% Group authors per affiliation:
\author{B.T. Rawlins}
\author{R. Laubscher\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{ryno.laubscher@uct.ac.za}
\author{P. Rousseau}
\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
CFD\sep Eulerian-Eulerian\sep Boiler \sep Low-load operation
\end{keyword}

\end{frontmatter}

\linenumbers

\begin{center}
\begin{tabular}{ |llllll| } 
 \hline
\multicolumn{3}{|c}{\textbf{Nomenclature}} & & &\\
& & & & & \\
\textit{Symbol} & \textit{Quantity} & \textit{Unit} & & &\\
A &  Area & $m^2$ & g & Gravity & $m/s^2$\\
 \hline
\end{tabular}
\end{center}

\section{Introduction}

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript. Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal. It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.

\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class. In addition, it features commands and options to format the
\begin{itemize}
\item document style
\item baselineskip
\item front matter
\item keywords and MSC codes
\item theorems, definitions and proofs
\item lables of enumerations
\item citation style and labeling.
\end{itemize}

\section{Mathematical model}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}[(1)]
\item Group the authors per affiliation.
\item Use footnotes to indicate the affiliations.
\end{enumerate}
See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.

\section{Numerical setup}

\subsection{Model validation}

\section{Results \& discussion}

\section{Conclusions}

\section{Bibliography styles}

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2021-08-30 PAPER_2/PAPER_2_REV1.tex
Update - 30/08/2021

@@
 \usepackage{lineno,hyperref}
+\usepackage{tabu}
+\usepackage{tabularx}
+\usepackage{subfigure}
 \modulolinenumbers[5]
@@
 
-\title{Low load investigation of a 620MWe power boiler using fast Eulerian-Eulerian CFD model}
+\title{Low load operating protocol investigation of a 620MWe power boiler using a fast Eulerian-Eulerian CFD model}
 
@@
 \begin{abstract}
+
 This template helps you to create a properly formatted \LaTeX\ manuscript.
+Low load operation of utility boiler
+
 \end{abstract}
@@
 \begin{center}
-\begin{tabular}{ |llllll| } 
+\begin{tabular}{|p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}|} 
  \hline
@@
 & & & & & \\
-\textit{Symbol} & \textit{Quantity} & \textit{Unit} & & &\\
+& &  & \multicolumn{3}{l|}{\textit{Greek letters}}\\
+\textit{Symbol} & \textit{Quantity} & \textit{Unit} & $\alpha_p$ & Particle absorption coefficient &$m^{-1}$\\
 A &  Area & $m^2$ & g & Gravity  & $m/s^2$\\
@@
 
-\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.
+If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.
 
@@
 
+\begin{table}[h!]
+\centering
+\caption{Utility boiler fuel characteristics}
+\vspace{5mm}
+\label{fuel}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
+\hline
+\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
+\hline
+\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
+Carbon & $0.7753$ & $kg/kg_{fuel}$\\
+Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
+Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
+Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
+Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
+\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
+Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
+Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
+Ash & $0.4090$ & $kg/kg_{fuel}$\\
+Moisture & $0.0550$ & $kg/kg_{fuel}$\\
+\hline
+\textbf{Energy content - (DAF)} & \textbf{Value} &\\
+\hline
+Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
+\hline
+\end{tabularx}}
+\end{table}
+
+Validation separately mention the rates/loadings - give results for 40\% case inputs
+Low Ultra low load inputs
+
 \subsection{Model validation}
+The validation of the proposed model was conducted for three steady state MCR loads of 100\%, 80\% and 60\%. The  
+\\
+Figures of the Histrograms and CO graphs as in paper
+Data plots and overall performance of the model
+Inputs for the various loads table
+
+\begin{figure}\label{fig_heat_valid}
+	\subfigure[]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
+	\subfigure[]{\includegraphics[width=0.32\textwidth]{80_VALID_BAR}}
+	\subfigure[]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
+\caption{Validation of the experimental and models heat load to the furnace, PSH and HTSH for steady state loads of a) 100\% MCR, b) 80\% MCR and c) 60\% MCR}
+\end{figure}
+
+\begin{figure}\label{fig_comb_valid}
+\centering
+\subfigure[]{\includegraphics[width = 0.45\textwidth]{COPPM_VALID}}
+\subfigure[]{\includegraphics[width = 0.45\textwidth]{XO2_VALID}}
+\caption{Experimentally calculated $CO$ and $O_2$ concentration predictions at a height of 37.5 (m)}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale = 0.5]{TEMP_KEY}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_TEMP}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_TEMP}}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_TEMP}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_TEMP}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
+\caption{Hi}
+\end{figure}
+
+ghff
+\begin{figure}[h!]
+\centering
+\includegraphics[scale = 0.5]{VEL_KEY}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_VEL}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_VEL}}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_VEL}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_VEL}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
+\caption{bye}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale = 0.5]{HEATFLUX_KEY}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_HEATFLUX}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_HEATFLUX}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_HEATFLUX}}\\
+\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_HEATFLUX}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_HEATFLUX}}
+\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_HEATFLUX}}
+\caption{bye}
+\end{figure}
 

### 2021-08-31 PAPER_2/PAPER_2_REV1.tex
Update - 31/08/2021

@@
 	\subfigure[]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
-\caption{Validation of the experimental and models heat load to the furnace, PSH and HTSH for steady state loads of a) 100\% MCR, b) 80\% MCR and c) 60\% MCR}
+\caption{Validation of the experimental and models heat load to the furnace, PSH and HTSH for steady state loads of (a) 100\% MCR, (b) 80\% MCR and (c) 60\% MCR}
 \end{figure}
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.55]{CO_MF_KEY}
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
+\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
+\end{figure}
+
+\clearpage
 \section{Results \& discussion}

### 2021-09-01 PAPER_2/PAPER_2_REV1.tex
Update - 01/09/2021

@@
 
-\section{Numerical setup}
+\section{Numerical modelling setup}
+In this section the numerical model configuration will be explained covering  the boilers geometry,  model inputs (e.g.
+fuel characteristics and boundary conditions) ending with the numerical solution strategy employed.
+
+\subsection{Geometry}
+
+\subsection{Model inputs}
 
@@
 
+\subsection{Numerical solution strategy}
+
 Validation separately mention the rates/loadings - give results for 40\% case inputs
@@
 
+\section{Results \& discussion}
+The current section will discuss the results obtained from using the above-mentioned modelling methodologies.
+The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100\%, 81\% and 60\% MCR loads) to that of the experimentally obtained results of the actual plant.
+Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.
+
 \subsection{Model validation}
-The validation of the proposed model was conducted for three steady state MCR loads of 100\%, 80\% and 60\%. The  
-\\
-Figures of the Histrograms and CO graphs as in paper
-Data plots and overall performance of the model
-Inputs for the various loads table
 
-\begin{figure}\label{fig_heat_valid}
+The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%.
+The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau (REFERENCE), where they used an EL reference frame and DO radiation model.
+
+\begin{figure}[h!]
+\label{fig_heat_valid}
 	\subfigure[]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
@@
 	\subfigure[]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
-\caption{Validation of the experimental and models heat load to the furnace, PSH and HTSH for steady state loads of (a) 100\% MCR, (b) 80\% MCR and (c) 60\% MCR}
+\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and pendant SH at (a) 100\% MCR, (b) 80\% MCR and (c) 60\% MCR}
 \end{figure}
 
-\begin{figure}\label{fig_comb_valid}
+In figure \ref{fig_heat_valid} it is shown that the overall heat loads are in good agreement with the measured results.
+For the simulated validation loads the proposed model results are within the associated error band, the general trend is an under prediction on the furnace heat loads and an over prediction on the platen super-heater.
+The pendant super heater illustrate the best comparable results for all load cases.\\
+
+The CFD model was further validated by comparing the $CO_{ppm}$ and $X_{O_{2}}$ measurements against the CFD results.
+The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during a full load (100\% MCR) operating conditions.
+The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$] increment.\\
+\begin{figure}[h!]\label{fig_probe_valid}
 \centering
-\subfigure[]{\includegraphics[width = 0.45\textwidth]{COPPM_VALID}}
-\subfigure[]{\includegraphics[width = 0.45\textwidth]{XO2_VALID}}
-\caption{Experimentally calculated $CO$ and $O_2$ concentration predictions at a height of 37.5 (m)}
+\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{COPPM_VALID}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
+\caption{Experimentally calculated $CO$ and $O_2$ concentration predictions}
 \end{figure}
 
+Figure \ref{fig_probe_valid} shows the averaged measurement values to that of the CFD predictions.
+It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
+For further information regarding the validation of the model the interested reader is directed to the works of Rawlins et al [REFERENCE]
+
+\subsection{Simulation results for various burner firing arrangements at 32\% MCR }
+
+Explain the investigation
+table with case descriptions
+Need flownex model and process modelling description
 \begin{figure}
 \centering
-\includegraphics[scale = 0.5]{TEMP_KEY}\\
+\includegraphics[scale = 0.5]{TEMP_KEY} [K]\\
 \subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
@@
 
-ghff
 \begin{figure}[h!]
@@
 
+\begin{table}[h!]
+\centering
+\caption{Utility boiler fuel characteristics}
+\vspace{5mm}
+\label{fuel}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\textwidth}{l l l l l l l}
+\hline
+\textbf{Value} & \textbf{Case 1} & \textbf{Case 2} & \textbf{Case 3}& \textbf{Case 4}&\textbf{Case 5}&\textbf{Case 6}\\
+\hline
+\textbf{Platen max temp}\\
+\textbf{Pendant max temp}\\
+\textbf{Main steam flow rate}\\
+\hline
+
+\end{tabularx}}
+\end{table}
+
 \clearpage
-\section{Results \& discussion}
 

### 2021-09-06 PAPER_2/PAPER_2_REV1.tex
Update - 05/09/2021

@@
 \usepackage{tabu}
+\usepackage{float}
 \usepackage{tabularx}
 \usepackage{subfigure}
+\usepackage[fleqn]{amsmath}
 \modulolinenumbers[5]
 
-\journal{Journal of \LaTeX\ Templates}
+\journal{Journal of Applied Thermal Engineering}
 
@@
 
-This template helps you to create a properly formatted \LaTeX\ manuscript.
 Low load operation of utility boiler
@@
 \begin{center}
-\begin{tabular}{|p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}|} 
+\begin{tabular}{|p{0.075\textwidth}p{0.3\textwidth}p{0.05\textwidth}p{0.075\textwidth}p{0.3\textwidth}p{0.05\textwidth}|} 
  \hline
-\multicolumn{3}{|c}{\textbf{Nomenclature}} & &  &\\
-& & & & & \\
-& &  & \multicolumn{3}{l|}{\textit{Greek letters}}\\
-\textit{Symbol} & \textit{Quantity} & \textit{Unit} & $\alpha_p$ & Particle absorption coefficient &$m^{-1}$\\
-A &  Area & $m^2$ & g & Gravity  & $m/s^2$\\
+\multicolumn{3}{|l}{\textbf{Nomenclature}} & &  &\\
+\textit{Symbol} & \textit{Quantity} & \textit{Unit} & & &\\
+$A$ &  Area & $m^2$ & & &\\
+$A_p$ & Particle surface area & $m^2$& & & \\
+$d_p$&Particle diameter & $m$ & & & \\
+$E$& Fluid total energy&$J/kg$ & & & \\
+$E_a$& Reaction activation energy&$J/kmol$ & & & \\
+$P$& Pressure & $Pa$ & & & \\
+$T_g$& Gas temperature& $K$ & & & \\
+$T_p$&Particle temperature & $K$& & & \\
+$u$& Velocity &$m/s^2$ & & &\\
 \hline
@@
 
-If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.
+\section{Mathematical model}
+In this section the modelling techniques used by the study are elaborated.
+A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport resolution.
+Following this is a description of the adopted heat transfer modelling techniques and the ends with a description of the process modelling configuration.
+\subsection{Computational fluid dynamics modelling}
 
-\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript.
-Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal.
-It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.
+\subsubsection{Fluid flow, turbulence and combustion modelling}
+The flue gas was modelled using a Eulerian framework.
+The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase.
+This approach solves a species continuity equation for each constituent present in the mixture.
+To reduce the computational burden it was assumed that the various processes were in steady-state.To correctly account for the particle inertial effects on the gas phase convection an effective density is defined as follows;
+\begin{equation} \label{eqn_eff_rho}
+	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
+\end{equation}
 
-\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class.
-In addition, it features commands and options to format the
-\begin{itemize}
-\item document style
-\item baselineskip
-\item front matter
-\item keywords and MSC codes
-\item theorems, definitions and proofs
-\item lables of enumerations
-\item citation style and labeling.
-\end{itemize}
+In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem.
+This model has been successfully used by researchers [REFERECENCES], in modelling the effects of coal-fired swirl burners.
+The model generally generates higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.
 
-\section{Mathematical model}
+The process of coal combustion comprises four steps.
+Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions.
+Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
+\begin{gather}
+\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
+\begin{split}
+&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
+&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
+\end{split}
+\end{gather}
 
-The author names and affiliations could be formatted in two ways:
-\begin{enumerate}[(1)]
-\item Group the authors per affiliation.
-\item Use footnotes to indicate the affiliations.
-\end{enumerate}
-See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.
+A devolatilization temperature of 553 [$K$] (REFERENCE) along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al (REFERENCE) were utilized.
+The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street (REFERENCE), which is given in equation (\ref{eqn_char_rate}).
+The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}).
+\begin{gather}
+\frac{dm_{char}}{dt} = -A_p P_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
+C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
+\end{gather}
+The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al (REFERENCE).
+\begin{gather}
+R_{diff} = \frac{5X10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^0.75 \label{eqn_char_diff_rate}\\
+\begin{split}
+&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
+&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
+\end{split}
+ \label{eqn_char_kin_rate}
+\end{gather}
 
-\section{Numerical modelling setup}
-In this section the numerical model configuration will be explained covering  the boilers geometry,  model inputs (e.g.
-fuel characteristics and boundary conditions) ending with the numerical solution strategy employed.
+The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate, and uses the minimum of the three for the source terms calculations.
+A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau (REFERENCE).
 
-\subsection{Geometry}
+\subsubsection{Particle modelling}
+The pseudo particles transported into the domain are modelled using the general scalar field transport equation (REFERENCE).
+The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash.
+Each of the scalar field equations are given in table \ref{tab_scalars}.
+
+\begin{table}[h!]
+\centering
+\caption{Scalar field equation descriptions}\label{tab_scalars}       
+\begin{tabular}{lll}
+\hline
+Variable &Description& Transport equation \\
+\hline
+$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
+$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
+$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
+$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
+$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
+$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
+\hline
+\end{tabular}
+\end{table}
+
+The energy transport of the pseudo particle, is transported by defining the particle enthalpy using the following equation:
+\begin{equation}\label{eqn_phi_hp}
+\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dM_{evap}}{dt}h_{fg}\right)\frac{1}{V}
+\end{equation}
+
+The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dM_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn}\right)$.
+This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{epple}, \cite{knaus}).
+The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
+
+\subsection{Heat transfer modelling modelling}
+The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces (REFERENCE) and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) (REFERENCE) shown in equation ().
+\begin{equation}
+\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_SB T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\end{equation}
+In the present work the RTE is solved sing the P1 model.
+Ranade and Gupta (REFERENCE) illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 MWe CFPP boiler.
+The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$).
+The P1 model transport variable is the incident radiation (G - [$W/m^2$]), and can be written for a particle laden domain as:
+\begin{equation}
+\begin{split}
+&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
+&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
+\end{split}
+\end{equation}
+
+The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al (REFERENCE).
+The WSGGM accounts for the radiation emitted by tri-atomic gases, namely $CO_2$, $H_2O$ and $SO_2$ present in the flue gas stream.
+The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p$) present in a cell.
+There formulations are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
+\begin{gather}
+\alpha_p = \frac{\epsilon_p A_{pn}N_p}{V} \label{eqn_part_abs}\\
+\sigma_p = \frac{(1-\epsilon_p)(1-f_p) A_{pn}N_p}{V} \label{eqn_part_scat} \\
+E_p = \frac{\epsilon_p \sigma_{SB} T_p^4 A_{pn}N_p}{V}\label{eqn_part_emisp}
+\end{gather}
+
+It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) are used, that are based on the correlations of LOCKWOOD AND YIN.
+
+\subsection{Process simulation model}
+A 1D discretized model of the furnace evaporator, platen SH, pendant SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021.
+The model simulates the internal convection heat transfer inside the tubes, the conduction through the tube walls.
+The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit.
+The heat exchangers were modelled using a two-phase mixture approach, this assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area.
+The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
+\begin{gather}
+\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
+\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
+\end{gather}
+Applying the mixture density the following transport equations are solved;
+
+\begin{equation}\label{eqn_mix_conti}
+\frac{\partial}{\partial t}(\rho_M A)+\frac{\partial}{\partial s}(\rho_MAu) = 0
+\end{equation}
+\begin{equation}\label{eqn_mix_mom}
+\frac{1}{A} \frac{\partial}{\partial t}(\rho_M A u)+\frac{1}{A} \frac{\partial}{\partial s}(\rho_M A u^2) = -\frac{\partial p}{\partial s}-\frac{\tau_W P}{A}- \rho_M g \frac{\partial z}{\partial s}
+\end{equation}
+\begin{equation}\label{eqn_mix_energy}
+\begin{split}
+&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\\&\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
+\end{split}
+\end{equation}
+
+The interface between the process and CFD simulation are the furnace, platen and pendant SH external walls, which similar to the study conducted by Laubscher and Rousseau (REFERENCE).
+However, for this study the downstream heat exchangers are included in the process model and there is an indirect coupling between the models.
+
+The process model is primarily used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
+The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various cases have on the system.
+
+\section{Case study boiler description \& set-up}
+In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry and process model set-up,  modelling inputs (e.g.
+fuel characteristics and boundary conditions) and ends with the numerical solution strategy.
+\newpage
+\subsection{Geometry \& process model set-up}
+
+The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], a width of 14.01 [$m$] and a height of 64 [$m$].
+The CFD geometric model makes use of a symmetry plane  at half the width of the furnace.
+This was done to reduce the cell count of the numerical mesh.
+Both the platen and pendant super heaters (SH) are modelled as walls, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively.
+There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$].
+Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, pendant SH, boundary walls (front, rear and side) and the domains outlet and inlets.
+A single burner is also highlighted in figure \ref{fig_geometry} indicating the primary air (PA) and secondary air (SA) inlets.
+\\
+\begin{figure} [h!]
+\centering
+\includegraphics[scale=0.5]{GEOMETRY}
+\caption{Boiler geometry and layout}
+\label{fig_geometry}
+\end{figure}
+
+The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and PA mixture to a burner row consisting of 6 burners.
+This mixture is injected through the inner burner annulus while the SA is fed through the outer annulus as seen figure \ref{fig_geometry}.
+The operating protocol of the case study boiler requires that burners which are not firing (F) to inject SA air at a rate of 5 [$kg/s$], this is to maintain non-firing (NF) burner integrity.
+
+Subsequently a process model of the boiler configuration is shown in figure \ref{fig_flownex}.
+The process model includes all the heat exchanging components up till and downstream of the pendant SH, which include the secondary reheater (RH), primary SH, primary RH, economiser and the SA air heaters.
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.5]{FLOWNEX_SETUP}
+\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
+\label{fig_flownex}
+\end{figure}
 
@@
 
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).
 \begin{table}[h!]
@@
 \vspace{5mm}
-\label{fuel}
+\label{tbl_fuel}
 {\tabulinesep=1.2mm
@@
 
+For a 32\% MCR load case the following three burner firing configurations were used:
+\begin{enumerate}
+\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
+\item Middle front and rear row burners are fired (Case 2 \& Case 5)
+\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
+\end{enumerate}
+
+Two permutations of the SA flow rate, at the non-firing burners, for each of the firing configurations mentioned above brings the total amount of simulations to six.
+Table \ref{tbl_case_inputs} shows the input conditions for cases 1 to 6.
+The data is the result of a boilers mass and energy balance calculations.
+
+\begin{table}[h!]
+\centering
+\caption{Case 1 to 6 model inputs on a per burner basis.}
+\label{tbl_case_inputs}
+\vspace{5mm}
+\label{fuel}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.25\textwidth} l}
+\hline
+Active burners & \textbf{Cases 1 - 3} & \textbf{Cases 4 - 6}\\
+\hline
+\textbf{Fuel flow rate} [$kg/s$]&1.05  &1.05\\
+\textbf{PA flow rate} [$kg/s$]&4.95  &4.95\\
+\textbf{SA flow rate} [$kg/s$]&14.85  &14.85\\
+\hline
+Non firing burners &  & \\
+\hline
+\textbf{SA flow rate} [$kg/s$]&5  &2.5\\
+\hline
+Input air temperatures& &\\
+\hline
+\textbf{PA} [$K$]&373  &373\\
+\textbf{SA} [$K$]&520  &510\\
+\hline
+\end{tabularx}}
+\end{table}
+
 \subsection{Numerical solution strategy}
 
-Validation separately mention the rates/loadings - give results for 40\% case inputs
-Low Ultra low load inputs
+The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
+the pressure-momentum coupling utilised the SIMPLE technique.
+Second-order upwinding was used to discretize the momentum, energy and species equations, whereas PRESTO!
+was used to discretize the pressure equation.
+The scalar field equations used a second-order upwind scheme.
+
+The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
+For all cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
+The remaining fields were solved till convergence.
 
@@
 The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%.
-The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau (REFERENCE), where they used an EL reference frame and DO radiation model.
+The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau (REFERENCE), where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
 
 \begin{figure}[h!]
-\label{fig_heat_valid}
 	\subfigure[]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
@@
 \caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and pendant SH at (a) 100\% MCR, (b) 80\% MCR and (c) 60\% MCR}
+\label{fig_heat_valid}
 \end{figure}
@@
 The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$] increment.\\
-\begin{figure}[h!]\label{fig_probe_valid}
+\begin{figure}[h!]
 \centering
@@
 \caption{Experimentally calculated $CO$ and $O_2$ concentration predictions}
+\label{fig_probe_valid}
 \end{figure}
@@
 \centering
-\includegraphics[scale = 0.5]{TEMP_KEY} [K]\\
+\includegraphics[scale = 0.45]{TEMP_KEY} [$K$]\\
 \subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
@@
 \centering
-\includegraphics[scale = 0.5]{VEL_KEY}\\
+\includegraphics[scale = 0.45]{VEL_KEY} [$m/s$]\\
 \subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
@@
 \centering
-\includegraphics[scale = 0.5]{HEATFLUX_KEY}\\
+\includegraphics[scale = 0.45]{HEATFLUX_KEY} [$W/m^2$]\\
 \subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_HEATFLUX}}
@@
 \centering
-\includegraphics[scale=0.55]{CO_MF_KEY}
+\includegraphics[scale=0.45]{CO_MF_KEY} [$Y_{CO}$] \\
 \subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.5]{PROBE_LOCATIONS}
+\caption{Probe location}
+\label{fig_probe_loc}
+\end{figure}
+
 \begin{table}[h!]
@@
 \caption{Utility boiler fuel characteristics}
-\vspace{5mm}
 \label{fuel}
 {\tabulinesep=1.2mm
-\begin{tabularx}{\textwidth}{l l l l l l l}
+\begin{tabularx}{\linewidth}{p{0.35\linewidth} XXXXXX}
 \hline
-\textbf{Value} & \textbf{Case 1} & \textbf{Case 2} & \textbf{Case 3}& \textbf{Case 4}&\textbf{Case 5}&\textbf{Case 6}\\
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
 \hline
-\textbf{Platen max temp}\\
-\textbf{Pendant max temp}\\
-\textbf{Main steam flow rate}\\
+\textbf{Main steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
+\textbf{Main steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
+\textbf{RH steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
+\textbf{RH steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
+\textbf{Boiler efficiency} [$\%$]&162&172&182&164&174&184\\
+\textbf{Attemperator 1} [$kg/s$]&162&172&182&164&174&184\\
+\textbf{Attemperator 2} [$kg/s$]&162&172&182&164&174&184\\
+\textbf{Attemperator RH} [$kg/s$]&162&172&182&164&174&184\\
+\textbf{Platen wall temp (mean,min,max)} [$^{\circ}C$] &162&172&182&164&174&184 \\
+\textbf{Pendant wall temp (mean,min,max)} [$^{\circ}C$]&162&172&182&164&174&184  \\
 \hline
-
 \end{tabularx}}
@@
 \clearpage
-
 \section{Conclusions}
 
-\section{Bibliography styles}
-
-There are various bibliography styles available.
-You can select the style of your choice in the preamble of this document.
-These styles are Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.
-
-Here are two sample references: \cite{Feynman1963118,Dirac1953888}.
+\section*{Acknowledgements}
+The authors would like to thank the Eskom EPPEI program for financially supporting the present study and acknowledge the computational resources provided by the Centre for High Performance Computing (CHPC), South Africa.
 

### 2021-09-06 PAPER_2/PAPER_2_REV1.tex
Update - 06/09/2021

@@
 \section{Introduction}
+In the beginning the giant penguins of south east asia used to hunt the great walri of svenborg.
 
@@
 
+\begin{figure}[h!]
+\centering
+\subfigure[]{\includegraphics[scale = 0.36]{SYMMETRY_PROBE_COPPM}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.36]{OFFSET_PROBE_COPPM}}\\
+\subfigure[]{\includegraphics[scale = 0.35]{SYMMETRY_PROBE_XO2}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}
+
+\caption{bye}
+\end{figure}
+
 \begin{table}[h!]
 \centering
-\caption{Utility boiler fuel characteristics}
+\caption{Process model control parameters}
 \label{fuel}
 {\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.35\linewidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
 \hline
@@
 \hline
-\textbf{Main steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
-\textbf{Main steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
-\textbf{RH steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
-\textbf{RH steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
-\textbf{Boiler efficiency} [$\%$]&162&172&182&164&174&184\\
-\textbf{Attemperator 1} [$kg/s$]&162&172&182&164&174&184\\
-\textbf{Attemperator 2} [$kg/s$]&162&172&182&164&174&184\\
-\textbf{Attemperator RH} [$kg/s$]&162&172&182&164&174&184\\
-\textbf{Platen wall temp (mean,min,max)} [$^{\circ}C$] &162&172&182&164&174&184 \\
-\textbf{Pendant wall temp (mean,min,max)} [$^{\circ}C$]&162&172&182&164&174&184  \\
+\textbf{Main steam flow rate} 	[$kg/s$]		&166&163&170	&171&169&163\\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&535&535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&150&148&154	&154&153&147\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&520&490\\
+\textbf{Boiler efficiency} 		[$\%$]			&86.2&84.9&88.8	&88.2&86.6&82.2\\
+\textbf{Attemperator 1} 		[$kg/s$]			&10.5&15&16		&11.5&9.5&12\\
+\textbf{Attemperator 2} 		[$kg/s$]			&5&8&5			&4&5&5.5\\
+\textbf{Attemperator RH} 		[$kg/s$]			&0.5&1&1		&0&0&0\\
+\hline
+\end{tabularx}}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\caption{Platen and pendant wall temperatures}
+\label{fuel}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\multicolumn{7}{l}{\textit{Platen SH}}\\
+\textbf{Max wall temperature} [$K$]  &754 & 750 & 765 & 766 & 753 & 763\\
+\textbf{Mean wall temperature} [$K$] &726 & 712 & 719 & 727 & 715 & 724\\
+\multicolumn{7}{l}{\textit{Pendant SH}}\\
+\textbf{Max wall temperature} [$K$]  & 805 & 807 & 811 & 808 & 800 & 802\\
+\textbf{Mean wall temperature} [$K$] & 793 & 786 & 792 & 795 & 788 & 784\\
+\hline
+\end{tabularx}}
+\end{table}
+
+\begin{equation}
+T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
+\end{equation}
+
+\begin{table}[h!]
+\centering
+\caption{Radiative heat transfer percentage for the platen and pendant SH}
+\label{fuel}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\linewidth}{p{0.25\linewidth} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+Platen SH [\%] & 91.6 & 94.1 & 92.5 & 92.6 & 93.9 & 93.4\\
+Pendant SH [\%] & 92.8 & 92.7 & 93.5 & 93.4 & 92.7 & 94.1\\
 \hline

### 2021-09-07 PAPER_2/PAPER_2_REV1.tex
Update - 07/09/2021

@@
 
-A devolatilization temperature of 553 [$K$] (REFERENCE) along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al (REFERENCE) were utilized.
-The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street (REFERENCE), which is given in equation (\ref{eqn_char_rate}).
+A devolatilization temperature of 553 [$K$] (REFERENCE) along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized.
+The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street (\cite{Baum1971}), which is given in equation (\ref{eqn_char_rate}).
 The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}).
@@
 The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate, and uses the minimum of the three for the source terms calculations.
-A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau (REFERENCE).
+A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
 
 \subsubsection{Particle modelling}
-The pseudo particles transported into the domain are modelled using the general scalar field transport equation (REFERENCE).
+The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash.
@@
 The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dM_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn}\right)$.
-This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{epple}, \cite{knaus}).
+This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003}, \cite{Cai2015}).
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
@@
 \subsection{Heat transfer modelling modelling}
-The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces (REFERENCE) and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) (REFERENCE) shown in equation ().
-\begin{equation}
+The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
+\begin{equation}\label{eqn_RTE}
 \frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_SB T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
@@
 In the present work the RTE is solved sing the P1 model.
-Ranade and Gupta (REFERENCE) illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 MWe CFPP boiler.
+Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 MWe CFPP boiler.
 The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$).
@@
 
-The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al (REFERENCE).
+The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al \cite{Smith1982}.
 The WSGGM accounts for the radiation emitted by tri-atomic gases, namely $CO_2$, $H_2O$ and $SO_2$ present in the flue gas stream.
@@
 
-The interface between the process and CFD simulation are the furnace, platen and pendant SH external walls, which similar to the study conducted by Laubscher and Rousseau (REFERENCE).
+The interface between the process and CFD simulation are the furnace, platen and pendant SH external walls, which is similar to the study conducted by Laubscher and Rousseau (REFERENCE).
 However, for this study the downstream heat exchangers are included in the process model and there is an indirect coupling between the models.
@@
 The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%.
-The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau (REFERENCE), where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
+The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
 
@@
 \subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
-\caption{Hi}
+\caption{Temperature fields for cases 1 through 6}
 \end{figure}
@@
 \subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
-\caption{bye}
+\caption{Velocity fields for cases 1 through 6}
 \end{figure}
@@
 \includegraphics[scale = 0.45]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_HEATFLUX}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_HEATFLUX}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_HEATFLUX}}\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_HEATFLUX}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_HEATFLUX}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_HEATFLUX}}
-\caption{bye}
+\subfigure[]{\includegraphics[scale = 0.29]{BOT_HEATFLUX}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.35]{MID_HEATFLUX}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.35]{FBRM_HEATFLUX}}\\
+\subfigure[]{\includegraphics[scale = 0.35]{BOT05_HEATFLUX}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.35]{MID05_HEATFLUX}}
+\hspace{5mm}
+\subfigure[]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
+\caption{Heat fluxes profiles for cases 1 through 6}
 \end{figure}
@@
 				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
+\caption{CO mass fraction ($Y_{CO}$) concentrations for cases 1 through 6 on a temperature iso-surface of 1600 K}
 \end{figure}
@@
 
-\caption{bye}
+\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
 \end{figure}
@@
 \centering
-\caption{Platen and pendant wall temperatures}
+\caption{Furnace exit conditions and SH wall temperatures}
 \label{fuel}
 {\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{0.4\linewidth} XXXXXX}
 \hline
@@
 \hline
+\multicolumn{7}{l}{\textit{Furnace exit}}\\
+\textbf{Exit temperature} [$K$] & 1168 & 1230 & 1215 & 1208 & 1306 & 1298\\
+\textbf{Unburnt carbon} [$(\times 10^{-3})\,\%$] & 1.83 & 1.94 & 1.54 & 1.81 & 1.89 & 1.62\\
 \multicolumn{7}{l}{\textit{Platen SH}}\\
@@
 
-\bibliography{mybibfile}
+\bibliography{PAPER1_LOW_LOAD}
 

### 2021-09-22 PAPER_2/PAPER_2_REV1.tex
Update - 15/09/2021 1#
update - 22/09/2021

@@
 \section{Introduction}
-In the beginning the giant penguins of south east asia used to hunt the great walri of svenborg.
+
+The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement.
+Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient supply of attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.
+
+The model was developed for a 32 $\%$ boiler load with 6 various firing combinations.
+To establish accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ boiler loads and compared to plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid}.
 
@@
 In this section the modelling techniques used by the study are elaborated.
-A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport resolution.
+A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution.
 Following this is a description of the adopted heat transfer modelling techniques and the ends with a description of the process modelling configuration.
@@
 In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem.
-This model has been successfully used by researchers [REFERECENCES], in modelling the effects of coal-fired swirl burners.
+This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners.
 The model generally generates higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.
@@
 
-A devolatilization temperature of 553 [$K$] (REFERENCE) along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized.
+A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized.
 The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street (\cite{Baum1971}), which is given in equation (\ref{eqn_char_rate}).
@@
 \end{gather}
-The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al (REFERENCE).
+The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
 \begin{gather}
@@
 \subsubsection{Particle modelling}
-The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
+The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a multi-phase Eulerian-Eulerain (EE) model the characteristics of coal combustion and furnace heat transfer with adequate accuracy.The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash.
@@
 The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dM_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn}\right)$.
-This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003}, \cite{Cai2015}).
+This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
@@
 
-It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) are used, that are based on the correlations of LOCKWOOD AND YIN.
+It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) are used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \citep{Yin2015} respectively.
 
 \subsection{Process simulation model}
-A 1D discretized model of the furnace evaporator, platen SH, pendant SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021.
+A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021.
 The model simulates the internal convection heat transfer inside the tubes, the conduction through the tube walls.
@@
 
-The interface between the process and CFD simulation are the furnace, platen and pendant SH external walls, which is similar to the study conducted by Laubscher and Rousseau (REFERENCE).
-However, for this study the downstream heat exchangers are included in the process model and there is an indirect coupling between the models.
+The CFD heat load results for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}.
 
-The process model is primarily used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
+The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
 The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various cases have on the system.
@@
 \section{Case study boiler description \& set-up}
-In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry and process model set-up,  modelling inputs (e.g.
+In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry, the process model set-up, the various  modelling inputs (e.g.
 fuel characteristics and boundary conditions) and ends with the numerical solution strategy.
@@
 \subsection{Geometry \& process model set-up}
-
 The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], a width of 14.01 [$m$] and a height of 64 [$m$].
-The CFD geometric model makes use of a symmetry plane  at half the width of the furnace.
+The CFD geometric model (of Figure \ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace.
 This was done to reduce the cell count of the numerical mesh.
-Both the platen and pendant super heaters (SH) are modelled as walls, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively.
+Both the platen and final SH are modelled as walls, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively.
 There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$].
-Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, pendant SH, boundary walls (front, rear and side) and the domains outlet and inlets.
-A single burner is also highlighted in figure \ref{fig_geometry} indicating the primary air (PA) and secondary air (SA) inlets.
-\\
+Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domains outlet and inlets.\\
 \begin{figure} [h!]
 \centering
-\includegraphics[scale=0.5]{GEOMETRY}
+\includegraphics[scale=0.4]{GEOMETRY}
 \caption{Boiler geometry and layout}
@@
 
-The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and PA mixture to a burner row consisting of 6 burners.
-This mixture is injected through the inner burner annulus while the SA is fed through the outer annulus as seen figure \ref{fig_geometry}.
-The operating protocol of the case study boiler requires that burners which are not firing (F) to inject SA air at a rate of 5 [$kg/s$], this is to maintain non-firing (NF) burner integrity.
+The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners.
+This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen figure \ref{fig_geometry}.
 
-Subsequently a process model of the boiler configuration is shown in figure \ref{fig_flownex}.
-The process model includes all the heat exchanging components up till and downstream of the pendant SH, which include the secondary reheater (RH), primary SH, primary RH, economiser and the SA air heaters.
+The process model of the boiler configuration is shown in Figure \ref{fig_flownex}.
+The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
 \begin{figure}[h!]
@@
 \subsection{Model inputs}
-
-Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).\\
 \begin{table}[h!]
@@
 
-For a 32\% MCR load case the following three burner firing configurations were used:
+For a 32\% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand.
+For this study six cases are simulated in total with the following three burner firing configurations being utilized:
 \begin{enumerate}
@@
 
-Two permutations of the SA flow rate, at the non-firing burners, for each of the firing configurations mentioned above brings the total amount of simulations to six.
+Two permutations of the SA flow rate, at the non-firing burners, are used for each of the firing configurations mentioned above.
 Table \ref{tbl_case_inputs} shows the input conditions for cases 1 to 6.
@@
 
+Table \ref{tbl_case_inputs} shows a lower mass flow rate of SA air for case 4 to 6, this was done to compare the expected increase in boiler utilization efficiency, since less dry gas losses are expected, and the effects the drop in the flue-gas mass flow rate has on the convective pass components modelled in the process model.
+
 \subsection{Numerical solution strategy}
@@
 
+The operating protocol of the case study boiler requires that burners which are not firing to inject SA air at a rate of 5 [$kg/s$], this is to maintain non-firing burner integrity.
+
 \section{Results \& discussion}
@@
 
-\subsection{Model validation}
+\subsection{Model validation}\label{sec_model_valid}
 
@@
 \subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
-\caption{Temperature fields for cases 1 through 6}
+\caption{Temperature fields for cases 1 through 6 [(a)-(f)]}
 \end{figure}
@@
 \subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
-\caption{Velocity fields for cases 1 through 6}
+\caption{Velocity fields for cases 1 through 6 [(a)-(f)]}
 \end{figure}
@@
 \subfigure[]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
-\caption{Heat fluxes profiles for cases 1 through 6}
+\caption{Heat fluxes profiles for cases 1 through 6 [(a)-(f)]}
 \end{figure}
@@
 				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
-\caption{CO mass fraction ($Y_{CO}$) concentrations for cases 1 through 6 on a temperature iso-surface of 1600 K}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.5]{PROBE_LOCATIONS}
-\caption{Probe location}
-\label{fig_probe_loc}
+\caption{CO mass fraction ($Y_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
 \end{figure}
@@
 \textbf{Max wall temperature} [$K$]  & 805 & 807 & 811 & 808 & 800 & 802\\
-\textbf{Mean wall temperature} [$K$] & 793 & 786 & 792 & 795 & 788 & 784\\
+\textbf{Mean wall temperature} [$K$] & 793 & 788 & 792 & 795 & 788 & 784\\
 \hline
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.25\linewidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{0.25\linewidth} XX}
 \hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+&\multicolumn{2}{c}{Cases}\\
+ &\textbf{3}&\textbf{6}\\
 \hline
-Platen SH [\%] & 91.6 & 94.1 & 92.5 & 92.6 & 93.9 & 93.4\\
-Pendant SH [\%] & 92.8 & 92.7 & 93.5 & 93.4 & 92.7 & 94.1\\
+Evaporator \\
+Platen SH [\%] & \\
+Pendant SH [\%] &\\
+Secondary RH [\%]\\
+Primary SH [\%]\\
+Primary RH [\%]\\
+Economiser [\%]\\
 \hline

### 2021-09-23 PAPER_2/PAPER_2_REV1.tex
update-23/09.2021

@@
 
-\title{Low load operating protocol investigation of a 620MWe power boiler using a fast Eulerian-Eulerian CFD model}
+\title{Low load operating protocol investigation of a 620MWe power boiler using an indirectly coupled process model}
 
@@
 \section{Introduction}
+The use of coal fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change.
+However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
+Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 $\%$ of the energy needs being met using CFPPs \cite{eskom}.
+The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol.
+This will inherently mean CFPPs will need to operate at low-loads for continuous time periods.
 
-The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement.
+Mathematical models that can accurately capture the behaviour of the boilers thermal-hydraulic response at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}.
+Since, the long term deviation from design conditions can lead to operational incapabilities affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.
+
+The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumnavigating the use of time-consuming and costly field tests.
+CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).
+
+Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}.
+The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boiler considerably affect the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.
+
+Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 $\%$.
+The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances.
+Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler.
+A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions.
+However, to the best the authors' knowledge, no integration of 1-D thermal-hydraulic model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.
+
+The use of a 1-D thermal-hydraulic modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions.
+These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}.
+Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D thermal-hydraulic models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.
+
+The use of coupled simulations has proven to solve the deficiencies of a full 1-D thermal-hydraulic model by coupling the fireside CFD to a 1-D water network.
+Recently Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}.
+Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.
+
+The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler.
 Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient supply of attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.
 
-The model was developed for a 32 $\%$ boiler load with 6 various firing combinations.
-To establish accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ boiler loads and compared to plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid}.
+The model was simulated for a 32 $\%$ boiler load with 6 various firing combinations.
+To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ boiler loads and compared to plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.
 
@@
 \subsection{Computational fluid dynamics modelling}
-
 \subsubsection{Fluid flow, turbulence and combustion modelling}
@@
 This approach solves a species continuity equation for each constituent present in the mixture.
-To reduce the computational burden it was assumed that the various processes were in steady-state.To correctly account for the particle inertial effects on the gas phase convection an effective density is defined as follows;
+To reduce the computational burden it was assumed that the various processes were in steady-state.
+The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
+Mass conservation:
+\begin{equation}\label{eqn_RANS_mass}
+\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
+\end{equation}
+Momentum conservation:
+\\
+\begin{equation}\label{eqn_momentum}
+\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{P}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
+\end{equation}\\
+\\
+Energy conservation:
+\begin{equation}\label{eqn_energy}
+\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+P])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
+\end{equation}
+\\
+Species transport:
+\begin{equation}\label{eqn_species}
+\begin{split}
+&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
+&k = 1,2,3...N
+\end{split}
+\end{equation}
+
+To correctly account for the particle inertial effects on the gas phase convection an effective density is defined as follows;
 \begin{equation} \label{eqn_eff_rho}

### 2021-09-24 PAPER_2/PAPER_2_REV1.tex
Update - 24/09/2021

@@
 The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler.
-Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient supply of attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.
+Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.
 
-The model was simulated for a 32 $\%$ boiler load with 6 various firing combinations.
+The model was simulated for a boiler load of 32 $\%$  with 6 various firing combinations.
 To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ boiler loads and compared to plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.
@@
 A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution.
-Following this is a description of the adopted heat transfer modelling techniques and the ends with a description of the process modelling configuration.
+Following this is a description of the heat transfer modelling techniques and the ends with a description of the process modelling configuration.
 \subsection{Computational fluid dynamics modelling}
@@
 A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized.
-The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street (\cite{Baum1971}), which is given in equation (\ref{eqn_char_rate}).
+The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}).
 The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}).
@@
 \subsubsection{Particle modelling}
-The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a multi-phase Eulerian-Eulerain (EE) model the characteristics of coal combustion and furnace heat transfer with adequate accuracy.The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
+The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a multi-phase Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash.
-Each of the scalar field equations are given in table \ref{tab_scalars}.
+Each of the scalar field equations are given in Table \ref{tab_scalars}.
 
@@
 A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021.
-The model simulates the internal convection heat transfer inside the tubes, the conduction through the tube walls.
+The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls.
 The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit.
@@
 
-The CFD heat load results for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}.
-
 The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
@@
 \section{Case study boiler description \& set-up}
-In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry, the process model set-up, the various  modelling inputs (e.g.
+In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry, the process model set-up, the various  modelling inputs (i.e.
 fuel characteristics and boundary conditions) and ends with the numerical solution strategy.
-\newpage
+
 \subsection{Geometry \& process model set-up}
@@
 \begin{figure} [h!]
-\centering
-\includegraphics[scale=0.4]{GEOMETRY}
+\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
 \caption{Boiler geometry and layout}
@@
 The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners.
-This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen figure \ref{fig_geometry}.
+This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.
 
@@
 The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
+The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH) are inlets and outlets.
 \begin{figure}[h!]
@@
 
+The heat load results of the CFD simulation for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}. 
+\newpage
 \subsection{Model inputs}
@@
 
-For a 32\% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand.
+For a 32\% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.
 For this study six cases are simulated in total with the following three burner firing configurations being utilized:
@@
 \hline
-\textbf{Fuel flow rate} [$kg/s$]&1.05  &1.05\\
+\textbf{Fuel flow rate} [$kg/s$]&3.14  &3.14\\
 \textbf{PA flow rate} [$kg/s$]&4.95  &4.95\\
@@
 \hline
-\textbf{SA flow rate} [$kg/s$]&5  &2.5\\
+\textbf{SA flow rate} [$kg/s$]&5.0  &2.5\\
 \hline
@@
 \subsection{Numerical solution strategy} 
-
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
@@
 
-The operating protocol of the case study boiler requires that burners which are not firing to inject SA air at a rate of 5 [$kg/s$], this is to maintain non-firing burner integrity.
-
 \section{Results \& discussion}
 The current section will discuss the results obtained from using the above-mentioned modelling methodologies.
-The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100\%, 81\% and 60\% MCR loads) to that of the experimentally obtained results of the actual plant.
+The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100\%, 80\% and 60\% MCR loads) to that of the experimentally obtained results of the actual plant.
 Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.
@@
 \subsection{Model validation}\label{sec_model_valid}
-
 The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%.
@@
 \end{figure}
-
-In figure \ref{fig_heat_valid} it is shown that the overall heat loads are in good agreement with the measured results.
+\clearpage
+In Figure \ref{fig_heat_valid} it is shown that the overall heat loads are in good agreement with the calculated results.
 For the simulated validation loads the proposed model results are within the associated error band, the general trend is an under prediction on the furnace heat loads and an over prediction on the platen super-heater.
-The pendant super heater illustrate the best comparable results for all load cases.\\
+The pendant super heater illustrate the best comparable results for all load cases.
 
@@
 The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during a full load (100\% MCR) operating conditions.
-The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$] increment.\\
+The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$].\\
 \begin{figure}[h!]
@@
 It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
-For further information regarding the validation of the model the interested reader is directed to the works of Rawlins et al [REFERENCE]
-
+\newpage
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }

### 2021-09-25 PAPER_2/PAPER_2_REV1.tex
Update 25/09/2021

@@
 The model was simulated for a boiler load of 32 $\%$  with 6 various firing combinations.
-To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ boiler loads and compared to plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.
+To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ maximum continuous rating (MCR) loads and compared to actual plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.
 
@@
 \subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
-\caption{Experimentally calculated $CO$ and $O_2$ concentration predictions}
+\caption{Experimentally calculated $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentration predictions}
 \label{fig_probe_valid}
@@
 
-Explain the investigation
-table with case descriptions
-Need flownex model and process modelling description
-\begin{figure}
+Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} illustrate the temperature and velocity profiles for the various firing arrangements.
+With only the middle burner rows firing (Cases 2 and 5) there a is substantial cold region located in the lower half the furnace, resulting in the lowest heat uptake of the furnace for all the cases.
+This is further exaggerated when considering the Table \ref{tbl_process_parameters} with the mid-firing arrangement producing the lowest steam flow rates resulting in the lowest boiler efficiencies.
+The bottom firing arrangement (Cases 1 and 4) results in fireball located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is more even distribution of the fireball in the furnace domain.
+This leads to the highest steam generation rate and boiler efficiency as shown in Table \ref{tbl_process_parameters}.
+
+Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
+Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
+Cases 2 and 5 show that most of the unit heat fluxes are absorbed in the upper half of the boiler, contrary to cases 1 and 4, where the lower half has a higher heat flux absorption, and cases 3 and 6 showing an even distribution throughout the furnace.
+
+The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_CO$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
+For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these ideal circumstances.
+Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the top half of the furnace hopper, furthermore considering Figures \ref{fig_cfd_coppm}(c) and (d) a lower concentration of oxygen is reported.
+
+Investigating the combustion stability for all the cases, symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
+The general trends of the $CO_{ppm}$ correspond with each cases burner firing arrangement, as seen with cases 3 and 6, a mixed firing arrangement, where two peaks are observed in the vicinity of the bottom and middle burner rows.
+Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
+The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
+With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the fireball is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
+Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
+It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit temperature as is the case with cases 4 to 6.
+
+The external tube metal temperatures, of Figure \ref{tbl_cfd_results}, were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
+\begin{equation}\label{eqn_t_wall}
+T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
+\end{equation}
+For the platen and final SH the maximum surface temperature are observed for cases 2 and 5.
+For comparison a 100 \% MCR load the maximum temperatures reported for the platen and final SH are of 500 $[^\circ C]$ and 623 $[^\circ C]$, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
+Thus,
+
+Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
+
+\begin{figure}\label{fig_cfd_temp}
 \centering
 \includegraphics[scale = 0.45]{TEMP_KEY} [$K$]\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_TEMP}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_TEMP}}\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_TEMP}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_TEMP}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
+\subfigure[Case 1]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
+\subfigure[Case 2]{\includegraphics[width=0.32\textwidth]{MID_TEMP}}
+\subfigure[Case 3]{\includegraphics[width=0.32\textwidth]{FBRM_TEMP}}\\
+\subfigure[Case 4]{\includegraphics[width=0.32\textwidth]{BOT05_TEMP}}
+\subfigure[Case 5]{\includegraphics[width=0.32\textwidth]{MID05_TEMP}}
+\subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
 \caption{Temperature fields for cases 1 through 6 [(a)-(f)]}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h!]\label{fig_cfd_velo}
 \centering
 \includegraphics[scale = 0.45]{VEL_KEY} [$m/s$]\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_VEL}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_VEL}}\\
-\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_VEL}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_VEL}}
-\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
+\subfigure[Case 1]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
+\subfigure[Case 2]{\includegraphics[width=0.32\textwidth]{MID_VEL}}
+\subfigure[Case 3]{\includegraphics[width=0.32\textwidth]{FBRM_VEL}}\\
+\subfigure[Case 4]{\includegraphics[width=0.32\textwidth]{BOT05_VEL}}
+\subfigure[Case 5]{\includegraphics[width=0.32\textwidth]{MID05_VEL}}
+\subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
 \caption{Velocity fields for cases 1 through 6 [(a)-(f)]}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h!]\label{fig_cfd_heat_flux}
 \centering
 \includegraphics[scale = 0.45]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[]{\includegraphics[scale = 0.29]{BOT_HEATFLUX}}
+\subfigure[Case 1]{\includegraphics[scale = 0.29]{BOT_HEATFLUX}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.35]{MID_HEATFLUX}}
+\subfigure[Case 2]{\includegraphics[scale = 0.35]{MID_HEATFLUX}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.35]{FBRM_HEATFLUX}}\\
-\subfigure[]{\includegraphics[scale = 0.35]{BOT05_HEATFLUX}}
+\subfigure[Case 3]{\includegraphics[scale = 0.35]{FBRM_HEATFLUX}}\\
+\subfigure[Case 4]{\includegraphics[scale = 0.35]{BOT05_HEATFLUX}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.35]{MID05_HEATFLUX}}
+\subfigure[Case 5]{\includegraphics[scale = 0.35]{MID05_HEATFLUX}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
+\subfigure[Case 6]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
 \caption{Heat fluxes profiles for cases 1 through 6 [(a)-(f)]}
@@
 
-\begin{figure}
+\begin{figure}\label{fig_cfd_coppm}
 \centering
-\includegraphics[scale=0.45]{CO_MF_KEY} [$Y_{CO}$] \\
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
+\includegraphics[scale=0.45]{CO_MF_KEY} [$X_{CO}$] \\
+\subfigure[Case 1]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
+\subfigure[Case 2]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
+\subfigure[Case 3]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
+\subfigure[Case 4]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
+\subfigure[Case 5]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
-\subfigure[]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
+\subfigure[Case 6]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
 				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
-\caption{CO mass fraction ($Y_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
+\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
 \end{figure}
 
-\begin{figure}[h!]
+\begin{figure}[h!]\label{fig_cfd_probe}
 \centering
-\subfigure[]{\includegraphics[scale = 0.36]{SYMMETRY_PROBE_COPPM}}
+\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.36]{SYMMETRY_PROBE_COPPM}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.36]{OFFSET_PROBE_COPPM}}\\
-\subfigure[]{\includegraphics[scale = 0.35]{SYMMETRY_PROBE_XO2}}
+\subfigure[Offset vertical plot]{\includegraphics[scale = 0.36]{OFFSET_PROBE_COPPM}}\\
+\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.35]{SYMMETRY_PROBE_XO2}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}
+\subfigure[Offset vertical plot]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}
 
@@
 
-\begin{table}[h!]
+\begin{table}[h!]\label{tbl_process_parameters}
 \centering
@@
 \hline
-\textbf{Main steam flow rate} 	[$kg/s$]		&166&163&170	&171&169&163\\
-\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&535&535\\
-\textbf{RH steam flow rate} 	[$kg/s$]		&150&148&154	&154&153&147\\
-\textbf{RH steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&520&490\\
-\textbf{Boiler efficiency} 		[$\%$]			&86.2&84.9&88.8	&88.2&86.6&82.2\\
-\textbf{Attemperator 1} 		[$kg/s$]			&10.5&15&16		&11.5&9.5&12\\
-\textbf{Attemperator 2} 		[$kg/s$]			&5&8&5			&4&5&5.5\\
-\textbf{Attemperator RH} 		[$kg/s$]			&0.5&1&1		&0&0&0\\
+\textbf{Main steam flow rate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&520&510&512\\
+\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
+\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
+\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.67&4.2\\
+\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
 \hline
@@
 
-\begin{table}[h!]
+\begin{table}[h!]\label{tbl_cfd_results}
 \centering
@@
 \multicolumn{7}{l}{\textit{Platen SH}}\\
-\textbf{Max wall temperature} [$K$]  &754 & 750 & 765 & 766 & 753 & 763\\
-\textbf{Mean wall temperature} [$K$] &726 & 712 & 719 & 727 & 715 & 724\\
-\multicolumn{7}{l}{\textit{Pendant SH}}\\
-\textbf{Max wall temperature} [$K$]  & 805 & 807 & 811 & 808 & 800 & 802\\
-\textbf{Mean wall temperature} [$K$] & 793 & 788 & 792 & 795 & 788 & 784\\
+\textbf{Max wall temperature} [$^{\circ}C$]  &477 & 492 & 481  & 480 & 493 & 490\\
+\textbf{Mean wall temperature} [$^{\circ}C$] &439 & 453 & 446 & 454 & 442 & 451\\
+\multicolumn{7}{l}{\textit{Final SH}}\\
+\textbf{Max wall temperature} [$^{\circ}C$]  & 602 & 624 & 608 & 595 & 626 & 612\\
+\textbf{Mean wall temperature} [$^{\circ}C$] & 520 & 523 & 517 & 512 & 520 & 511\\
 \hline
@@
 \end{table}
-
-\begin{equation}
-T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
-\end{equation}
 
@@
 \section{Conclusions}
-
+ghhhb
+jyjjf
 \section*{Acknowledgements}

### 2021-09-27 PAPER_2/PAPER_2_REV1.tex
Update 27/09/2021

@@
 \modulolinenumbers[5]
+
+\usepackage{framed}
+\usepackage{multicol} % Multiple columns environment
+
+\usepackage{nomencl} % Nomenclature package
+\makenomenclature
+\setlength{\nomitemsep}{0pt}
+
+\newcommand{\nomunit}[1]{%
+  \renewcommand{\nomentryend}{\hspace*{\fill}#1}%
+}
+
+\renewcommand\nomgroup[1]{% 
+  \item[\bfseries
+  \ifstrequal{#1}{A}{Symbols}{%
+  \ifstrequal{#1}{B}{Greek symbols}{%
+  \ifstrequal{#1}{C}{Abbreviations}{}}}%
+]}
 
@@
 Low load operation of utility boiler
-
+ghfbksbv\\
+sfjvnsfjlvl\\
+kfnmvknsfklvns\\
+lk;sfvnsfnvsd\\
+sk,vnsfk;nvk;sdv\\
+ksdnv;sdv\\
+sknvk
 \end{abstract}
@@
 
+\printnomenclature
+
+\nomenclature[A]{$A$}{Area \nomunit{$m^2$}}
+\nomenclature[A]{$A_p$}{Particle surface area \nomunit{$m^2$}}
+\nomenclature[A]{$A_{pn}$}{Projected particle surface area \nomunit{$m^2$}}
+\nomenclature[A]{$A_{c}$}{Carbon pre-exponential factor \nomunit{$s^{-1}$}}
+\nomenclature[A]{$A_{vol}$}{Volatile pre-exponential factor \nomunit{$s^{-1}$}}
+\nomenclature[A]{$d_p$}{Particle diameter \nomunit{$m$}}
+\nomenclature[A]{$E$}{Fluid total energy \nomunit{$J/kg$}}
+\nomenclature[A]{$E_{a,c}$}{Carbon activation energy \nomunit{$J/kmol$}}
+\nomenclature[A]{$E_{a,vol}$}{Volatile activation energy \nomunit{$J/kmol$}}
+\nomenclature[A]{$E_p$}{Particle emission power \nomunit{$W/m^3$}}
+\nomenclature[A]{$f_{heat}$}{Near surface char oxidation fraction \nomunit{$-$}}
+\nomenclature[A]{$f_{p}$}{Forward scattering factor \nomunit{$-$}}
+\nomenclature[A]{$G$}{Incident radiation \nomunit{$W/m^2$}}
+\nomenclature[A]{$g$}{Gravitational constant \nomunit{$m/s^2$}}
+\nomenclature[A]{$h_{fg}$}{Enthalpy of evaporation \nomunit{$J/kg$}}
+\nomenclature[A]{$h_M$}{Mixture enthalpy \nomunit{$J/kg$}}
+\nomenclature[A]{$h_{rxn}$}{Enthalpy of reaction \nomunit{$J/kg$}}
+\nomenclature[A]{$J_k$ }{Species diffusion flux \nomunit{$m^2/s$}}
+\nomenclature[A]{$m_{0,vol}$}{Original mass of volatiles \nomunit{$kg$}}
+\nomenclature[A]{$m_{char}$}{Mass of carbon \nomunit{$kg$}}
+\nomenclature[A]{$m_{evap}$}{Mass of moisture \nomunit{$kg$}}
+\nomenclature[A]{$m_{vol}$}{Mass of volatiles \nomunit{$kg$}}
+\nomenclature[A]{$N_{p}$}{Number of particles \nomunit{$-$}}
+\nomenclature[A]{$P$}{Perimeter \nomunit{$m$}}
+\nomenclature[A]{$p$}{Pressure \nomunit{$Pa$}}
+\nomenclature[A]{$p_{O_{2}}$}{Partial pressure of $O_2$ \nomunit{$Pa$}}
+\nomenclature[A]{$\dot{Q}_{conv}$}{Convective heat transfer rate \nomunit{$W$}}
+\nomenclature[A]{$\dot{Q}_{rad}$}{Radiative heat transfer rate \nomunit{$W$}}
+\nomenclature[A]{$\dot{Q}_{w}$}{Wall heat transfer rate \nomunit{$W$}}
+\nomenclature[A]{$R$}{Universal gas constant \nomunit{$J/molK$}}
+\nomenclature[A]{$R_{c}$}{Carbon reaction rate \nomunit{$s^{-1}$}}
+\nomenclature[A]{$R_{diff}$}{Diffusion reaction rate \nomunit{$s^{-1}$}}
+\nomenclature[A]{$R_{vol}$}{Volatile reaction rate \nomunit{$s^{-1}$}}
+\nomenclature[A]{$T_g$}{Gas temperature \nomunit{$K$}}
+\nomenclature[A]{$T_p$}{Particle temperature \nomunit{$K$}}
+\nomenclature[A]{$t$}{Time \nomunit{$s$}}
+\nomenclature[A]{$u$}{Velocity \nomunit{$m/s$}}
+\nomenclature[A]{$V$}{Volume \nomunit{$m^3$}}
+\nomenclature[A]{$Y_k$}{Species mass fraction \nomunit{$kg/kg$}}
+\nomenclature[A]{$x$}{Quality \nomunit{$-$}}
+\nomenclature[B]{$\alpha_g$}{Gas absorption coefficient \nomunit{$m^{-1}$}}
+\nomenclature[B]{$\alpha_H$}{Mixture void fraction \nomunit{$-$}}
+\nomenclature[B]{$\alpha_p$}{Particle absorption coefficient \nomunit{$m^{-1}$}}
+\nomenclature[B]{$\epsilon$}{Emissivity \nomunit{$-$}}
+\nomenclature[B]{$\rho$}{Gas density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\rho_{eff}$}{Effective density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\rho_g$}{Gas density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\rho_l$}{Liquid density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\rho_M$}{Mixture density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\rho_p$}{Particle density \nomunit{$kg/m^3$}}
+\nomenclature[B]{$\sigma_{SB}$}{Stefan-Boltzmann constant \nomunit{$W/m^2K^4$}}
+\nomenclature[B]{$\sigma_{p}$}{Particle scattering coefficient \nomunit{$m^{-1}$}}
+\nomenclature[B]{$\phi$}{Scalar variable \nomunit{$-$}}
+\nomenclature[C]{$MCR$}{Maximum continuous rating}
+\nomenclature[C]{$CFPP$}{Coal fired power plant}
+\nomenclature[C]{$CFD$}{Computational fluid dynamics}
+\nomenclature[C]{$SH$}{Superheater}
+\nomenclature[C]{$EE$}{Eulerian-Eulerian}
+\nomenclature[C]{$WSGGM$}{Weighted sum of gray gas model}
+\nomenclature[C]{$RTE$}{Radiative transport equation}
+\nomenclature[C]{$HHV$}{Higher heating value}
+\nomenclature[C]{$DAF$}{Dry ash free}
+\nomenclature[C]{$AR$}{As-received}
+\nomenclature[C]{$PA$}{Primary air}
+\nomenclature[C]{$SA-AH$}{Secondary air - air heater}
+\nomenclature[C]{$SA$}{Secondary air}
+\nomenclature[C]{$RH$}{Reheater}
+\nomenclature[C]{$ATT$}{Attemperator}
+\nomenclature[C]{$EC$}{Economiser}
+\nomenclature{\mbox{}}{}
 \linenumbers
-
-\begin{center}
-\begin{tabular}{|p{0.075\textwidth}p{0.3\textwidth}p{0.05\textwidth}p{0.075\textwidth}p{0.3\textwidth}p{0.05\textwidth}|} 
- \hline
-\multicolumn{3}{|l}{\textbf{Nomenclature}} & &  &\\
-\textit{Symbol} & \textit{Quantity} & \textit{Unit} & & &\\
-$A$ &  Area & $m^2$ & & &\\
-$A_p$ & Particle surface area & $m^2$& & & \\
-$d_p$&Particle diameter & $m$ & & & \\
-$E$& Fluid total energy&$J/kg$ & & & \\
-$E_a$& Reaction activation energy&$J/kmol$ & & & \\
-$P$& Pressure & $Pa$ & & & \\
-$T_g$& Gas temperature& $K$ & & & \\
-$T_p$&Particle temperature & $K$& & & \\
-$u$& Velocity &$m/s^2$ & & &\\
-\hline
-\end{tabular}
-\end{center}
-
 \section{Introduction}
@@
 \begin{equation}\label{eqn_momentum}
-\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{P}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
+\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
 \end{equation}\\
-\\
 Energy conservation:
 \begin{equation}\label{eqn_energy}
-\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+P])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
+\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
 \end{equation}
@@
 
-To correctly account for the particle inertial effects on the gas phase convection an effective density is defined as follows;
+To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
 \begin{equation} \label{eqn_eff_rho}
@@
 \begin{gather}
-\frac{dm_{char}}{dt} = -A_p P_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
+\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
 C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
@@
 \begin{gather}
-R_{diff} = \frac{5X10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^0.75 \label{eqn_char_diff_rate}\\
+R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
 \begin{split}
@@
 \begin{equation}\label{eqn_phi_hp}
-\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dM_{evap}}{dt}h_{fg}\right)\frac{1}{V}
+\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
 \end{equation}
 
-The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dM_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dM_{c}}{dt}h_{rxn}\right)$.
+The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$.
 This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
@@
 \begin{equation}\label{eqn_RTE}
-\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_SB T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
 \end{equation}
@@
 The WSGGM accounts for the radiation emitted by tri-atomic gases, namely $CO_2$, $H_2O$ and $SO_2$ present in the flue gas stream.
-The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p$) present in a cell.
+The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p = \rho \phi_{mp0} V / \left( \rho_p \pi \bar{d_p}^3 /6 \right)$) present in a cell.
 There formulations are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
@@
 
-It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) are used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \citep{Yin2015} respectively.
+It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \citep{Yin2015} respectively.
 
@@
 \label{tbl_case_inputs}
-\vspace{5mm}
-\label{fuel}
+\vspace{2mm}
 {\tabulinesep=1.2mm
@@
 \hline
-\textbf{Fuel flow rate} [$kg/s$]&3.14  &3.14\\
-\textbf{PA flow rate} [$kg/s$]&4.95  &4.95\\
-\textbf{SA flow rate} [$kg/s$]&14.85  &14.85\\
+\textbf{Fuel flow-rate} [$kg/s$]&3.14  &3.14\\
+\textbf{PA flow-rate} [$kg/s$]&4.95  &4.95\\
+\textbf{SA flow-rate} [$kg/s$]&14.85  &14.85\\
 \hline
@@
 \hline
-\textbf{SA flow rate} [$kg/s$]&5.0  &2.5\\
+\textbf{SA flow-rate} [$kg/s$]&5.0  &2.5\\
 \hline
@@
 
-Table \ref{tbl_case_inputs} shows a lower mass flow rate of SA air for case 4 to 6, this was done to compare the expected increase in boiler utilization efficiency, since less dry gas losses are expected, and the effects the drop in the flue-gas mass flow rate has on the convective pass components modelled in the process model.
+Table \ref{tbl_case_inputs} shows a lower mass flow rate of SA air for case 4 to 6, this was done to compare the expected increase in boiler utilization efficiency, since less dry gas losses are expected, and the effects the drop in the flue-gas mass flow-rate has on the convective pass components modelled in the process model.
 
@@
 The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
-For all cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
+For all cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow-rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
 The remaining fields were solved till convergence.
@@
 \begin{figure}[h!]
-	\subfigure[]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
-	\subfigure[]{\includegraphics[width=0.32\textwidth]{80_VALID_BAR}}
-	\subfigure[]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
-\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and pendant SH at (a) 100\% MCR, (b) 80\% MCR and (c) 60\% MCR}
+	\subfigure[100 \% MCR]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
+	\subfigure[80 \% MCR]{\includegraphics[width=0.32\textwidth]{80_VALID_BAR}}
+	\subfigure[60 \% MCR]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
+\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
 \label{fig_heat_valid}
@@
 \end{figure}
-
-Figure \ref{fig_probe_valid} shows the averaged measurement values to that of the CFD predictions.
+Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
 It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
@@
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
-
-Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} illustrate the temperature and velocity profiles for the various firing arrangements.
-With only the middle burner rows firing (Cases 2 and 5) there a is substantial cold region located in the lower half the furnace, resulting in the lowest heat uptake of the furnace for all the cases.
-This is further exaggerated when considering the Table \ref{tbl_process_parameters} with the mid-firing arrangement producing the lowest steam flow rates resulting in the lowest boiler efficiencies.
-The bottom firing arrangement (Cases 1 and 4) results in fireball located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is more even distribution of the fireball in the furnace domain.
+The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+With only the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
+This is further exaggerated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
+The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}).
 This leads to the highest steam generation rate and boiler efficiency as shown in Table \ref{tbl_process_parameters}.
 
-Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
-Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
-Cases 2 and 5 show that most of the unit heat fluxes are absorbed in the upper half of the boiler, contrary to cases 1 and 4, where the lower half has a higher heat flux absorption, and cases 3 and 6 showing an even distribution throughout the furnace.
-
-The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_CO$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
-For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these ideal circumstances.
-Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
-Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the top half of the furnace hopper, furthermore considering Figures \ref{fig_cfd_coppm}(c) and (d) a lower concentration of oxygen is reported.
-
-Investigating the combustion stability for all the cases, symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
-The general trends of the $CO_{ppm}$ correspond with each cases burner firing arrangement, as seen with cases 3 and 6, a mixed firing arrangement, where two peaks are observed in the vicinity of the bottom and middle burner rows.
-Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
-The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
-With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the fireball is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
-Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
-It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit temperature as is the case with cases 4 to 6.
-
-The external tube metal temperatures, of Figure \ref{tbl_cfd_results}, were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
-\begin{equation}\label{eqn_t_wall}
-T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
-\end{equation}
-For the platen and final SH the maximum surface temperature are observed for cases 2 and 5.
-For comparison a 100 \% MCR load the maximum temperatures reported for the platen and final SH are of 500 $[^\circ C]$ and 623 $[^\circ C]$, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
-Thus,
-
-Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
-
-\begin{figure}\label{fig_cfd_temp}
+\begin{figure}[h!]
 \centering
@@
 \caption{Temperature fields for cases 1 through 6 [(a)-(f)]}
+\label{fig_cfd_temp}
 \end{figure}
 
-\begin{figure}[h!]\label{fig_cfd_velo}
+\begin{figure}[h!]
 \centering
@@
 \caption{Velocity fields for cases 1 through 6 [(a)-(f)]}
+\label{fig_cfd_velo}
 \end{figure}
 
-\begin{figure}[h!]\label{fig_cfd_heat_flux}
+\begin{table}[h!]
+\centering
+\caption{Process model control parameters}
+\vspace{2mm}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\textbf{Main steam flow-rate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
+\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
+\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
+\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
+\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
+\hline
+\label{tbl_process_parameters}
+\end{tabularx}}
+\end{table}
+
+Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
+Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
+An even distribution of unit heat fluxes is seen in cases 3 and 6 with minimal localised heat flux concentrations being observed.
+Cases 2 and 5 show that most of the unit heat fluxes are absorbed in the upper half of the boiler with case 5 showing a higher heat flux on the rear wall.
+This could be due the use of a lower SA flow-rate leading to velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
+With this is mind a lower SA flow-rate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+With high gas temperatures and velocity impingement, cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding cases 1, 2 and 3.
+
+\begin{figure}[h!]
 \centering
 \includegraphics[scale = 0.45]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[Case 1]{\includegraphics[scale = 0.29]{BOT_HEATFLUX}}
+\subfigure[Case 1]{\includegraphics[scale = 0.35]{BOT_HEATFLUX}}
 \hspace{5mm}
@@
 \subfigure[Case 3]{\includegraphics[scale = 0.35]{FBRM_HEATFLUX}}\\
-\subfigure[Case 4]{\includegraphics[scale = 0.35]{BOT05_HEATFLUX}}
+\subfigure[Case 4]{\includegraphics[scale = 0.29]{BOT05_HEATFLUX}}
 \hspace{5mm}
@@
 \caption{Heat fluxes profiles for cases 1 through 6 [(a)-(f)]}
+\label{fig_cfd_heat_flux}
 \end{figure}
 
-\begin{figure}\label{fig_cfd_coppm}
+The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
+For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these ideal circumstances.
+Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
+The figures generally highlight the location and distribution of the flame core for each case.
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.
+
+\begin{figure}[h!]
 \centering
@@
 \caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
+\label{fig_cfd_coppm}
 \end{figure}
 
-\begin{figure}[h!]\label{fig_cfd_probe}
+Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
+The general trends of the $CO_{ppm}$ correspond with each cases burner firing arrangement, as seen with cases 3 and 6, a mixed firing arrangement, where two peaks are observed in the vicinity of the bottom and middle burner rows.
+Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
+The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
+With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the flame core is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
+Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
+It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit temperature as seen with cases 4 to 6.
+
+\begin{figure}[h!]
 \centering
@@
 \subfigure[Offset vertical plot]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}
+\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
+\label{fig_cfd_probe}
+\end{figure}
+\clearpage
 
-\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
-\end{figure}
-
-\begin{table}[h!]\label{tbl_process_parameters}
-\centering
-\caption{Process model control parameters}
-\label{fuel}
-{\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
-\hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
-\hline
-\textbf{Main steam flow rate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
-\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
-\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
-\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&520&510&512\\
-\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
-\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
-\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.67&4.2\\
-\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
-\hline
-\end{tabularx}}
-\end{table}
-
-\begin{table}[h!]\label{tbl_cfd_results}
+\begin{table}[h!]
 \centering
 \caption{Furnace exit conditions and SH wall temperatures}
-\label{fuel}
+\vspace{2mm}
 {\tabulinesep=1.2mm
@@
 \hline
+\label{tbl_cfd_results}
 \end{tabularx}}
 \end{table}
+The external tube metal temperatures, of Table \ref{tbl_cfd_results}, were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
+\begin{equation}\label{eqn_t_wall}
+T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
+\end{equation}
+For the platen and final SH the maximum surface temperature are observed for cases 2 and 5.
+For comparison a 100 \% MCR load the maximum temperatures reported for the platen and final SH are of 500 $[^\circ C]$ and 623 $[^\circ C]$, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
+Thus, continued operation using the firing arrangement of cases 2 and 5, could lead to SH failure.
+
+Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
+Table \ref{tbl_process_parameters} summarizes the results with the highest boiler efficiencies been observed for cases 3 and 6.
+With a lower SA flow-rate cases 4 to 6 exhibit a higher boiler efficiency due to the decrease in dry gas losses, when compared to cases 1 to 3.
+All cases exhibit adequate control of the main steam exit temperature by use of ATT1 and ATT2.
+The re-heaters' exit temperature, for all cases, are determined to within the 20 [$^\circ C$] tolerance for the intermediate turbine inlet conditions, as stipulated in the design C-schedules for the plant.
+However, with the lack of ATT-RH control, a sudden decreases in steam generation can lead to SH overheating and possible SH failure.
+Considering all of the above, cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load 32 \% MCR.
+
+Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat exchanger for cases 3 and 6.
+It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10 \% being transferred to convection at low-load.
+Considering the convective pass heat exchangers (RH2 through to the EC, refer to Figure \ref{fig_flownex}) the convective heat transfer becomes more apparent as seen with the reduction in radiative heat transfer percentage.
+Case 6 tends to exhibit less convective heat transfer for the said  heat exchangers, due to the fact of a lower SA flow-rate for non-firing burners.
+This will reduce the total amount of flue-gas flowing through the boiler, for the same cross flow-area and similar density the velocity would be expected to drop, reducing the convective heat transfer.
 
@@
 \centering
-\caption{Radiative heat transfer percentage for the platen and pendant SH}
-\label{fuel}
+\caption{Radiative heat transfer percentage for cases 3 and 6}
+\vspace{2mm}
 {\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.25\linewidth} XX}
+\begin{tabularx}{\linewidth}{p{0.4\linewidth} XX}
 \hline
-&\multicolumn{2}{c}{Cases}\\
- &\textbf{3}&\textbf{6}\\
+ &\textbf{Case 3}&\textbf{Case 6}\\
 \hline
-Evaporator \\
-Platen SH [\%] & \\
-Pendant SH [\%] &\\
-Secondary RH [\%]\\
-Primary SH [\%]\\
-Primary RH [\%]\\
-Economiser [\%]\\
+Furnace [\%] & 89.2 & 88.9\\
+Platen SH (SH2) [\%] & 92.5& 93.4\\
+Final SH (SH3) [\%] & 93.5& 94.0\\
+RH2 [\%] & 47.6& 52.2\\
+SH1 [\%] & 37.2& 40.7\\
+RH1 [\%] & 18.7& 21.5\\
+EC [\%] & 5.4& 6.5\\
 \hline
+\label{tbl_rad_conv}
 \end{tabularx}}
@@
 \section{Conclusions}
-ghhhb
-jyjjf
+The present study demonstrates the use of a coupled simulation used to study the effects of burner configuration at a boiler load of 32 \% MCR.
+A validation case was performed for the developed CFD model which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
+The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.
+
+The results show that using a burner arrangement that raises the position of the flame core (cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
+Subsequently, this firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream potentially leading to economic losses, regarding the efficient combustion of the fuel and the lowest boiler utilization efficiency.
+
+Operation of the boiler using firing arrangements of cases 1 and 4, in relation to cases 3 and 6 results in lower boiler utilization efficiency and exit flue-gas temperature.
+Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high possibility of fire side corrosion occurring at continuous low-load operation using cases 1 and 4.
+
+The mixed firing arrangement, of case 3 and 6, exhibits the best boiler utilization efficiency overall.
+A 4.8 \% decrease in unburnt carbon percentage is observed when operating using case 3 in relation to case 6.
+The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $^\circ C$, allowing for better control.
+
+Based on the current numerical study, carried out to determine the most favourable operating parameters and combustion stability, case 3 is seen as the optimal firing arrangement for the boiler under consideration.
+
 \section*{Acknowledgements}
 The authors would like to thank the Eskom EPPEI program for financially supporting the present study and acknowledge the computational resources provided by the Centre for High Performance Computing (CHPC), South Africa.
-
-\section*{References}
 

### 2021-09-28 PAPER_2/PAPER_2_REV1.tex
Update 28/09/2021

@@
 \bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Low load operating protocol investigation of a 620MWe power boiler using an indirectly coupled process model}
+\title{Numerical investigation of the low-load operating protocol of a 620MWe sub-critical power boiler through co-simulation}
 
@@
 \begin{abstract}
-
-Low load operation of utility boiler
-ghfbksbv\\
-sfjvnsfjlvl\\
-kfnmvknsfklvns\\
-lk;sfvnsfnvsd\\
-sk,vnsfk;nvk;sdv\\
-ksdnv;sdv\\
-sknvk
+This paper uses co-simulation techniques which incorporate a computational fluid dynamic (CFD) model together with a process level model to investigate the low-load operation of a 620 $MWe$ sub-critical boiler.
+A 1D discretized two-phase model of the water/steam circuit of the furnace, the radiant superheaters (SH) and the convective/back pass heat exchangers was developed.
+This was coupled with a detailed CFD model incorporating the furnace and radiant superheaters using an Eulerian-Eulerian reference frame.
+The coupled model is used to investigate the combustion stability, the water/steam side effects and the radiant heat exchanger operational limits for six burner firing arrangements for a minimal boiler load of 32 \%.
+The results show that certain firing arrangements can lead to a high possibility of fire-side corrosion and the over-heating of heat exchanging components.
+Based on the numerical simulations carried out in terms of obtaining combustion stability, a favourable boiler utilization efficiency and the safe operation of heat exchanging components, a mixed firing arrangement accompanied with a higher secondary air (SA) mass flow-rate for non-firing burners was selected as the best case for the boiler under investigation.
 \end{abstract}
@@
 \begin{keyword}
-CFD\sep Eulerian-Eulerian\sep Boiler \sep Low-load operation
+CFD\sep Boiler \sep Low-load operation \sep Co-simulation
 \end{keyword}
-
+\newpage
 \end{frontmatter}
@@
 \nomenclature[B]{$\alpha_p$}{Particle absorption coefficient \nomunit{$m^{-1}$}}
-\nomenclature[B]{$\epsilon$}{Emissivity \nomunit{$-$}}
+\nomenclature[B]{$\epsilon_p$}{Particle emissivity \nomunit{$-$}}
 \nomenclature[B]{$\rho$}{Gas density \nomunit{$kg/m^3$}}
@@
 However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
-Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 $\%$ of the energy needs being met using CFPPs \cite{eskom}.
+Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}.
 The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol.
@@
 
-Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 $\%$.
+Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%.
 The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances.
@@
 The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler.
-Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.
+Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $[^\circ C]$.
 
@@
 Momentum conservation:
-\\
 \begin{equation}\label{eqn_momentum}
 \frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
-\end{equation}\\
+\end{equation}
 Energy conservation:
@@
 \end{equation}
-\\
 Species transport:
@@
 \end{equation}
-
 To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
@@
 \caption{Scalar field equation descriptions}\label{tab_scalars}  
+\vspace{2mm}     
 \begin{tabular}{lll}
@@
 In the present work the RTE is solved sing the P1 model.
-Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 MWe CFPP boiler.
+Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler.
 The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$).
-The P1 model transport variable is the incident radiation (G - [$W/m^2$]), and can be written for a particle laden domain as:
+The P1 model transport variable is the incident radiation (G), and can be written for a particle laden domain as:
 \begin{equation}
@@
 The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
-The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH) are inlets and outlets.
+The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets.
 \begin{figure}[h!]
@@
 \caption{Utility boiler fuel characteristics}
-\vspace{5mm}
+\vspace{2mm}
 \label{tbl_fuel}
@@
 
-For a 32\% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.
+For a 32 \% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.
 For this study six cases are simulated in total with the following three burner firing configurations being utilized:
@@
 The current section will discuss the results obtained from using the above-mentioned modelling methodologies.
-The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100\%, 80\% and 60\% MCR loads) to that of the experimentally obtained results of the actual plant.
+The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100 \%, 80 \% and 60 \% MCR loads) to that of the experimentally obtained results of the actual plant.
 Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.
@@
 \subsection{Model validation}\label{sec_model_valid}
-The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%.
+The validation of the proposed model was conducted for three steady-state MCR loads of 100 \%, 80 \% and 60 \%.
 The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
@@
 \end{figure}
+
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
@@
 				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
-\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
+\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
 \label{fig_cfd_coppm}
@@
 A 4.8 \% decrease in unburnt carbon percentage is observed when operating using case 3 in relation to case 6.
-The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $^\circ C$, allowing for better control.
+The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $[^\circ C]$, allowing for better control.
 

### 2021-10-05 PAPER_2/PAPER_2_REV1.tex
Update1 - 05/10/2021
Update2 - 05/10/2021

@@
 
-\journal{Journal of Applied Thermal Engineering}
+\journal{Energy}
 
@@
 
-\title{Numerical investigation of the low-load operating protocol of a 620MWe sub-critical power boiler through co-simulation}
+\title{Numerical investigation of low-load operation of a subcritical power boiler using CFD and process modelling}
 
@@
 \address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
+\address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}
 
@@
 \section{Introduction}
-The use of coal fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change.
-However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
-Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}.
-The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol.
-This will inherently mean CFPPs will need to operate at low-loads for continuous time periods.
+The use of coal-fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change.
+However, the switch to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
+Due to the abundance of coal resource present in Southern Africa, CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}.
+The promising integration of renewable energy and the decommissioning of old CFPPs in Southern Africa, will push these plants from a primarily base load operation to a mid-merit/flexible operating protocol.
+The switch to flexible operation will inherently mean CFPPs will need to operate at low-loads for continuous time periods.
 
-Mathematical models that can accurately capture the behaviour of the boilers thermal-hydraulic response at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}.
-Since, the long term deviation from design conditions can lead to operational incapabilities affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.
+Mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}.
+Since, the long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.
 
-The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumnavigating the use of time-consuming and costly field tests.
+The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumventing the use of time-consuming and costly field tests.
 CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).
@@
 A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions.
-However, to the best the authors' knowledge, no integration of 1-D thermal-hydraulic model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.
+The aforementioned reseacrh specifically investigated combustion and gas-side effects.
+However, to the best the authors' knowledge, no integration of 1-D process model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.
 
-The use of a 1-D thermal-hydraulic modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions.
+The use of a 1-D process modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions.
 These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}.
-Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D thermal-hydraulic models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.
+Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.
 
-The use of coupled simulations has proven to solve the deficiencies of a full 1-D thermal-hydraulic model by coupling the fireside CFD to a 1-D water network.
-Recently Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}.
+The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model.
+Some recent papers that investigated boiler operations using a co-simulation approach are: Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}.
 Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.
 
-The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler.
-Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $[^\circ C]$.
+The goal of the current work is to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flow-rates and metal temperatures.
+The current work proposes the use of CFD modelling  to investigate the low-load gas-side effects at various firing conditions for a 620 $MWe$ two-pass sub-critical boiler.
+For the current work CFD gas-side results are coupled to a comprehensive process model of the case study boilers water side.
 
@@
 \section{Mathematical model}
-In this section the modelling techniques used by the study are elaborated.
-A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution.
-Following this is a description of the heat transfer modelling techniques and the ends with a description of the process modelling configuration.
+In this section the modelling techniques used by the study are briefly discussed.
 \subsection{Computational fluid dynamics modelling}
@@
 \end{equation}
-To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
+To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows;
 \begin{equation} \label{eqn_eff_rho}
@@
 This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners.
-The model generally generates higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.
+The model generally produces higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.
 
-The process of coal combustion comprises four steps.
+The process of coal combustion comprises of four sequential steps.
 Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions.
@@
 
-A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized.
+A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.
 The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}).
@@
 \subsubsection{Particle modelling}
-The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a multi-phase Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}.
+The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.
+The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}.
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash.
@@
 
-The energy transport of the pseudo particle, is transported by defining the particle enthalpy using the following equation:
+The energy transport of the pseudo particle phase, is transported by defining a particle phase energy equation, which in turn uses the particle enthalpy.
 \begin{equation}\label{eqn_phi_hp}
@@
 
-The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$.
+The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$.
 This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
+To solve the additional transport equations and their source terms, C programs were developed.
 
 \subsection{Heat transfer modelling modelling}
-The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
+Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
 \begin{equation}\label{eqn_RTE}
@@
 \end{equation}
-In the present work the RTE is solved sing the P1 model.
+In the present work the RTE is solved using the P1 model.
 Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler.
 The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$).
-The P1 model transport variable is the incident radiation (G), and can be written for a particle laden domain as:
+The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
 \begin{equation}
@@
 The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p = \rho \phi_{mp0} V / \left( \rho_p \pi \bar{d_p}^3 /6 \right)$) present in a cell.
-There formulations are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
+The equations for the radiative properties are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
 \begin{gather}
@@
 \subsection{Process simulation model}
-A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021.
+A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021.
 The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls.
@@
 \end{gather}
-Applying the mixture density the following transport equations are solved;
+Applying the mixture density the following transport equations are solved per process model component;
 
@@
 The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
-The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various cases have on the system.
+The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various Cases have on the water-side of the boiler system.
 
 \section{Case study boiler description \& set-up}
-In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry, the process model set-up, the various  modelling inputs (i.e.
-fuel characteristics and boundary conditions) and ends with the numerical solution strategy.
+In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boiler geometry, the process model set-up, the various  modelling inputs (i.e.
+fuel characteristics and boundary conditions) and the numerical solution strategy.
 
@@
 
-The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners.
+The boiler furnace is fed by 6 mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners.
 This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.
@@
 The process model of the boiler configuration is shown in Figure \ref{fig_flownex}.
-The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
+The process model includes all the heat exchangers up to and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
 The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets.
+The process model is used to determine the required attemperation flow-rates and water/steam side thermal response.
+The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system which include the downcomers and steam drum.
+As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.
+
+The coupling interface between the simulation models are the heat exchanger external tube surfaces, namely the furnace, platen and final SH walls.
+The CFD heat loads are used as energy sources for these components as indicated in Figure \ref{fig_flownex}.
+Furthermore, the CFD flue-gas results (i.e.
+composition, mass flow and temperature) exiting the final SH are used as boundary inputs for the heat exchangers downstream of the final SH (SH3).
+The steam flow boundary values for the RH and EC sections are fixed mass inlet flows and temperatures with the corresponding outlets set to a fixed pressure.
+
 \begin{figure}[h!]
@@
 
-The heat load results of the CFD simulation for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}. 
 \newpage
 \subsection{Model inputs}
-Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).\\
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the fuels higher heating value (HHV).\\
 \begin{table}[h!]
@@
 For a 32 \% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.
-For this study six cases are simulated in total with the following three burner firing configurations being utilized:
+For this study six Cases are simulated in total with the following three burner firing configurations being investigated:
 \begin{enumerate}
@@
 
+Typically 5 [$kg/s$] of air is fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
+The result is a high air-fuel ratio in the furnace which leads to higher dry gas losses.
+to lower this loss, this study will investigate the affect of reducing the air-fuel ratio by lowering the non-firing burner SA flow-rate from 5 to 2.5 [$kg/s$].
 Two permutations of the SA flow rate, at the non-firing burners, are used for each of the firing configurations mentioned above.
-Table \ref{tbl_case_inputs} shows the input conditions for cases 1 to 6.
-The data is the result of a boilers mass and energy balance calculations.
+Table \ref{tbl_case_inputs} shows the input conditions for Cases 1 to 6.
+The data is the result of a boilers mass and energy balance calculation.
 
@@
 
-Table \ref{tbl_case_inputs} shows a lower mass flow rate of SA air for case 4 to 6, this was done to compare the expected increase in boiler utilization efficiency, since less dry gas losses are expected, and the effects the drop in the flue-gas mass flow-rate has on the convective pass components modelled in the process model.
-
 \subsection{Numerical solution strategy} 
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
-the pressure-momentum coupling utilised the SIMPLE technique.
+The pressure-momentum coupling utilised the SIMPLE method.
 Second-order upwinding was used to discretize the momentum, energy and species equations, whereas PRESTO!
@@
 The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
-For all cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow-rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
+For all Cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow-rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
 The remaining fields were solved till convergence.
@@
 \section{Results \& discussion}
-The current section will discuss the results obtained from using the above-mentioned modelling methodologies.
-The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100 \%, 80 \% and 60 \% MCR loads) to that of the experimentally obtained results of the actual plant.
-Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.
-
 \subsection{Model validation}\label{sec_model_valid}
-The validation of the proposed model was conducted for three steady-state MCR loads of 100 \%, 80 \% and 60 \%.
+The validation of the proposed model was conducted for three steady-state MCR loads of 100 \%, 80 \% and 60 \%, where actual plant measurements are used to calculate the
+thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
 The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
@@
 In Figure \ref{fig_heat_valid} it is shown that the overall heat loads are in good agreement with the calculated results.
-For the simulated validation loads the proposed model results are within the associated error band, the general trend is an under prediction on the furnace heat loads and an over prediction on the platen super-heater.
-The pendant super heater illustrate the best comparable results for all load cases.
+For the simulated validation loads the proposed model results are within the associated error band, the general trend is an under prediction on the furnace heat loads, with a maximum percentage error of 2 \%, and an over prediction on the platen SH, with a maximum percentage error of 7 \% .
+The pendant SH illustrate the best comparable results for all load Cases.
 
@@
 The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-With only the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
-This is further exaggerated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
+When the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
+This is further exacerbated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
 The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}).
-This leads to the highest steam generation rate and boiler efficiency as shown in Table \ref{tbl_process_parameters}.
+This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Table \ref{tbl_process_parameters}.
 
@@
 \subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
-\caption{Temperature fields for cases 1 through 6 [(a)-(f)]}
+\caption{Temperature fields for Cases 1 through 6 [(a)-(f)]}
 \label{fig_cfd_temp}
@@
 \subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
-\caption{Velocity fields for cases 1 through 6 [(a)-(f)]}
+\caption{Velocity fields for Cases 1 through 6 [(a)-(f)]}
 \label{fig_cfd_velo}
@@
 Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
-An even distribution of unit heat fluxes is seen in cases 3 and 6 with minimal localised heat flux concentrations being observed.
+An even distribution of unit heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
 Cases 2 and 5 show that most of the unit heat fluxes are absorbed in the upper half of the boiler with case 5 showing a higher heat flux on the rear wall.
-This could be due the use of a lower SA flow-rate leading to velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
-With this is mind a lower SA flow-rate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-With high gas temperatures and velocity impingement, cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding cases 1, 2 and 3.
+This could be due the use of a lower SA flow-rate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
+With this is mind a lower SA flow-rate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.
 
@@
 \subfigure[Case 6]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
-\caption{Heat fluxes profiles for cases 1 through 6 [(a)-(f)]}
+\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
 \label{fig_cfd_heat_flux}
@@
 The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
-For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these ideal circumstances.
+For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
 Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
@@
 				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
-\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
+\caption{CO molar fraction ($X_{CO}$) concentrations for 
+Cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
 \label{fig_cfd_coppm}
@@
 
-Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
-The general trends of the $CO_{ppm}$ correspond with each cases burner firing arrangement, as seen with cases 3 and 6, a mixed firing arrangement, where two peaks are observed in the vicinity of the bottom and middle burner rows.
+Investigating the combustion stability for all the Cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
 Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
@@
 Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
-It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit temperature as seen with cases 4 to 6.
+It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
 
@@
 The external tube metal temperatures, of Table \ref{tbl_cfd_results}, were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
+Fouling thermal resistances of 0.0067 and 0.015 [$m^2K/W$] were used for the platen and final SH respectively.
 \begin{equation}\label{eqn_t_wall}
@@
 \end{equation}
-For the platen and final SH the maximum surface temperature are observed for cases 2 and 5.
-For comparison a 100 \% MCR load the maximum temperatures reported for the platen and final SH are of 500 $[^\circ C]$ and 623 $[^\circ C]$, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
-Thus, continued operation using the firing arrangement of cases 2 and 5, could lead to SH failure.
+For the platen and final SH the maximum surface temperature are observed for Cases 2 and 5.
+For comparison at 100 \% MCR load the maximum and mean temperatures reported for the platen and final SH are 500 \& 446 $[^\circ C]$ and 623 \& 531 $[^\circ C]$ respectively, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
+Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.
 
 Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
-Table \ref{tbl_process_parameters} summarizes the results with the highest boiler efficiencies been observed for cases 3 and 6.
-With a lower SA flow-rate cases 4 to 6 exhibit a higher boiler efficiency due to the decrease in dry gas losses, when compared to cases 1 to 3.
-All cases exhibit adequate control of the main steam exit temperature by use of ATT1 and ATT2.
-The re-heaters' exit temperature, for all cases, are determined to within the 20 [$^\circ C$] tolerance for the intermediate turbine inlet conditions, as stipulated in the design C-schedules for the plant.
-However, with the lack of ATT-RH control, a sudden decreases in steam generation can lead to SH overheating and possible SH failure.
-Considering all of the above, cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load 32 \% MCR.
+Table \ref{tbl_process_parameters} summarizes the results with the highest boiler efficiencies observed for Cases 3 and 6.
+With a lower SA flow-rate Cases 4 to 6 exhibit a higher boiler efficiency due to the decrease in dry gas losses, when compared to Cases 1 to 3.
+All Cases exhibit adequate control of the main steam exit temperature by use of ATT1 and ATT2.
+The exit temperature of the reheaters, for all Cases, are determined to within the 20 [$^\circ C$] tolerance for the intermediate turbine inlet conditions, as stipulated in the design C-schedules for the plant.
+However, with the lack of ATT-RH control, a sudden decreases in steam generation can lead to RH overheating and possible RH failure.
+Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load 32 \% MCR.
 
-Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat exchanger for cases 3 and 6.
+Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat exchanger for Cases 3 and 6.
 It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10 \% being transferred to convection at low-load.
@@
 \centering
-\caption{Radiative heat transfer percentage for cases 3 and 6}
+\caption{Radiative heat transfer percentage for Cases 3 and 6}
 \vspace{2mm}
@@
 
-The results show that using a burner arrangement that raises the position of the flame core (cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
+The results show that using a burner arrangement that raises the position of the flame core (Cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
 Subsequently, this firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream potentially leading to economic losses, regarding the efficient combustion of the fuel and the lowest boiler utilization efficiency.
 
-Operation of the boiler using firing arrangements of cases 1 and 4, in relation to cases 3 and 6 results in lower boiler utilization efficiency and exit flue-gas temperature.
-Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high possibility of fire side corrosion occurring at continuous low-load operation using cases 1 and 4.
+Operation of the boiler using firing arrangements of Cases 1 and 4, in relation to Cases 3 and 6 results in lower boiler utilization efficiency and exit flue-gas temperature.
+Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high possibility of fire side corrosion occurring at continuous low-load operation using Cases 1 and 4.
 

### 2021-10-20 PAPER_2/PAPER_2_REV1.tex
Update2 - 20/10/2021

@@
 \cortext[mycorrespondingauthor]{Corresponding author}
-\ead{ryno.laubscher@uct.ac.za}
+\ead{rlaubscher@sun.ac.za}
 \author{P. Rousseau}
-\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
+\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
 \address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}
@@
 \begin{abstract}
-This paper uses co-simulation techniques which incorporate a computational fluid dynamic (CFD) model together with a process level model to investigate the low-load operation of a 620 $MWe$ sub-critical boiler.
-A 1D discretized two-phase model of the water/steam circuit of the furnace, the radiant superheaters (SH) and the convective/back pass heat exchangers was developed.
-This was coupled with a detailed CFD model incorporating the furnace and radiant superheaters using an Eulerian-Eulerian reference frame.
-The coupled model is used to investigate the combustion stability, the water/steam side effects and the radiant heat exchanger operational limits for six burner firing arrangements for a minimal boiler load of 32 \%.
-The results show that certain firing arrangements can lead to a high possibility of fire-side corrosion and the over-heating of heat exchanging components.
-Based on the numerical simulations carried out in terms of obtaining combustion stability, a favourable boiler utilization efficiency and the safe operation of heat exchanging components, a mixed firing arrangement accompanied with a higher secondary air (SA) mass flow-rate for non-firing burners was selected as the best case for the boiler under investigation.
+Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model.
+A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers.
+This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame.
+The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating.
+The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components.
+Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
 \end{abstract}
@@
 \nomenclature{\mbox{}}{}
-\linenumbers
+%\linenumbers
 \section{Introduction}
-The use of coal-fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change.
-However, the switch to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
-Due to the abundance of coal resource present in Southern Africa, CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}.
-The promising integration of renewable energy and the decommissioning of old CFPPs in Southern Africa, will push these plants from a primarily base load operation to a mid-merit/flexible operating protocol.
-The switch to flexible operation will inherently mean CFPPs will need to operate at low-loads for continuous time periods.
+The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change.
+However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
+Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\
 
-Mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}.
-Since, the long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.
+The integration of renewable energy sources will push CFPPs from primarily base load operation to a mid-merit/flexible operating protocol, which includes prolonged operation at low-loads.
+Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.\\
 
-The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumventing the use of time-consuming and costly field tests.
-CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).
+While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}.
+Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions.
+CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).\\
 
 Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}.
-The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boiler considerably affect the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.
+The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\
 
-Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%.
+Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%.
 The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances.
 Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler.
-A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions.
-The aforementioned reseacrh specifically investigated combustion and gas-side effects.
-However, to the best the authors' knowledge, no integration of 1-D process model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.
+A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions.
+The aforementioned research specifically investigated combustion and gas-side effects.\\
 
-The use of a 1-D process modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions.
-These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}.
-Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.
+Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions.
+These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}.
+Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy.
+However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
 
 The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model.
-Some recent papers that investigated boiler operations using a co-simulation approach are: Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}.
-Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.
+Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\
 
-The goal of the current work is to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flow-rates and metal temperatures.
-The current work proposes the use of CFD modelling  to investigate the low-load gas-side effects at various firing conditions for a 620 $MWe$ two-pass sub-critical boiler.
-For the current work CFD gas-side results are coupled to a comprehensive process model of the case study boilers water side.
+However, to the authors’ knowledge, the integration of a 1-D process model with a detail CFD model has not been used to investigate the steam side operational performance of a CFPP boiler specifically at low-load.
+The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\
 
-The model was simulated for a boiler load of 32 $\%$  with 6 various firing combinations.
-To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ maximum continuous rating (MCR) loads and compared to actual plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.
+To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements.
+Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.
 
 \section{Mathematical model}
-In this section the modelling techniques used by the study are briefly discussed.
 \subsection{Computational fluid dynamics modelling}
 \subsubsection{Fluid flow, turbulence and combustion modelling}
-The flue gas was modelled using a Eulerian framework.
+The flue gas-side was modelled using a Eulerian framework.
 The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase.
 This approach solves a species continuity equation for each constituent present in the mixture.
-To reduce the computational burden it was assumed that the various processes were in steady-state.
-The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
+To reduce the computational burden, it was assumed that the various processes were in steady-state.
+The governing equations for the gas phase are written below in their respective Reynolds.\\
 Mass conservation:
@@
 \end{equation}
-To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows;
+To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
 \begin{equation} \label{eqn_eff_rho}
@@
 
-In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem.
+In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem.
 This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners.
-The model generally produces higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.
+The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.\\
 
-The process of coal combustion comprises of four sequential steps.
-Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions.
+The process of coal combustion comprises of four sequential steps namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions.
 Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
@@
 
-A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.
+A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
+
 The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}).
@@
 
-The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate, and uses the minimum of the three for the source terms calculations.
+The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate.
+It then applies the minimum of the three for the source terms calculations.
 A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
@@
 \subsubsection{Particle modelling}
-The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.
+The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}.
+Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.
 The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}.
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash.
-Each of the scalar field equations are given in Table \ref{tab_scalars}.
+The scalar field equations are provided in Table \ref{tab_scalars}.\\
 
@@
 
-The energy transport of the pseudo particle phase, is transported by defining a particle phase energy equation, which in turn uses the particle enthalpy.
+The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
 \begin{equation}\label{eqn_phi_hp}
@@
 The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$.
-This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
+This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
@@
 
-\subsection{Heat transfer modelling modelling}
+\subsection{Heat transfer modelling}
 Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
@@
 \subsection{Process simulation model}
-A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021.
+A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021.
 The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls.
 The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit.
-The heat exchangers were modelled using a two-phase mixture approach, this assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area.
+The heat exchangers were modelled using a homogeneous two-phase mixture approach, which assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area.
 The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
@@
 
-The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case.
-The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various Cases have on the water-side of the boiler system.
+The process model is used to determine the required attemperation flow rates to achieve the exit steam conditions, boiler efficiency, and steam generation for each case.
+The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects on the water-side of the boiler system.
 
@@
 \subsection{Geometry \& process model set-up}
-The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], a width of 14.01 [$m$] and a height of 64 [$m$].
+The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], width of 14.01 [$m$] and height of 64 [$m$].
 The CFD geometric model (of Figure \ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace.
 This was done to reduce the cell count of the numerical mesh.
-Both the platen and final SH are modelled as walls, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively.
+Both the platen and final SH are modelled as solid wall panels, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively.
 There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$].
-Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domains outlet and inlets.\\
+Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.\\
 \begin{figure} [h!]
@@
 
-The boiler furnace is fed by 6 mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners.
-This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.
+The boiler furnace is fed by six mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of six burners.
+This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.\\
 
@@
 The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets.
-The process model is used to determine the required attemperation flow-rates and water/steam side thermal response.
-The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system which include the downcomers and steam drum.
-As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.
+The process model is used to determine the required attemperation flowrates and water/steam side thermal response.
+The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system that includes the downcomers and steam drum.
+As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.\\
 
-The coupling interface between the simulation models are the heat exchanger external tube surfaces, namely the furnace, platen and final SH walls.
+The coupling interface between the simulation models are the heat-exchanger external tube surfaces, namely the furnace, platen and final SH walls.
 The CFD heat loads are used as energy sources for these components as indicated in Figure \ref{fig_flownex}.
+The furnace heat load to the evaporator walls determines the circulation rate through the evaporator.
+The steam drum separates the gas from the liquid, with the liquid water being recirculated through the evaporator and the saturated vapour (steam) being sent through the main steam line for superheating.
+Thus the steam generation is calculated.
 Furthermore, the CFD flue-gas results (i.e.
-composition, mass flow and temperature) exiting the final SH are used as boundary inputs for the heat exchangers downstream of the final SH (SH3).
-The steam flow boundary values for the RH and EC sections are fixed mass inlet flows and temperatures with the corresponding outlets set to a fixed pressure.
-
+composition, mass flow and temperature) exiting the final SH are used as boundary values for the heat exchangers downstream of the final SH (SH3), as shown in Figure \ref{fig_flownex}.
+The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.
 \begin{figure}[h!]
@@
 
+Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Figure \ref{fig_flownex}).\\
+
+The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side.
+The total heat transferred to the water-side control volume can be written as the sum of the absorbed direct radiation and the combined convective and gas radiative heat transfer (i.e.
+$\dot{Q}_{steam}=\dot{Q}_{abs}+\dot{Q}_{cr}$).
+The external heat transfer coefficient, from the flue-gas to the heat-exchanger walls makes use of the Gnielinski correlation \cite{Gnielinski2016} for the various heat-exchanger tube arrangements.
+Figure \ref{fig_heat_exchanger_model} incorporates the direct radiative interactions in each heat-exchanger.
+It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
+\begin{figure}[h!]
+\centerline{\includegraphics[scale=0.5]{HEAT_EXCHANGER_PROCESS_MODEL}}
+\caption{Heat-exchanger component model}
+\label{fig_heat_exchanger_model}
+\end{figure}
+
 \newpage
 \subsection{Model inputs}
-Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the fuels higher heating value (HHV).\\
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.\\
 \begin{table}[h!]
@@
 
-For a 32 \% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.
-For this study six Cases are simulated in total with the following three burner firing configurations being investigated:
+For a boiler load 32\% MCR the current operational protocol is to use the bottom front and rear burner rows to meet the low-load demand during start-up.
+For this study six cases are simulated with the following three burner firing configurations being investigated:
 \begin{enumerate}
@@
 
-Typically 5 [$kg/s$] of air is fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
-The result is a high air-fuel ratio in the furnace which leads to higher dry gas losses.
-to lower this loss, this study will investigate the affect of reducing the air-fuel ratio by lowering the non-firing burner SA flow-rate from 5 to 2.5 [$kg/s$].
-Two permutations of the SA flow rate, at the non-firing burners, are used for each of the firing configurations mentioned above.
+A secondary air flo rate of 5 [$kg/s$] is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
+The result is a high air-fuel ratio in the furnace, which leads to higher dry gas losses.
+To lower this loss, this study will investigate the effect of reducing the air-fuel ratio by lowering the non-firing burner SA flowrate from 5 to 2.5 [$kg/s$].
+Two permutations of the SA flowrate, at the non-firing burners, are used for each of the firing configurations mentioned above.
 Table \ref{tbl_case_inputs} shows the input conditions for Cases 1 to 6.
-The data is the result of a boilers mass and energy balance calculation.
+This data was obtained via conventional boiler mass and energy balance calculations.
 
@@
 \hline
-\textbf{Fuel flow-rate} [$kg/s$]&3.14  &3.14\\
-\textbf{PA flow-rate} [$kg/s$]&4.95  &4.95\\
-\textbf{SA flow-rate} [$kg/s$]&14.85  &14.85\\
+\textbf{Fuel flowrate} [$kg/s$]&3.14  &3.14\\
+\textbf{PA flowrate} [$kg/s$]&4.95  &4.95\\
+\textbf{SA flowrate} [$kg/s$]&14.85  &14.85\\
 \hline
@@
 \hline
-\textbf{SA flow-rate} [$kg/s$]&5.0  &2.5\\
+\textbf{SA flowrate} [$kg/s$]&5.0  &2.5\\
 \hline
@@
 The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
-For all Cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flow-rate of 190 [$kg/s$] and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
+For all cases the maximum mass imbalance was 0.024 [$kg/s$] for a total gas flowrate of 190 [$kg/s$], and a heat imbalance of 1770 [$kW$] for a total heat input of 283 [$MW$].
 The remaining fields were solved till convergence.
@@
 \subsection{Model validation}\label{sec_model_valid}
-The validation of the proposed model was conducted for three steady-state MCR loads of 100 \%, 80 \% and 60 \%, where actual plant measurements are used to calculate the
-thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
+The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\% respectively.
+Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
 The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
@@
 \begin{figure}[h!]
-	\subfigure[100 \% MCR]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
-	\subfigure[80 \% MCR]{\includegraphics[width=0.32\textwidth]{80_VALID_BAR}}
-	\subfigure[60 \% MCR]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
+\centerline{
+	\subfigure[100\% MCR]{\includegraphics[width=0.4\textwidth]{100_VALID_BAR}}
+	\subfigure[80\% MCR]{\includegraphics[width=0.4\textwidth]{80_VALID_BAR}}
+	\subfigure[60\% MCR]{\includegraphics[width=0.4\textwidth]{60_VALID_BAR}}}
 \caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
@@
 \clearpage
-In Figure \ref{fig_heat_valid} it is shown that the overall heat loads are in good agreement with the calculated results.
-For the simulated validation loads the proposed model results are within the associated error band, the general trend is an under prediction on the furnace heat loads, with a maximum percentage error of 2 \%, and an over prediction on the platen SH, with a maximum percentage error of 7 \% .
-The pendant SH illustrate the best comparable results for all load Cases.
+Figure \ref{fig_heat_valid} shows that the calculated overall heat loads are in good agreement with the measured values where the model results are within the associated uncertainty range in all but one case.
+The simulation systematically under predicts the furnace heat loads, with a maximum percentage error of 2\%, while predominating overpredicting the platen SH loads, with a maximum percentage error of 7\%.\\
 
 The CFD model was further validated by comparing the $CO_{ppm}$ and $X_{O_{2}}$ measurements against the CFD results.
-The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during a full load (100\% MCR) operating conditions.
-The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$].\\
+The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during full load (100\% MCR) operating conditions.
+The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].\\
 \begin{figure}[h!]
@@
 \subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
-\caption{Experimentally calculated $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentration predictions}
+\caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
 \label{fig_probe_valid}
@@
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
-It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
+It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.
 \newpage
@@
 The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-When the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
+With the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
 This is further exacerbated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
@@
 \hline
-\textbf{Main steam flow-rate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
 \textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
@@
 Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
-An even distribution of unit heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
-Cases 2 and 5 show that most of the unit heat fluxes are absorbed in the upper half of the boiler with case 5 showing a higher heat flux on the rear wall.
-This could be due the use of a lower SA flow-rate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
-With this is mind a lower SA flow-rate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.
+An even distribution of heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
+Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
+This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
+With this is mind a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
 
@@
 The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
-For low-load operation this phenomena becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
+For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
 Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
 The figures generally highlight the location and distribution of the flame core for each case.
-Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.\\
 
@@
 
-Investigating the combustion stability for all the Cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
+Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
 Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
@@
 Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
-It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
+It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
 
@@
 \end{table}
-The external tube metal temperatures, of Table \ref{tbl_cfd_results}, were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
+The external tube metal temperatures, shown in Table \ref{tbl_cfd_results} were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
 Fouling thermal resistances of 0.0067 and 0.015 [$m^2K/W$] were used for the platen and final SH respectively.
@@
 \end{equation}
+
 For the platen and final SH the maximum surface temperature are observed for Cases 2 and 5.
-For comparison at 100 \% MCR load the maximum and mean temperatures reported for the platen and final SH are 500 \& 446 $[^\circ C]$ and 623 \& 531 $[^\circ C]$ respectively, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
-Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.
+For comparison, at 100\% MCR load the maximum and mean temperatures reported for the platen and final SH are 500 \& 446 $[^\circ C]$ and 623 \& 531 $[^\circ C]$ respectively, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
+Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.\\
 
@@
 Table \ref{tbl_process_parameters} summarizes the results with the highest boiler efficiencies observed for Cases 3 and 6.
-With a lower SA flow-rate Cases 4 to 6 exhibit a higher boiler efficiency due to the decrease in dry gas losses, when compared to Cases 1 to 3.
-All Cases exhibit adequate control of the main steam exit temperature by use of ATT1 and ATT2.
+With a lower SA flowrate Cases 4 to 6 exhibit a higher boiler efficiency due to the decrease in dry gas losses, when compared to Cases 1 to 3.
+All cases exhibit adequate control of the main steam exit temperature by use of ATT1 and ATT2.
 The exit temperature of the reheaters, for all Cases, are determined to within the 20 [$^\circ C$] tolerance for the intermediate turbine inlet conditions, as stipulated in the design C-schedules for the plant.
-However, with the lack of ATT-RH control, a sudden decreases in steam generation can lead to RH overheating and possible RH failure.
-Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load 32 \% MCR.
+However, with the lack of ATT-RH control, a sudden decrease in steam generation can lead to RH overheating and possible RH failure.
+Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.\\
 
-Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat exchanger for Cases 3 and 6.
-It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10 \% being transferred to convection at low-load.
+Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
+It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10\% being transferred via convection at low-load.
 Considering the convective pass heat exchangers (RH2 through to the EC, refer to Figure \ref{fig_flownex}) the convective heat transfer becomes more apparent as seen with the reduction in radiative heat transfer percentage.
-Case 6 tends to exhibit less convective heat transfer for the said  heat exchangers, due to the fact of a lower SA flow-rate for non-firing burners.
-This will reduce the total amount of flue-gas flowing through the boiler, for the same cross flow-area and similar density the velocity would be expected to drop, reducing the convective heat transfer.
+Case 6 involves less convective heat transfer due to the SA flowrate for non-firing burners.
+This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
 
@@
 \section{Conclusions}
-The present study demonstrates the use of a coupled simulation used to study the effects of burner configuration at a boiler load of 32 \% MCR.
-A validation case was performed for the developed CFD model which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
+The present study demonstrates the use of a coupled CFD/process model to study the effects of burner configuration at a boiler load of 32\% MCR.
+A validation case was first performed for the CFD model, which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
 The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.
+\\
 
-The results show that using a burner arrangement that raises the position of the flame core (Cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
-Subsequently, this firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream potentially leading to economic losses, regarding the efficient combustion of the fuel and the lowest boiler utilization efficiency.
+The subsequent analysis results show that using a burner arrangement that raises the position of the flame core (Cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
+This firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream and therefore the lowest boiler utilization efficiency.\\
 
-Operation of the boiler using firing arrangements of Cases 1 and 4, in relation to Cases 3 and 6 results in lower boiler utilization efficiency and exit flue-gas temperature.
-Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high possibility of fire side corrosion occurring at continuous low-load operation using Cases 1 and 4.
+Operation of the boiler using firing arrangements of Cases 1 and 4 also results in a lower boiler utilization efficiency and exit flue-gas temperature compared to Cases3 and 6.
+Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high risk of fire side corrosion occurring at continuous low-load operation.\\
 
-The mixed firing arrangement, of case 3 and 6, exhibits the best boiler utilization efficiency overall.
-A 4.8 \% decrease in unburnt carbon percentage is observed when operating using case 3 in relation to case 6.
-The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $[^\circ C]$, allowing for better control.
+The mixed firing arrangements, of Cases 3 and 6, exhibit the best boiler utilization efficiencies.
+A 4.8\% decrease in unburnt carbon percentage is observed when operating using Case 3 in relation to Case 6.
+The predicted re-heater exit steam temperature of Case 3 is substantially closer to the desired temperature of 535 $[^\circ C]$, thus allowing for better control.\\
 
-Based on the current numerical study, carried out to determine the most favourable operating parameters and combustion stability, case 3 is seen as the optimal firing arrangement for the boiler under consideration.
+Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, Case 3 is considered to be the best operational strategy at this low load for the boiler under investigation.
 

### 2021-11-05 PAPER_2/PAPER_2_REV1.tex
Update - 05/11/2021

@@
 
-\journal{Energy}
+\makeatletter
+\def\ps@pprintTitle{%
+ \let\@oddhead\@empty
+ \let\@evenhead\@empty
+ \def\@oddfoot{\centerline{\thepage}}%
+ \let\@evenfoot\@oddfoot}
+\makeatother
 
@@
 
-\title{Numerical investigation of low-load operation of a subcritical power boiler using CFD and process modelling}
+\title{Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.}
 
 %% Group authors per affiliation:
-\author{B.T. Rawlins}
-\author{R. Laubscher\corref{mycorrespondingauthor}}
+\author{B.T. Rawlins $^{a}$ \corref{mycorrespondingauthor}}
 \cortext[mycorrespondingauthor]{Corresponding author}
-\ead{rlaubscher@sun.ac.za}
-\author{P. Rousseau}
-\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
-\address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}
+\ead{rwlbra001@myuct.ac.za}
+\author{R. Laubscher $^b$}
+\author{P. Rousseau $^a$}
+\address{$^a$ Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
+\address{$^b$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}
 
 \begin{abstract}
+To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation.
 Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model.
@@
 \nomenclature{\mbox{}}{}
-%\linenumbers
+\linenumbers
 \section{Introduction}
@@
 However, with the lack of ATT-RH control, a sudden decrease in steam generation can lead to RH overheating and possible RH failure.
-Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.\\
-
-Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
-It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10\% being transferred via convection at low-load.
-Considering the convective pass heat exchangers (RH2 through to the EC, refer to Figure \ref{fig_flownex}) the convective heat transfer becomes more apparent as seen with the reduction in radiative heat transfer percentage.
-Case 6 involves less convective heat transfer due to the SA flowrate for non-firing burners.
-This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
+Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.
 
@@
 
-\clearpage
+Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
+It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10\% being transferred via convection at low-load.
+Considering the convective pass heat exchangers (RH2 through to the EC, refer to Figure \ref{fig_flownex}) the convective heat transfer becomes more apparent as seen with the reduction in radiative heat transfer percentage.
+Case 6 involves less convective heat transfer due to the SA flowrate for non-firing burners.
+This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
+
 \section{Conclusions}

### 2022-01-19 ASME_journal/journal-1.1 REVISION/JOURNAL_MANUSCRIPT_BRAD_RAWLINS.tex
Update 2 19/01/2022

--- 2021-11-05 PAPER_2/PAPER_2_REV1.tex
@@
-\documentclass[review]{elsarticle}
-\usepackage[utf8]{inputenc} 
-\usepackage{lineno,hyperref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Template for producing ASME-format journal articles using LaTeX    %
+% Written by   Harry H. Cheng, Professor and Director                %
+%              Integration Engineering Laboratory                    %
+%              Department of Mechanical and Aeronautical Engineering %
+%              University of California                              %
+%              Davis, CA 95616                                       %
+%              Tel: (530) 752-5020 (office)                          %
+%                   (530) 752-1028 (lab)                             %
+%              Fax: (530) 752-4158                                   %
+%              Email: hhcheng@ucdavis.edu                            %
+%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
+%              May 7, 1994                                           %
+% Modified: February 16, 2001 by Harry H. Cheng                      %
+% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
+% Use at your own risk, send complaints to /dev/null                 %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% use twocolumn and 10pt options with the asme2ej format
+\documentclass[twocolumn,10pt]{asme2ej}
+
+\usepackage{graphicx} %% for loading jpg figures
 \usepackage{tabu}
@@
 \usepackage{subfigure}
-\usepackage[fleqn]{amsmath}
-\modulolinenumbers[5]
+\usepackage{amsmath}
+\usepackage{multicol}
+\usepackage{color,soul}
+\usepackage{xcolor}
 
-\usepackage{framed}
-\usepackage{multicol} % Multiple columns environment
+\newcommand{\highlight}[1]{%
+  \colorbox{yellow!}{$\displaystyle#1$}}
+%% The class has several options
+%  onecolumn/twocolumn - format for one or two columns per page
+%  10pt/11pt/12pt - use 10, 11, or 12 point font
+%  oneside/twoside - format for oneside/twosided printing
+%  final/draft - format for final/draft copy
+%  cleanfoot - take out copyright info in footer leave page number
+%  cleanhead - take out the conference banner on the title page
+%  titlepage/notitlepage - put in titlepage or leave out titlepage
+%  
+%% The default is oneside, onecolumn, 10pt, final
 
-\usepackage{nomencl} % Nomenclature package
-\makenomenclature
-\setlength{\nomitemsep}{0pt}
+\title{Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.}
 
-\newcommand{\nomunit}[1]{%
-  \renewcommand{\nomentryend}{\hspace*{\fill}#1}%
+%%% first author
+\author{Brad T. Rawlins\thanks{Corresponding author}
+    \affiliation{
+	Ph.D. Candidate\\
+	Department of Mechanical \\Engineering\\
+	University of Cape Town\\
+    Email: rwlbra001@myuct.ac.za
+    \vspace{5mm}
     }
 
-\renewcommand\nomgroup[1]{% 
-  \item[\bfseries
-  \ifstrequal{#1}{A}{Symbols}{%
-  \ifstrequal{#1}{B}{Greek symbols}{%
-  \ifstrequal{#1}{C}{Abbreviations}{}}}%
-]}
+}
 
-\makeatletter
-\def\ps@pprintTitle{%
- \let\@oddhead\@empty
- \let\@evenhead\@empty
- \def\@oddfoot{\centerline{\thepage}}%
- \let\@evenfoot\@oddfoot}
-\makeatother
+%%% second author
+%%% remove the following entry for single author papers
+%%% add more entries for additional authors
+\author{Ryno Laubscher 
+    \affiliation{Associate Professor\\
+    Department of Mechanical \\Engineering\\
+	Stellenbosch University\\
+    Email: rlaubscher@sun.ac.za
+    }
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%
+%%% third author
+%%% remove the following entry for single author papers
+%%% add more entries for additional authors
+\author{Pieter Rousseau
+    \affiliation{Professor\\
+        Department of Mechanical \\Engineering\\
+        University of Cape Town\\
+        Email: pieter.rousseau@uct.ac.za
+    }
+}
 
@@
 
-\begin{frontmatter}
+\maketitle
 
-\title{Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.}
-
-%% Group authors per affiliation:
-\author{B.T. Rawlins $^{a}$ \corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{rwlbra001@myuct.ac.za}
-\author{R. Laubscher $^b$}
-\author{P. Rousseau $^a$}
-\address{$^a$ Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
-\address{$^b$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
-To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation.
+{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation.
 Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model.
@@
 Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
+}
 \end{abstract}
 
-\begin{keyword}
-CFD\sep Boiler \sep Low-load operation \sep Co-simulation
-\end{keyword}
-\newpage
-\end{frontmatter}
-
-\printnomenclature
-
-\nomenclature[A]{$A$}{Area \nomunit{$m^2$}}
-\nomenclature[A]{$A_p$}{Particle surface area \nomunit{$m^2$}}
-\nomenclature[A]{$A_{pn}$}{Projected particle surface area \nomunit{$m^2$}}
-\nomenclature[A]{$A_{c}$}{Carbon pre-exponential factor \nomunit{$s^{-1}$}}
-\nomenclature[A]{$A_{vol}$}{Volatile pre-exponential factor \nomunit{$s^{-1}$}}
-\nomenclature[A]{$d_p$}{Particle diameter \nomunit{$m$}}
-\nomenclature[A]{$E$}{Fluid total energy \nomunit{$J/kg$}}
-\nomenclature[A]{$E_{a,c}$}{Carbon activation energy \nomunit{$J/kmol$}}
-\nomenclature[A]{$E_{a,vol}$}{Volatile activation energy \nomunit{$J/kmol$}}
-\nomenclature[A]{$E_p$}{Particle emission power \nomunit{$W/m^3$}}
-\nomenclature[A]{$f_{heat}$}{Near surface char oxidation fraction \nomunit{$-$}}
-\nomenclature[A]{$f_{p}$}{Forward scattering factor \nomunit{$-$}}
-\nomenclature[A]{$G$}{Incident radiation \nomunit{$W/m^2$}}
-\nomenclature[A]{$g$}{Gravitational constant \nomunit{$m/s^2$}}
-\nomenclature[A]{$h_{fg}$}{Enthalpy of evaporation \nomunit{$J/kg$}}
-\nomenclature[A]{$h_M$}{Mixture enthalpy \nomunit{$J/kg$}}
-\nomenclature[A]{$h_{rxn}$}{Enthalpy of reaction \nomunit{$J/kg$}}
-\nomenclature[A]{$J_k$ }{Species diffusion flux \nomunit{$m^2/s$}}
-\nomenclature[A]{$m_{0,vol}$}{Original mass of volatiles \nomunit{$kg$}}
-\nomenclature[A]{$m_{char}$}{Mass of carbon \nomunit{$kg$}}
-\nomenclature[A]{$m_{evap}$}{Mass of moisture \nomunit{$kg$}}
-\nomenclature[A]{$m_{vol}$}{Mass of volatiles \nomunit{$kg$}}
-\nomenclature[A]{$N_{p}$}{Number of particles \nomunit{$-$}}
-\nomenclature[A]{$P$}{Perimeter \nomunit{$m$}}
-\nomenclature[A]{$p$}{Pressure \nomunit{$Pa$}}
-\nomenclature[A]{$p_{O_{2}}$}{Partial pressure of $O_2$ \nomunit{$Pa$}}
-\nomenclature[A]{$\dot{Q}_{conv}$}{Convective heat transfer rate \nomunit{$W$}}
-\nomenclature[A]{$\dot{Q}_{rad}$}{Radiative heat transfer rate \nomunit{$W$}}
-\nomenclature[A]{$\dot{Q}_{w}$}{Wall heat transfer rate \nomunit{$W$}}
-\nomenclature[A]{$R$}{Universal gas constant \nomunit{$J/molK$}}
-\nomenclature[A]{$R_{c}$}{Carbon reaction rate \nomunit{$s^{-1}$}}
-\nomenclature[A]{$R_{diff}$}{Diffusion reaction rate \nomunit{$s^{-1}$}}
-\nomenclature[A]{$R_{vol}$}{Volatile reaction rate \nomunit{$s^{-1}$}}
-\nomenclature[A]{$T_g$}{Gas temperature \nomunit{$K$}}
-\nomenclature[A]{$T_p$}{Particle temperature \nomunit{$K$}}
-\nomenclature[A]{$t$}{Time \nomunit{$s$}}
-\nomenclature[A]{$u$}{Velocity \nomunit{$m/s$}}
-\nomenclature[A]{$V$}{Volume \nomunit{$m^3$}}
-\nomenclature[A]{$Y_k$}{Species mass fraction \nomunit{$kg/kg$}}
-\nomenclature[A]{$x$}{Quality \nomunit{$-$}}
-\nomenclature[B]{$\alpha_g$}{Gas absorption coefficient \nomunit{$m^{-1}$}}
-\nomenclature[B]{$\alpha_H$}{Mixture void fraction \nomunit{$-$}}
-\nomenclature[B]{$\alpha_p$}{Particle absorption coefficient \nomunit{$m^{-1}$}}
-\nomenclature[B]{$\epsilon_p$}{Particle emissivity \nomunit{$-$}}
-\nomenclature[B]{$\rho$}{Gas density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\rho_{eff}$}{Effective density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\rho_g$}{Gas density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\rho_l$}{Liquid density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\rho_M$}{Mixture density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\rho_p$}{Particle density \nomunit{$kg/m^3$}}
-\nomenclature[B]{$\sigma_{SB}$}{Stefan-Boltzmann constant \nomunit{$W/m^2K^4$}}
-\nomenclature[B]{$\sigma_{p}$}{Particle scattering coefficient \nomunit{$m^{-1}$}}
-\nomenclature[B]{$\phi$}{Scalar variable \nomunit{$-$}}
-\nomenclature[C]{$MCR$}{Maximum continuous rating}
-\nomenclature[C]{$CFPP$}{Coal fired power plant}
-\nomenclature[C]{$CFD$}{Computational fluid dynamics}
-\nomenclature[C]{$SH$}{Superheater}
-\nomenclature[C]{$EE$}{Eulerian-Eulerian}
-\nomenclature[C]{$WSGGM$}{Weighted sum of gray gas model}
-\nomenclature[C]{$RTE$}{Radiative transport equation}
-\nomenclature[C]{$HHV$}{Higher heating value}
-\nomenclature[C]{$DAF$}{Dry ash free}
-\nomenclature[C]{$AR$}{As-received}
-\nomenclature[C]{$PA$}{Primary air}
-\nomenclature[C]{$SA-AH$}{Secondary air - air heater}
-\nomenclature[C]{$SA$}{Secondary air}
-\nomenclature[C]{$RH$}{Reheater}
-\nomenclature[C]{$ATT$}{Attemperator}
-\nomenclature[C]{$EC$}{Economiser}
-\nomenclature{\mbox{}}{}
-\linenumbers
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{nomenclature}
+\entry{}{\textit{Variables}}
+\entry{$A$}{Area [$m^2$]}
+\entry{$A_p$}{Particle surface area [$m^2$]}
+\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
+\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
+\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
+\entry{$d_p$}{Particle diameter [$m$]}
+\entry{$E$}{Fluid total energy [$J/kg$]}
+\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
+\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
+\entry{$E_p$}{Particle emission power [$W/m^3$]}
+\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
+\entry{$f_{p}$}{Forward scattering factor [$-$]}
+\entry{$G$}{Incident radiation [$W/m^2$]}
+\entry{$g$}{Gravitational constant [$m/s^2$]}
+\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
+\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
+\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
+\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
+\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
+\entry{$m_{char}$}{Mass of carbon [$kg$]}
+\entry{$m_{evap}$}{Mass of moisture [$kg$]}
+\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
+\entry{$N_{p}$}{Number of particles [$-$]}
+\entry{$P$}{Perimeter [$m$]}
+\entry{$p$}{Pressure [$Pa$]}
+\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
+\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
+\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
+\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
+\entry{$R$}{Universal gas constant [$J/molK$]}
+\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
+\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
+\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
+\entry{$S$}{\hl{Mass source term}[$kg/m^3$]}
+\entry{$S_m$}{\hl{Momentum source term} [$/m^3$]}
+\entry{$S_h$}{\hl{Energy source term} [$W/m^3$]}
+\entry{$S_k$}{\hl{Species source term} [$kg/m^3$]}
+\entry{$T_g$}{Gas temperature [$K$]}
+\entry{$T_p$}{Particle temperature [$K$]}
+\entry{$t$}{Time [$s$]}
+\entry{$u$}{Velocity [$m/s$]}
+\entry{$V$}{Volume [$m^3$]}
+\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
+\entry{$x$}{Quality [$-$]}
+\entry{}{\textit{Greek Variables}}
+\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
+\entry{$\alpha_H$}{Mixture void fraction [$-$]}
+\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
+\entry{$\epsilon_p$}{Particle emissivity [$-$]}
+\entry{$\rho$}{Gas density [$kg/m^3$]}
+\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
+\entry{$\rho_g$}{Gas density [$kg/m^3$]}
+\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
+\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
+\entry{$\rho_p$}{Particle density [$kg/m^3$]}
+\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
+\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
+\entry{$\phi$}{Scalar variable [$-$]}
+\entry{}{\textit{Abbreviations}}
+\entry{$MCR$}{Maximum continuous rating}
+\entry{$CFPP$}{Coal fired power plant}
+\entry{$CFD$}{Computational fluid dynamics}
+\entry{$SH$}{Superheater}
+\entry{$EE$}{Eulerian-Eulerian}
+\entry{$WSGGM$}{Weighted sum of gray gas model}
+\entry{$RTE$}{Radiative transport equation}
+\entry{$HHV$}{Higher heating value}
+\entry{$DAF$}{Dry ash free}
+\entry{$AR$}{As-received}
+\entry{$PA$}{Primary air}
+\entry{$SA-AH$}{Secondary air - air heater}
+\entry{$SA$}{Secondary air}
+\entry{$RH$}{Reheater}
+\entry{$ATT$}{Attemperator}
+\entry{$EC$}{Economiser}
+\end{nomenclature}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions.
-CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).\\
+CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).\\
 
 Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}.
-The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\
+The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\
 
@@
 The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances.
-Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler.
+Similarly, Chang et al \cite{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler.
 A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions.
@@
 However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
-
+\newpage
 The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model.
@@
 To reduce the computational burden, it was assumed that the various processes were in steady-state.
-The governing equations for the gas phase are written below in their respective Reynolds.\\
+\hl{The governing equations for the gas phase are written below in their respective Reynolds averaged forms}.\\
 Mass conservation:
 \begin{equation}\label{eqn_RANS_mass}
-\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
+\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=\highlight{S}
 \end{equation}
@@
 \begin{equation}\label{eqn_momentum}
-\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
+\begin{split}
+&\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\\
+&\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
+\end{split}
 \end{equation}
@@
 \end{equation}
+
 To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
@@
 
-A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
-
+A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
+\newpage
 The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}).
@@
 \end{gather}
-The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
+The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
 \begin{gather}
@@
 \vspace{2mm}     
-\begin{tabular}{lll}
+\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabularx}
 \end{table}
@@
 \begin{equation}\label{eqn_phi_hp}
-\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
+\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=\left( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg} \right) \frac{1}{V} 
 \end{equation}
@@
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
-To solve the additional transport equations and their source terms, C programs were developed.
+\hl{To solve the additional transport equations and their source terms user defined functions, utilized by ANSYS Fluent, were developed using the C programming language.}
 
 \subsection{Heat transfer modelling}
-Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
+Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
 \begin{equation}\label{eqn_RTE}
-\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\begin{split}
+&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
+&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\end{split}
 \end{equation}
@@
 
-It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \citep{Yin2015} respectively.
-
+It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
+\begin{figure*} 
+\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
+\caption{Boiler geometry and layout}
+\label{fig_geometry}
+\end{figure*}
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.5]{FLOWNEX_SETUP}
+\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
+\label{fig_flownex}
+\end{figure*}
 \subsection{Process simulation model}
@@
 \begin{split}
-&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\\&\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
+&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\\
+&\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
 \end{split}
@@
 Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.\\
-\begin{figure} [h!]
-\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
-\caption{Boiler geometry and layout}
-\label{fig_geometry}
-\end{figure}
 
@@
 composition, mass flow and temperature) exiting the final SH are used as boundary values for the heat exchangers downstream of the final SH (SH3), as shown in Figure \ref{fig_flownex}.
-The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.5]{FLOWNEX_SETUP}
-\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
-\label{fig_flownex}
-\end{figure}
+The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.\\
 
@@
 It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
-\begin{figure}[h!]
-\centerline{\includegraphics[scale=0.5]{HEAT_EXCHANGER_PROCESS_MODEL}}
+\begin{figure*}[h!]
+\centerline{\includegraphics[scale=0.4]{HEAT_EXCHANGER_PROCESS_MODEL}}
 \caption{Heat-exchanger component model}
 \label{fig_heat_exchanger_model}
-\end{figure}
+\end{figure*}
 
-\newpage
 \subsection{Model inputs}
 Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.\\
+
 \begin{table}[h!]
@@
 \label{tbl_fuel}
-{\tabulinesep=1.2mm
-\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
+\begin{tabularx}{3.25in}{p{1.5in} p{0.8in} l}
 \hline
@@
 \hline
-\end{tabularx}}
+\vspace{0pt}
+\end{tabularx}
 \end{table}
@@
 \end{enumerate}
-
-A secondary air flo rate of 5 [$kg/s$] is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
-The result is a high air-fuel ratio in the furnace, which leads to higher dry gas losses.
-To lower this loss, this study will investigate the effect of reducing the air-fuel ratio by lowering the non-firing burner SA flowrate from 5 to 2.5 [$kg/s$].
-Two permutations of the SA flowrate, at the non-firing burners, are used for each of the firing configurations mentioned above.
-Table \ref{tbl_case_inputs} shows the input conditions for Cases 1 to 6.
-This data was obtained via conventional boiler mass and energy balance calculations.
-
 \begin{table}[h!]
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.25\textwidth} l}
+\begin{tabularx}{3.25in}{p{1.25in} p{1in} l}
 \hline
@@
 \end{tabularx}}
+\vspace{0pt}
 \end{table}
+
+A secondary air flow rate of 5 [$kg/s$] is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
+The result is a high air-fuel ratio in the furnace, which leads to higher dry gas losses.
+To lower this loss, this study will investigate the effect of reducing the air-fuel ratio by lowering the non-firing burner SA flowrate from 5 to 2.5 [$kg/s$].
+Two permutations of the SA flowrate, at the non-firing burners, are used for each of the firing configurations mentioned above.
+Table \ref{tbl_case_inputs} shows the input conditions for Cases 1 to 6.
+This data was obtained via conventional boiler mass and energy balance calculations.
 
@@
 was used to discretize the pressure equation.
-The scalar field equations used a second-order upwind scheme.
+The scalar field equations used a second-order upwind scheme.\\
 
@@
 Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
-The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
+The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \cite{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.\\
 
-\begin{figure}[h!]
-\centerline{
-	\subfigure[100\% MCR]{\includegraphics[width=0.4\textwidth]{100_VALID_BAR}}
-	\subfigure[80\% MCR]{\includegraphics[width=0.4\textwidth]{80_VALID_BAR}}
-	\subfigure[60\% MCR]{\includegraphics[width=0.4\textwidth]{60_VALID_BAR}}}
-\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
-\label{fig_heat_valid}
-\end{figure}
-\clearpage
 Figure \ref{fig_heat_valid} shows that the calculated overall heat loads are in good agreement with the measured values where the model results are within the associated uncertainty range in all but one case.
@@
 The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].\\
+
+\begin{figure*}[h]
+\centerline{\includegraphics[scale = 0.4]{VALIDATION}}
+\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
+\label{fig_heat_valid}
+\end{figure*}
 \begin{figure}[h!]
 \centering
-\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{COPPM_VALID}}
+\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{COPPM_VALID}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
+\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{XO2_VALID}}
 \caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
@@
 \end{figure}
-
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
 It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.
-\newpage
+
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
@@
 The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}).
-This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Table \ref{tbl_process_parameters}.
+This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Table \ref{tbl_process_parameters}.\\
 
-\begin{figure}[h!]
+\begin{figure*}[h!]
 \centering
-\includegraphics[scale = 0.45]{TEMP_KEY} [$K$]\\
-\subfigure[Case 1]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
-\subfigure[Case 2]{\includegraphics[width=0.32\textwidth]{MID_TEMP}}
-\subfigure[Case 3]{\includegraphics[width=0.32\textwidth]{FBRM_TEMP}}\\
-\subfigure[Case 4]{\includegraphics[width=0.32\textwidth]{BOT05_TEMP}}
-\subfigure[Case 5]{\includegraphics[width=0.32\textwidth]{MID05_TEMP}}
-\subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
+\includegraphics[width = 5in]{TEMP_KEY} [$K$]\\
+\subfigure[Case 1]{\includegraphics[width=0.25\textwidth]{BOT_TEMP}}
+\subfigure[Case 2]{\includegraphics[width=0.25\textwidth]{MID_TEMP}}
+\subfigure[Case 3]{\includegraphics[width=0.25\textwidth]{FBRM_TEMP}}\\
+\subfigure[Case 4]{\includegraphics[width=0.25\textwidth]{BOT05_TEMP}}
+\subfigure[Case 5]{\includegraphics[width=0.25\textwidth]{MID05_TEMP}}
+\subfigure[Case 6]{\includegraphics[width=0.25\textwidth]{FBRM05_TEMP}}
 \caption{Temperature fields for Cases 1 through 6 [(a)-(f)]}
 \label{fig_cfd_temp}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h!]
+\begin{figure*}[h!]
 \centering
-\includegraphics[scale = 0.45]{VEL_KEY} [$m/s$]\\
-\subfigure[Case 1]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
-\subfigure[Case 2]{\includegraphics[width=0.32\textwidth]{MID_VEL}}
-\subfigure[Case 3]{\includegraphics[width=0.32\textwidth]{FBRM_VEL}}\\
-\subfigure[Case 4]{\includegraphics[width=0.32\textwidth]{BOT05_VEL}}
-\subfigure[Case 5]{\includegraphics[width=0.32\textwidth]{MID05_VEL}}
-\subfigure[Case 6]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
+\includegraphics[width = 5in]{VEL_KEY} [$m/s$]\\
+\subfigure[Case 1]{\includegraphics[width=0.25\textwidth]{BOT_VEL}}
+\subfigure[Case 2]{\includegraphics[width=0.25\textwidth]{MID_VEL}}
+\subfigure[Case 3]{\includegraphics[width=0.25\textwidth]{FBRM_VEL}}\\
+\subfigure[Case 4]{\includegraphics[width=0.25\textwidth]{BOT05_VEL}}
+\subfigure[Case 5]{\includegraphics[width=0.25\textwidth]{MID05_VEL}}
+\subfigure[Case 6]{\includegraphics[width=0.25\textwidth]{FBRM05_VEL}}
 \caption{Velocity fields for Cases 1 through 6 [(a)-(f)]}
 \label{fig_cfd_velo}
-\end{figure}
-
-\begin{table}[h!]
-\centering
-\caption{Process model control parameters}
-\vspace{2mm}
-{\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
-\hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
-\hline
-\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
-\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
-\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
-\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
-\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
-\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
-\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
-\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
-\hline
-\label{tbl_process_parameters}
-\end{tabularx}}
-\end{table}
-
-Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
-Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{Du2017}.
-An even distribution of heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
-Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
-This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
-With this is mind a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale = 0.45]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[Case 1]{\includegraphics[scale = 0.35]{BOT_HEATFLUX}}
-\hspace{5mm}
-\subfigure[Case 2]{\includegraphics[scale = 0.35]{MID_HEATFLUX}}
-\hspace{5mm}
-\subfigure[Case 3]{\includegraphics[scale = 0.35]{FBRM_HEATFLUX}}\\
-\subfigure[Case 4]{\includegraphics[scale = 0.29]{BOT05_HEATFLUX}}
-\hspace{5mm}
-\subfigure[Case 5]{\includegraphics[scale = 0.35]{MID05_HEATFLUX}}
-\hspace{5mm}
-\subfigure[Case 6]{\includegraphics[scale = 0.35]{FBRM05_HEATFLUX}}
-\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
-\label{fig_cfd_heat_flux}
-\end{figure}
-
-The works of Dugum et al \citep{Du2017}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
-For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
-Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
-The figures generally highlight the location and distribution of the flame core for each case.
-Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.\\
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.45]{CO_MF_KEY} [$X_{CO}$] \\
-\subfigure[Case 1]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
-\subfigure[Case 2]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
-\subfigure[Case 3]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
-\subfigure[Case 4]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
-\subfigure[Case 5]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
-\subfigure[Case 6]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
-\caption{CO molar fraction ($X_{CO}$) concentrations for 
-Cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
-\label{fig_cfd_coppm}
-\end{figure}
-
-Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
-Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
-The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
-With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the flame core is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
-Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
-It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
-
-\begin{figure}[h!]
-\centering
-\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.36]{SYMMETRY_PROBE_COPPM}}
-\hspace{5mm}
-\subfigure[Offset vertical plot]{\includegraphics[scale = 0.36]{OFFSET_PROBE_COPPM}}\\
-\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.35]{SYMMETRY_PROBE_XO2}}
-\hspace{5mm}
-\subfigure[Offset vertical plot]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}
-\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
-\label{fig_cfd_probe}
-\end{figure}
-\clearpage
-
+\end{figure*}
 \begin{table}[h!]
@@
 \vspace{2mm}
-{\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.4\linewidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
 \hline
@@
 \label{tbl_cfd_results}
-\end{tabularx}}
+\end{tabularx}
 \end{table}
+\newpage
+Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
+Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{ugum2019}.
+An even distribution of heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
+Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
+This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
+\hl{With this in mind} a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
+
+\begin{figure*}[h!]
+\centering
+\includegraphics[width = 5in]{HEATFLUX_KEY} [$W/m^2$]\\
+\subfigure[Case 1]{\includegraphics[width=0.18\textwidth]{BOT_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 2]{\includegraphics[width=0.2\textwidth]{MID_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 3]{\includegraphics[width=0.2\textwidth]{FBRM_HEATFLUX}}\\
+\subfigure[Case 4]{\includegraphics[width=0.18\textwidth]{BOT05_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 5]{\includegraphics[width=0.2\textwidth]{MID05_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 6]{\includegraphics[width=0.2\textwidth]{FBRM05_HEATFLUX}}
+\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
+\label{fig_cfd_heat_flux}
+\end{figure*}
+\newpage
+\hl{The works of Dugum et al}\cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
+For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
+\hl{Figure} \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
+The figures generally highlight the location and distribution of the flame core for each case.
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.\\
+\begin{figure*}[h!]
+\centering
+\includegraphics[width = 5in]{CO_MF_KEY} [$X_{CO}$]\\
+\subfigure[Case 1]{	\includegraphics[width=0.16\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
+\hspace{5mm}
+\subfigure[Case 2]{	\includegraphics[width=0.16\textwidth, height = 7cm]{MID_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
+\hspace{5mm}
+\subfigure[Case 3]{	\includegraphics[width=0.16\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
+\subfigure[Case 4]{	\includegraphics[width=0.16\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
+\hspace{5mm}
+\subfigure[Case 5]{	\includegraphics[width=0.16\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
+\hspace{5mm}
+\subfigure[Case 6]{	\includegraphics[width=0.16\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
+				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}
+\caption{CO molar fraction ($X_{CO}$) concentrations for 
+Cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
+\label{fig_cfd_coppm}
+\end{figure*}
+
+Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
+Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
+The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
+With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the flame core is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
+Cases 3 and 6 exhibit the best characteristics with the least amount of unburnt carbon content being observed.
+It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
+\\
+
+\begin{figure*}[h!]
+\centering
+\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.45]{SYMMETRY_PROBE_COPPM}}
+\hspace{5mm}
+\subfigure[Offset vertical plot]{\includegraphics[scale = 0.45]{OFFSET_PROBE_COPPM}}
+\hspace{5mm}
+\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.45]{SYMMETRY_PROBE_XO2}}
+\hspace{5mm}
+\subfigure[Offset vertical plot]{\includegraphics[scale = 0.45]{OFFSET_PROBE_XO2}}
+\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
+\label{fig_cfd_probe}
+\end{figure*}
+
 The external tube metal temperatures, shown in Table \ref{tbl_cfd_results} were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
@@
 Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.\\
-
+\newpage
 Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
@@
 However, with the lack of ATT-RH control, a sudden decrease in steam generation can lead to RH overheating and possible RH failure.
-Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.
+Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.\\
+
+\begin{table}[h!]
+\centering
+\caption{Process model control parameters}
+\vspace{2mm}
+\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
+\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
+\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
+\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
+\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
+\hline
+\label{tbl_process_parameters}
+\end{tabularx}
+\end{table}
 
@@
 \end{table}
-
+\newpage
 Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
@@
 This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
+\newpage
 
@@
 A validation case was first performed for the CFD model, which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
-The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.
+The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.\\
+
+The subsequent analysis results show that using a burner arrangement that raises the position of the flame core (Cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
+This firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream and therefore the lowest boiler utilization efficiency.
 \\
 
-The subsequent analysis results show that using a burner arrangement that raises the position of the flame core (Cases 2 and 5) increases the exit flue-gas temperature and runs the risk of final SH failure due to overheating.
-This firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream and therefore the lowest boiler utilization efficiency.\\
-
 Operation of the boiler using firing arrangements of Cases 1 and 4 also results in a lower boiler utilization efficiency and exit flue-gas temperature compared to Cases3 and 6.
-Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high risk of fire side corrosion occurring at continuous low-load operation.\\
+Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high risk of fire side corrosion occurring at continuous low-load operation.
+\\
 
@@
 The predicted re-heater exit steam temperature of Case 3 is substantially closer to the desired temperature of 535 $[^\circ C]$, thus allowing for better control.\\
-
+\newpage
 Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, Case 3 is considered to be the best operational strategy at this low load for the boiler under investigation.
 
-\section*{Acknowledgements}
+\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgment}
 The authors would like to thank the Eskom EPPEI program for financially supporting the present study and acknowledge the computational resources provided by the Centre for High Performance Computing (CHPC), South Africa.
+\end{acknowledgment}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% The bibliography is stored in an external database file
+% in the BibTeX format (file_name.bib).  The bibliography is
+% created by the following command and it will appear in this
+% position in the document. You may, of course, create your
+% own bibliography by using thebibliography environment as in
+%
+% \begin{thebibliography}{12}
+% ...
+% \bibitem{itemreference} D. E. Knudsen.
+% {\em 1966 World Bnus Almanac.}
+% {Permafrost Press, Novosibirsk.}
+% ...
+% \end{thebibliography}
+
+% Here's where you specify the bibliography style file.
+% The full file name for the bibliography style file 
+% used for an ASME paper is asmems4.bst.
+\bibliographystyle{asmems4}
+
+% Here's where you specify the bibliography database file.
+% The full file name of the bibliography database for this
+% article is asme2e.bib. The name for your database is up
+% to you.
+\newpage
 \bibliography{PAPER1_LOW_LOAD}

### 2022-02-11 ASME_journal/journals-1.0/journals-1.0/TSEA-21-1636_FINAL_SUBMISSION.tex
Update-11/02/2022

--- 2022-01-19 ASME_journal/journal-1.1 REVISION/JOURNAL_MANUSCRIPT_BRAD_RAWLINS.tex
@@
 %              Integration Engineering Laboratory                    %
-%              Department of Mechanical and Aeronautical Engineering %
+%              Department of Mechanical and Aerospace Engineering    %
 %              University of California                              %
@@
 % Modified: January  01, 2003 by Geoffrey R. Shiflett                %
+% Modified: July 19, 2009 as a template in a single column for       %
+%           ASME Journals by Harry H. Cheng                          %
 % Use at your own risk, send complaints to /dev/null                 %
@@
 
-%%% use twocolumn and 10pt options with the asme2ej format
-\documentclass[twocolumn,10pt]{asme2ej}
+%%% use 10pt options with the asme2ej format
+\documentclass[10pt]{asme2ej}
 
+\usepackage{epsfig} %% for loading postscript figures
 \usepackage{graphicx} %% for loading jpg figures
@@
 
-\newcommand{\highlight}[1]{%
-  \colorbox{yellow!}{$\displaystyle#1$}}
 %% The class has several options
@@
     }	
-
     }
@@
 \begin{nomenclature}
-\entry{}{\textit{Variables}}
+\begin{multicols}{2}
+\entry{\textbf{\textit{Variables}}}{}
 \entry{$A$}{Area [$m^2$]}
@@
 \entry{$E_p$}{Particle emission power [$W/m^3$]}
-\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
-\entry{$f_{p}$}{Forward scattering factor [$-$]}
+\entry{$f_{heat}$}{Near surface char oxidation fraction [-]}
+\entry{$f_{p}$}{Forward scattering factor [-]}
 \entry{$G$}{Incident radiation [$W/m^2$]}
@@
 \entry{$m_{vol}$}{Mass of volatiles [$kg$]}
-\entry{$N_{p}$}{Number of particles [$-$]}
+\entry{$N_{p}$}{Number of particles [-]}
 \entry{$P$}{Perimeter [$m$]}
@@
 \entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
+\entry{$q_{wall}$}{Wall heat flux [$W/m^2$]}
 \entry{$R$}{Universal gas constant [$J/molK$]}
@@
 \entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
-\entry{$S$}{\hl{Mass source term}[$kg/m^3$]}
-\entry{$S_m$}{\hl{Momentum source term} [$/m^3$]}
-\entry{$S_h$}{\hl{Energy source term} [$W/m^3$]}
-\entry{$S_k$}{\hl{Species source term} [$kg/m^3$]}
+\entry{$S$}{Mass source term[$kg/m^3$]}
+\entry{$S_m$}{Momentum source term [$N/m^3$]}
+\entry{$S_h$}{Energy source term [$W/m^3$]}
+\entry{$S_k$}{Species source term [$kg/m^3$]}
 \entry{$T_g$}{Gas temperature [$K$]}
 \entry{$T_p$}{Particle temperature [$K$]}
+\entry{$T_{wall,i}$}{Wall temperature [$K$]}
+\entry{$T_{water}$}{Water temperature [$K$]}
 \entry{$t$}{Time [$s$]}
+\entry{$U_i$}{Over heat transfer coefficient [$W/m^2K$]}
 \entry{$u$}{Velocity [$m/s$]}
@@
 \entry{$Y_k$}{Species mass fraction [$kg/kg$]}
-\entry{$x$}{Quality [$-$]}
-\entry{}{\textit{Greek Variables}}
+\entry{$x$}{Quality [-]}
+\entry{\textbf{\textit{Greek Variables}}}{}
 \entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
-\entry{$\alpha_H$}{Mixture void fraction [$-$]}
+\entry{$\alpha_H$}{Mixture void fraction [-]}
 \entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
-\entry{$\epsilon_p$}{Particle emissivity [$-$]}
+\entry{$\epsilon_p$}{Particle emissivity [-]}
 \entry{$\rho$}{Gas density [$kg/m^3$]}
@@
 \entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
-\entry{$\phi$}{Scalar variable [$-$]}
-\entry{}{\textit{Abbreviations}}
+\entry{$\phi$}{Scalar variable [-]}
+\entry{\textbf{\textit{Abbreviations}}}{}
 \entry{$MCR$}{Maximum continuous rating}
@@
 \entry{$PA$}{Primary air}
-\entry{$SA-AH$}{Secondary air - air heater}
+\entry{$SA$-$AH$}{Secondary air - air heater}
 \entry{$SA$}{Secondary air}
@@
 \entry{$EC$}{Economiser}
+\end{multicols}
 \end{nomenclature}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
-\newpage
+
 The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model.
@@
 \subsection{Computational fluid dynamics modelling}
+The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities.
+The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture.
+The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase.
+This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer.
+Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
 \subsubsection{Fluid flow, turbulence and combustion modelling}
@@
 To reduce the computational burden, it was assumed that the various processes were in steady-state.
-\hl{The governing equations for the gas phase are written below in their respective Reynolds averaged forms}.\\
+The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
 Mass conservation:
 \begin{equation}\label{eqn_RANS_mass}
-\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=\highlight{S}
+\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
 \end{equation}
@@
 \begin{equation}\label{eqn_momentum}
-\begin{split}
-&\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\\
-&\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
-\end{split}
+\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
 \end{equation}
@@
 
-A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
-\newpage
-The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}).
-The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}).
+A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
+
+The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in Eqn.
+(\ref{eqn_char_rate}).
+The product species of the char oxidation reaction was set to $CO$ as shown in Eqn.
+(\ref{eqn_CO_reaction}).
 \begin{gather}
@@
 \end{gather}
-The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
+The diffusion and kinetic rates of Eqn.
+(\ref{eqn_char_rate}) are defined in Eqn.
+(\ref{eqn_char_diff_rate})  and Eqn.
+(\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
 \begin{gather}
@@
 The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash.
-The scalar field equations are provided in Table \ref{tab_scalars}.\\
+The scalar field equations are provided in Tab.
+\ref{tab_scalars}.\\
 
@@
 \vspace{2mm}     
-\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
+\begin{tabularx}{0.6\textwidth}{p{0.4in} p{0.3\textwidth} l}
 \hline
@@
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
-\hl{To solve the additional transport equations and their source terms user defined functions, utilized by ANSYS Fluent, were developed using the C programming language.}
+To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.
 
 \subsection{Heat transfer modelling}
-Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
+Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in Eqn.
+(\ref{eqn_RTE}).
 \begin{equation}\label{eqn_RTE}
-\begin{split}
-&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
-&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
-\end{split}
+\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
 \end{equation}
+
 In the present work the RTE is solved using the P1 model.
@@
 The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p = \rho \phi_{mp0} V / \left( \rho_p \pi \bar{d_p}^3 /6 \right)$) present in a cell.
-The equations for the radiative properties are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
+The equations for the radiative properties are given in Eqn.
+(\ref{eqn_part_abs}) through Eqn.
+(\ref{eqn_part_emisp}).
 \begin{gather}
@@
 It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
+
 \begin{figure*} 
@@
 \caption{Boiler geometry and layout}
+\label{fig_geometry}
+\end{figure*}
+\begin{figure*}
+\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
+\caption{Burner layout and mesh details}
 \label{fig_geometry}
@@
 A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021.
+\hl{The data transfer between the two models makes use of a one-way approach, where the CFD simulation data is transferred to the Flownex process model when convergence of each case is achieved, a further explanation of the coupling interface is given in Section } \ref{sec_set_up}.
 The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls.
@@
 The heat exchangers were modelled using a homogeneous two-phase mixture approach, which assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area.
-The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
+The homogeneous mixture fraction and mixture density are defined in Eqn.
+(\ref{eqn_vol_frac}) and Eqn.
+(\ref{eqn_mix_rho}) respectively.
 \begin{gather}
@@
 
-\subsection{Geometry \& process model set-up}
+\subsection{Geometry \& process model set-up} \label{sec_set_up}
 The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], width of 14.01 [$m$] and height of 64 [$m$].
-The CFD geometric model (of Figure \ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace.
+The CFD geometric model (of Fig.
+\ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace.
 This was done to reduce the cell count of the numerical mesh.
@@
 
-The boiler furnace is fed by six mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of six burners.
-This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.\\
+\hl{The boiler furnace is fed by six mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of six opposing wall mounted swirl burners.
+The swirl vanes were not modelled in this study, rather an axial and tangential velocity component were used for the secondary air (SA) inlets with these values being obtained from a detailed burner model supplied by the burner manufacturer, which included the vanes.
+The fuel/PA mixture is injected through the inner annulus of the burner while the SA air is fed through the outer annulus as seen in Fig.
+2.}\\
 
-The process model of the boiler configuration is shown in Figure \ref{fig_flownex}.
+The CFD wall boundary conditions were modelled using ANSYS Fluent v19.5’s convection boundary condition type, which requires the internal free stream temperature, the internal heat transfer coefficient, wall thicknesses and material conductivities.Being a flux boundary condition the wall heat flux ($\dot{q}_{wall}$) can be calculated using Eqn.
+23.
+\begin{equation}\label{eqn_q_flux}
+\dot{q}_{wall} = U_i(T_{wall,i}-T_{water})
+\end{equation}
+\hl{The overall heat transfer coefficient (U) is subsequently determined using the following expression.}
+\begin{equation}\label{eqn_overall_heat_coeff}
+U_i=\frac{1}{\frac{1}{h_{int}}+\frac{t_{wall}}{\lambda_{wall}}+\frac{t_{ash}}{\lambda_{ash}}}
+\end{equation}
+
+\hl{A 1D process model was used to estimate the furnace, platen and final SH internal heat transfer coefficients and internal temperatures for the low load case.
+For the validation cases the experimental data from site was used to estimate the mean water temperature in the heat exchangers.}\\
+
+The process model of the boiler configuration is shown in Fig.
+\ref{fig_flownex}.
 The process model includes all the heat exchangers up to and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH).
@@
 The coupling interface between the simulation models are the heat-exchanger external tube surfaces, namely the furnace, platen and final SH walls.
-The CFD heat loads are used as energy sources for these components as indicated in Figure \ref{fig_flownex}.
+The CFD heat loads are used as energy sources for these components as indicated in Fig.
+\ref{fig_flownex}.
 The furnace heat load to the evaporator walls determines the circulation rate through the evaporator.
@@
 Furthermore, the CFD flue-gas results (i.e.
-composition, mass flow and temperature) exiting the final SH are used as boundary values for the heat exchangers downstream of the final SH (SH3), as shown in Figure \ref{fig_flownex}.
+composition, mass flow and temperature) exiting the final SH are used as boundary values for the heat exchangers downstream of the final SH (SH3), as shown in Fig.
+\ref{fig_flownex}.
 The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.\\
 
-Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Figure \ref{fig_flownex}).\\
+Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}).\\
 
@@
 For this study six cases are simulated with the following three burner firing configurations being investigated:
+\newpage
 \begin{enumerate}
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{3.25in}{p{1.25in} p{1in} l}
+\begin{tabularx}{3.25in}{p{1.4in} p{0.75in} l}
 \hline
@@
 \hline
+\textbf{Excess air coefficients} & 1.37 & 1.32\\
+\hline
+
 \end{tabularx}}
@@
 
-A secondary air flow rate of 5 [$kg/s$] is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber.
-The result is a high air-fuel ratio in the furnace, which leads to higher dry gas losses.
-To lower this loss, this study will investigate the effect of reducing the air-fuel ratio by lowering the non-firing burner SA flowrate from 5 to 2.5 [$kg/s$].
+A secondary air flow rate of 5 kg/s is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber, with these three cases numbered 1, 2 and 3.
+The result is a high air-fuel ratio in the furnace, which leads to higher boiler dry gas loss.
+To lower this loss, this study will investigate the effect of reducing the air-fuel ratio by lowering the non-firing burner SA flowrate from 5 to 2.5 kg/s, with these three cases numbered 4, 5 and 6.
 Two permutations of the SA flowrate, at the non-firing burners, are used for each of the firing configurations mentioned above.
-Table \ref{tbl_case_inputs} shows the input conditions for Cases 1 to 6.
+Table 3 shows the input conditions for Cases 1 to 6.
 This data was obtained via conventional boiler mass and energy balance calculations.
 
-\subsection{Numerical solution strategy} 
+\subsection{Numerical solution strategy}\label{sec_num_sol}
+A numerical mesh consisting of approximately 6 million cells was used for the CFD simulations of this current study.
+To ensure that the results are grid size independent, simulations were also performed for mesh sizes of 3.5 million and 10 million cells during the validation study, discusses in Section \ref{sec_model_valid}.
+To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively\\ %.
+
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
@@
 Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
-The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \cite{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.\\
+The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.\\
 
@@
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
-The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
+The temperature and velocity profiles for the various firing arrangements are shown in Fig.
+\ref{fig_cfd_temp} and Fig.
+\ref{fig_cfd_velo} respectively.
 With the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
-This is further exacerbated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
-The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}).
-This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Table \ref{tbl_process_parameters}.\\
+This is further exacerbated when considering Tab.
+\ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
+The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Fig.
+\ref{fig_cfd_temp}).
+This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Tab.
+\ref{tbl_process_parameters}.\\
 
@@
 Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
-This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Figure \ref{fig_cfd_velo}.
-\hl{With this in mind} a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively.
-With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Figure \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
+This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Fig.
+\ref{fig_cfd_velo}.
+\hl{With this in mind} a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Fig.
+\ref{fig_cfd_temp} and Fig.\ref{fig_cfd_velo} respectively.
+With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Fig.
+\ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
+
+\begin{table}[h!]
+\centering
+\caption{Process model control parameters}
+\vspace{2mm}
+\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
+\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
+\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
+\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
+\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
+\hline
+\label{tbl_process_parameters}
+\end{tabularx}
+\end{table}
 
@@
 For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
-\hl{Figure} \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
+Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
 The figures generally highlight the location and distribution of the flame core for each case.
@@
 
-Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Figure \ref{fig_geometry}) are given in Figure \ref{fig_cfd_probe}.
+Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Fig.
+\ref{fig_geometry}) are given in Fig.
+\ref{fig_cfd_probe}.
 Cases 2 and 5 illustrates the highest $X_{O_{2}}$ concentration in the lower half of the burner since there is minimal combustion occurring.
-The unburnt carbon content and exit flue-gas temperatures for each case are reported in Table \ref{tbl_cfd_results}.
+The unburnt carbon content and exit flue-gas temperatures for each case are reported in Tab.
+\ref{tbl_cfd_results}.
 With the use of the middle burners (Cases 2 and 5) the highest exit temperature and unburnt carbon content is observed, since the flame core is located in the upper half of the furnace leading to the least possibility of complete combustion due to the shorter residence time.
@@
 
-The external tube metal temperatures, shown in Table \ref{tbl_cfd_results} were calculated using equation \ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
+The external tube metal temperatures, shown in Tab.
+\ref{tbl_cfd_results} were calculated using Eqn.
+\ref{eqn_t_wall}, which takes into account the temperature drop due to the ash deposit present on platen and final SH.
 Fouling thermal resistances of 0.0067 and 0.015 [$m^2K/W$] were used for the platen and final SH respectively.
@@
 \newpage
-Using the process model of Figure \ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
+Using the process model of Fig.
+\ref{fig_flownex} and the results of the CFD simulations the important process control parameters were determined.
 Table \ref{tbl_process_parameters} summarizes the results with the highest boiler efficiencies observed for Cases 3 and 6.
@@
 Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.\\
-
-\begin{table}[h!]
-\centering
-\caption{Process model control parameters}
-\vspace{2mm}
-\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
-\hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
-\hline
-\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
-\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
-\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
-\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
-\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
-\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
-\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
-\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
-\hline
-\label{tbl_process_parameters}
-\end{tabularx}
-\end{table}
 
@@
 
-Operation of the boiler using firing arrangements of Cases 1 and 4 also results in a lower boiler utilization efficiency and exit flue-gas temperature compared to Cases3 and 6.
+Operation of the boiler using firing arrangements of Cases 1 and 4 also results in a lower boiler utilization efficiency and exit flue-gas temperature compared to Cases 3 and 6.
 Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high risk of fire side corrosion occurring at continuous low-load operation.
@@
 The mixed firing arrangements, of Cases 3 and 6, exhibit the best boiler utilization efficiencies.
+Cases 3 and 6 display the best $X_{CO}$ molar concentration distribution which highlights the minimal likelihood of inducing fire-side corrosion in the furnace when utilizing this firing configuration.
 A 4.8\% decrease in unburnt carbon percentage is observed when operating using Case 3 in relation to Case 6.
 The predicted re-heater exit steam temperature of Case 3 is substantially closer to the desired temperature of 535 $[^\circ C]$, thus allowing for better control.\\
-\newpage
+
 Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, Case 3 is considered to be the best operational strategy at this low load for the boiler under investigation.
-
-\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{acknowledgment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 % to you.
-\newpage
+
 \bibliography{PAPER1_LOW_LOAD}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2022-02-11 ASME_journal/journals-1.0/journals-1.0/asme2ejs.tex
Update-11/02/2022

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aerospace Engineering    %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Modified: July 19, 2009 as a template in a single column for       %
%           ASME Journals by Harry H. Cheng                          %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use 10pt options with the asme2ej format
\documentclass[10pt]{asme2ej}

\usepackage{epsfig} %% for loading postscript figures

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

\title{The Final Version of an ASME Journal Article \\
Created Using 
\LaTeX2\raisebox{-.3ex}{$\epsilon$}
in ASME Format \\
Submitted for Publication}

%%% first author
\author{Harry H. Cheng
    \affiliation{
	Professor, Fellow of ASME\\
	Integration Engineering Laboratory\\
	Department of Mechanical Engineering\\
	University of California\\
	Davis, California 95616\\
    Email: hhcheng@ucdavis.edu
    }	
}

%%% second author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
\author{J. Michael McCarthy\thanks{Address all correspondence related to ASME style format and figures to this author.} \\
    \affiliation{ Editor, Fellow of ASME\\
	Journal of Mechanical Design\\
        Email: jmmccart@uci.edu
    }
}

%%% third author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
\author{Third Co-author\\
        Graduate Research Assistan, Student Member of ASME\\
       {\tensfb Fourth Co-author}\thanks{Address all correspondence for other issues to this author.} 
    \affiliation{Title, Member of ASME\\
        Department or Division Name\\
        Company or College Name\\
        City, State (spelled out), Zip Code\\
        Country (only if not U.S.)\\
        Email address (if available)
    }
}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it 
This article illustrates preparation of the final version of
an ASME journal paper submitted for publication using 
\LaTeX2\raisebox{-.3ex}{$\epsilon$}. For the convenience of proofreading
and editing, the final version shall be formatted in a single column. 
This article is formatted based on the contents in the article
entitled ``{\rm An ASME Journal Article Created Using 
\LaTeX2\raisebox{-.3ex}{$\epsilon$} in ASME Format for 
Testing Your Figures,}" which is a template for 
preparation of ASME papers submitted for review.
An abstract for an ASME paper should be less than 150 words and is normally in italics.  Notice that this abstract is to be set in 9pt Times Italic, single spaced and right justified.  
%%% 
Please use this template to test how your figures will look on the printed journal page of the Journal of Mechanical Design.  The Journal will no longer publish papers that contain errors in figure resolution.  These usually consist of unreadable or fuzzy text, and pixilation or rasterization of lines.  This template identifies the specifications used by JMD some of which may not be easily duplicated; for example, ASME actually uses Helvetica Condensed Bold, but this is not generally available so for the purpose of this exercise Helvetica is adequate.  However, reproduction of the journal page is not the goal, instead this exercise is to verify the quality of your figures. 
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{A}{You may include nomenclature here.}
\entry{$\alpha$}{There are two arguments for each entry of the nomemclature environment, the symbol and the definition.}
\end{nomenclature}

The primary text heading is  boldface and flushed left with the left margin.  The spacing between the  text and the heading is two line spaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

This article illustrates preparation of ASME paper using \LaTeX2\raisebox{-.3ex}{$\epsilon$}. The \LaTeX\  macro \verb+asme2ej.cls+, the {\sc Bib}\TeX\ style file \verb+asmems4.bst+, and the template \verb+asme2ej.tex+ that create this article are available on the WWW  at the URL address \verb+http://iel.ucdavis.edu/code/+. To ensure compliance with the 2003 ASME MS4 style guidelines  \cite{asmemanual}, you should modify neither the \LaTeX\ macro \verb+asme2ej.cls+ nor the {\sc Bib}\TeX\ style file \verb+asmems4.bst+. By comparing the output generated by typesetting this file and the \LaTeX2\raisebox{-.3ex}{$\epsilon$} source file, you should find everything you need to help you through the preparation of ASME paper using \LaTeX2\raisebox{-.3ex}{$\epsilon$}. Details on using \LaTeX\ can be found in \cite{latex}.

In order to get started in generating a two-column version of your paper, please format the document with 0.75in top margin, 1.5in bottom margin and 0.825in left and right margins.  Break the text into two sections one for the title heading, and another for the body of the paper.

The format of the heading is not critical, on the other hand formatting of the body of the text is the primary goal of this exercise.  This will allow you to see that the figures are matched to the column width and font size of the paper.  The double column of the heading section is set to 1.85in for the first column, a 0.5in spacing, and 4.5in for the second column.  For the body of the paper, set it to 3.34in for both columns with 0.17in spacing, both are right justified.

The information that is the focus of this exercise is found in 
section~\ref{sect_figure}.
Please use this template to format your paper in a way that is similar to the printed form of the Journal of Mechanical Design.  This will allow you to verify that the size and resolution of your figures match the page layout of the journal.  The ASME Journal of Mechanical Design will no longer publish papers that have the errors demonstrated here.

ASME simply requires that the font should be the appropriate size and not be blurred or pixilated, and that lines should be the appropriate weight and have minimal, preferably no, pixilation or rasterization.

The journal uses 10pt Times Roman Bold for headings, but Times Bold is good enough for this effort.  The text is set at 9pt Times Roman, and again Times will be fine.  Insert a new line after the heading, and two lines after each section.  This is not exactly right but it is close enough.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Very Very Very Very Very Very Very Very Very Very Very Long Heading}

The heading is boldface with upper and lower case letters. 
If the heading should run into more than one line, the run-over is not left-flushed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Second-Level Heading}

The next level of heading is also boldface with upper and lower case letters. 
The heading is flushed left with the left margin. The spacing to the next heading is two line spaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Third-Level Heading.}

The third-level of heading follows the style of the second-level heading.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Use of SI Units}

An ASME paper should use SI units.  When preference is given to SI units, the U.S. customary units may be given in parentheses or omitted. When U.S. customary units are given preference, the SI equivalent {\em shall} be provided in parentheses or in a supplementary table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Footnotes\protect\footnotemark}
\footnotetext{Examine the input file, asme2ej.tex, to see how a footnote is given in a head.}

Footnotes are referenced with superscript numerals and are numbered consecutively from 1 to the end of the paper\footnote{Avoid footnotes if at all possible.}. Footnotes should appear at the bottom of the column in which they are referenced.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mathematics}

Equations should be numbered consecutively beginning with (1) to the end of the paper, including any appendices.  The number should be enclosed in parentheses and set flush right in the column on the same line as the equation.  An extra line of space should be left above and below a displayed equation or formula. \LaTeX\ can automatically keep track of equation numbers in the paper and format almost any equation imaginable. An example is shown in Eqn.~(\ref{eq_ASME}). The number of a referenced equation in the text should be preceded by Eqn.\ unless the reference starts a sentence in which case Eqn.\ should be expanded to Equation.

\begin{equation}
f(t) = \int_{0_+}^t F(t) dt + \frac{d g(t)}{d t}
\label{eq_ASME}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Figures}
\label{sect_figure}

All figures should be positioned at the top of the page where possible.  All figures should be numbered consecutively and centered under the figure as shown in Fig.~\ref{figure_ASME}. All text within the figure should be no smaller than 7~pt. There should be a minimum two line spaces between figures and text. The number of a referenced figure or table in the text should be preceded by Fig.\ or Tab.\ respectively unless the reference starts a sentence in which case Fig.\ or Tab.\ should be expanded to Figure or Table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\setlength{\unitlength}{0.012500in}%
\begin{picture}(115,35)(255,545)
\thicklines
\put(255,545){\framebox(115,35){}}
\put(275,560){Beautiful Figure}
\end{picture}
\end{center}
\caption{The caption of a single sentence does not have period at the end}
\label{figure_ASME} 
\end{figure}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following subsections, I have inserted figures that have been provided by authors in order to demonstrate what to avoid.  In each case the authors provided figures that are 3.25in wide and 600dpi in the .tif graphics format.  The papers containing these figures have been held from production due to their poor quality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The 1st Example of Bad Figure}

%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
%%% 3.34in is the maximum width you can have for a figure
%\begin{figure} 
%\centerline{\psfig{figure=figure/FMANU_MD_05_1107_11.ps,width=3.34in}}
%\caption{Example taken from a paper that was held from production because the image quality is poor.  ASME sets %figures captions in 8pt, Helvetica Bold.}
%\label{fig_example1.ps}
%\end{figure}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%

In order to place the figure in this template using MSWord, select Insert Picture from File,and use wrapping that is  top and bottom. Make sure the figure is 3.25in wide.

Figure~`\ref{fig_example1.ps}
was taken from a recent paper that was held from publication, because the text is fuzzy and unreadable.  It was probably obtained by taking a screen shot of the computer output of the authors software.  This means the original figure was 72dpi (dots per inch) on a computer screen.  There is no way to improve the quality such a low resolution figure.

In order to understand how poor the quality of this figure is, please zoom in slightly, say to 200\%.  Notice that while the font of the paper is clear at this size, the font in the figures is fuzzy and blurred.  It is impossible to make out the small symbol beside the numbers along the abscissa of the graph.  Now consider the labels Time and Cost.  They are clearly in fonts larger that the text of the article, yet the pixilation or rasterization, associated with low resolution is obvious. This figure must be regenerated at higher resolution to ensure quality presentation.

The poor quality of this figure is immediately obvious on the printed page, and reduces the impact of the research contribution of the paper, and in fact detracts from the perceived quality of the journal itself.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The 2nd Example of Bad Figure}

%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%

Figure~\ref{fig_example2.ps}
demonstrates a common problem that arises when a figure is scaled down fit a single column width of 3.25in.  The original figure had labels that were readable at full size, but become unreadable when scaled to half size.  This figure also suffers from poor resolution as is seen in the jagged lines the ovals that form the chain.

This problem can be addressed by increasing the size of the figure to a double column width of 6.5in, so the text is readable.  But this will not improve the line pixilation, and a large low resolution figure is less desirable than a small one.  This also significantly expands the length of the paper, and may cause it to exceed the JMD nine page limit.  Additional pages require page charges of \$200 per page.  It is best to regenerate the figure at the resolution that ensures a quality presentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The 3rd Example of Bad Figure}
%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
\begin{figure} 
%\centerline{\psfig{figure=figure/FMANU_MD_04_1274_13.ps,width=3.34in}}

\caption{Another example of a figure with unreadable text.  Even when the paper was expanded to double column width the text as shown in Fig. was of such low quality that the paper was held from production.}
\label{fig_example3.ps}
\end{figure}

%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
%%% the maximum width in double column is 6.85in

%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%
An author provided the high resolution image 
in Fig.
that was sized to a single column width of 3.25in.  Upon seeing the poor quality of the text, the publisher scaled the image to double column width as shown in Fig.
at which point it took half of a page.  The publisher went on to do this for all eight figures generating four pages of figures that the author did not expect. ASME stopped production of the paper even with the larger figures due to the pixilation of the font.

Clearly the text in this figure is unreadable, and it is doubtful that the author can print the output in a way that it is readable.  This is a problem that the author must solve, not the publisher.

As you might expect, I have many more examples, but in the end the author is the best judge of what is needed in each figure.  ASME simply requires that the image meet a minimum standard for font and line quality, specifically the font should be the appropriate size and not be blurred or pixilated, and that lines should be the appropriate weight and have minimal, preferably no, pixilation or rasterization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tables}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% begin table   %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\caption{Figure and table captions do not end with a period}
\begin{center}
\label{table_ASME}
\begin{tabular}{c l l}
& & \\ % put some space after the caption
\hline
Example & Time & Cost \\
\hline
1 & 12.5 & \$1,000 \\
2 & 24 & \$2,000 \\
\hline
\end{tabular}
\end{center}
\end{table}
%%%%%%%%%%%%%%%% end table %%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All tables should be numbered consecutively  and centered above the table as shown in Table~\ref{table_ASME}. The body of the table should be no smaller than 7 pt.  There should be a minimum two line spaces between tables and text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Citing References}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The ASME reference format is defined in the authors kit provided by the ASME.  The format is:

\begin{quotation}
{\em Text Citation}. Within the text, references should be cited in  numerical order according to their order of appearance.  The numbered reference citation should be enclosed in brackets.
\end{quotation}

The references must appear in the paper in the order that they were cited.  In addition, multiple citations (3 or more in the same brackets) must appear as a `` [1-3]''.  A complete definition of the ASME reference format can be found in the  ASME manual \cite{asmemanual}.

The bibliography style required by the ASME is unsorted with entries appearing in the order in which the citations appear. If that were the only specification, the standard {\sc Bib}\TeX\ unsrt bibliography style could be used. Unfortunately, the bibliography style required by the ASME has additional requirements (last name followed by first name, periodical volume in boldface, periodical number inside parentheses, etc.) that are not part of the unsrt style. Therefore, to get ASME bibliography formatting, you must use the \verb+asmems4.bst+ bibliography style file with {\sc Bib}\TeX. This file is not part of the standard BibTeX distribution so you'll need to place the file someplace where LaTeX can find it (one possibility is in the same location as the file being typeset).

With \LaTeX/{\sc Bib}\TeX, \LaTeX\ uses the citation format set by the class file and writes the citation information into the .aux file associated with the \LaTeX\ source. {\sc Bib}\TeX\ reads the .aux file and matches the citations to the entries in the bibliographic data base file specified in the \LaTeX\ source file by the \verb+\bibliography+ command. {\sc Bib}\TeX\ then writes the bibliography in accordance with the rules in the bibliography .bst style file to a .bbl file which \LaTeX\ merges with the source text.  A good description of the use of {\sc Bib}\TeX\ can be found in \cite{latex, goosens} (see how two references are handled?).  The following is an example of how three or more references \cite{latex, asmemanual,  goosens} show up using the \verb+asmems4.bst+ bibliography style file in conjunction with the \verb+asme2ej.cls+ class file. Here are some more \cite{art, blt, ibk, icn, ips, mts, mis, pro, pts, trt, upd} which can be used to describe almost any sort of reference.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The only way to ensure that your figures are presented in the ASME Journal of Mechanical Design in the way you feel is appropriate and meets the requirement for quality presentation is for you to prepare a double column version of the paper in a form similar to that used by the Journal.

This gives you the opportunity to ensure that the figures are sized appropriately, in particular that the labels are readable and match the size of the text in the journal, and that the line weights and resolutions have no pixilation or rasterization.  Poor quality figures are immediately obvious on the printed page, and this detracts from the perceived quality of the journal.

I am pleased to provide advice on how to improve any figure, but this effort must start with a two-column version of the manuscript. Thank you in advance for your patience with this effort, it will ensure quality presentation of your research contributions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussions}
This template is not yet ASME journal paper format compliant at this point.
More specifically, the following features are not ASME format compliant.
\begin{enumerate}
\item
The format for the title, author, and abstract in the cover page.
\item
The font for title should be 24 pt Helvetica bold.
\end{enumerate}

\noindent
If you can help to fix these problems, please send us an updated template.
If you know there is any other non-compliant item, please let us know.
We will add it to the above list.
With your help, we shall make this template 
compliant to the ASME journal paper format.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgment}
ASME Technical Publications provided the format specifications for the Journal of Mechanical Design, though they are not easy to reproduce.  It is their commitment to ensuring quality figures in every issue of JMD that motivates this effort to have authors review the presentation of their figures.

Thanks go to D. E. Knuth and L. Lamport for developing the wonderful word processing software packages \TeX\ and \LaTeX. We would like to thank Ken Sprott, Kirk van Katwyk, and Matt Campbell for fixing bugs in the ASME style file \verb+asme2ej.cls+, and Geoff Shiflett for creating 
ASME bibliography stype file \verb+asmems4.bst+.
\end{acknowledgment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The bibliography is stored in an external database file
% in the BibTeX format (file_name.bib).  The bibliography is
% created by the following command and it will appear in this
% position in the document. You may, of course, create your
% own bibliography by using thebibliography environment as in
%
% \begin{thebibliography}{12}
% ...
% \bibitem{itemreference} D. E. Knudsen.
% {\em 1966 World Bnus Almanac.}
% {Permafrost Press, Novosibirsk.}
% ...
% \end{thebibliography}

% Here's where you specify the bibliography style file.
% The full file name for the bibliography style file 
% used for an ASME paper is asmems4.bst.
\bibliographystyle{asmems4}

% Here's where you specify the bibliography database file.
% The full file name of the bibliography database for this
% article is asme2e.bib. The name for your database is up
% to you.
\bibliography{asme2e}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix       %%% starting appendix
\section*{Appendix A: Head of First Appendix}
Avoid Appendices if possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix B: Head of Second Appendix}
\subsection*{Subsection head in appendix}
The equation counter is not reset in an appendix and the numbers will
follow one continual sequence from the beginning of the article to the very end as shown in the following example.
\begin{equation}
a = b + c.
\end{equation}

\end{document}

### 2022-02-11 ASME_journal/journals-1.3/journals-1.3/TSEA-21-1636_FINAL_SUBMISSION.tex
Update-11/02/2022

--- 2022-02-11 ASME_journal/journals-1.0/journals-1.0/TSEA-21-1636_FINAL_SUBMISSION.tex
@@
 %%% use 10pt options with the asme2ej format
-\documentclass[10pt]{asme2ej}
+%\documentclass[10pt]{asme2ej}
+\documentclass[11pt,cleanfoot]{asme2ej}
 
-\usepackage{epsfig} %% for loading postscript figures
-\usepackage{graphicx} %% for loading jpg figures
 \usepackage{tabu}
@@
 \usepackage{xcolor}
+
+\usepackage{graphicx} %% for loading jpg figures
+\usepackage{epsfig}
+\usepackage{fancyhdr}
+\usepackage{setspace}
+\usepackage{helvet}
+\usepackage[hyphens]{url}
+%\usepackage{hyphens}
+\renewcommand{\familydefault}{\sfdefault}
+\pagestyle{fancy}
+\lhead{{\it Journal of Thermal Science and Engineering Applications}}
+\rhead{}
+\renewcommand{\headrulewidth}{0pt}
+\topmargin 80 pt
+\headheight 14 pt
+\headsep 30 pt
+%\RequirePackage[hyphens]
+\usepackage{hyperref}   % to set up hyperlinks
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	citecolor=blue,
+	urlcolor=blue,
+}
+\usepackage[square,numbers]{natbib}
 
@@
 \maketitle    
-
+\doublespacing
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \entry{$E_p$}{Particle emission power [$W/m^3$]}
-\entry{$f_{heat}$}{Near surface char oxidation fraction [-]}
+\entry{$f_{heat}$}{Surface char oxidation fraction [-]}
 \entry{$f_{p}$}{Forward scattering factor [-]}
@@
 \entry{$t$}{Time [$s$]}
-\entry{$U_i$}{Over heat transfer coefficient [$W/m^2K$]}
+\entry{$U_i$}{Overall heat transfer coefficient}
+\entry{}{[$W/m^2K$]}
 \entry{$u$}{Velocity [$m/s$]}
@@
 \entry{$\rho_p$}{Particle density [$kg/m^3$]}
-\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
+\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant}
+\entry{}{[$W/m^2K^4$]}
 \entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
@@
 However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}.
-Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\
+Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.
 
 The integration of renewable energy sources will push CFPPs from primarily base load operation to a mid-merit/flexible operating protocol, which includes prolonged operation at low-loads.
-Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.\\
+Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.
 
@@
 Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions.
-CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).\\
+CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).
 
 Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}.
-The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\
+The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.
 
@@
 A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions.
-The aforementioned research specifically investigated combustion and gas-side effects.\\
+The aforementioned research specifically investigated combustion and gas-side effects.
 
@@
 Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy.
-However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
+However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.
 
 The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model.
-Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\
+Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.
 
@@
 The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\
-
 To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements.
 Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.
-
 \section{Mathematical model}
@@
 This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners.
-The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.\\
+The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.
 
@@
 
-A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
+A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.
 
@@
 A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
-
 \subsubsection{Particle modelling}
@@
 The scalar field equations are provided in Tab.
-\ref{tab_scalars}.\\
-
+\ref{tab_scalars}.
 \begin{table}[h!]
@@
 \vspace{2mm}     
-\begin{tabularx}{0.6\textwidth}{p{0.4in} p{0.3\textwidth} l}
+\begin{tabularx}{0.8\textwidth}{p{0.1\textwidth} p{0.4\textwidth} l}
 \hline
@@
 To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.
-
 \subsection{Heat transfer modelling}
@@
 It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
-
-\begin{figure*} 
-\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
-\caption{Boiler geometry and layout}
-\label{fig_geometry}
-\end{figure*}
-\begin{figure*}
-\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
-\caption{Burner layout and mesh details}
-\label{fig_geometry}
-\end{figure*}
-\begin{figure*}[h!]
-\centering
-\includegraphics[scale=0.5]{FLOWNEX_SETUP}
-\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
-\label{fig_flownex}
-\end{figure*}
 \subsection{Process simulation model}
 A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021.
-\hl{The data transfer between the two models makes use of a one-way approach, where the CFD simulation data is transferred to the Flownex process model when convergence of each case is achieved, a further explanation of the coupling interface is given in Section } \ref{sec_set_up}.
+The data transfer between the two models makes use of a one-way approach, where the CFD simulation data is transferred to the Flownex process model when convergence of each case is achieved, a further explanation of the coupling interface is given in Section  \ref{sec_set_up}.
 The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls.
@@
 Applying the mixture density the following transport equations are solved per process model component;
-
 \begin{equation}\label{eqn_mix_conti}
@@
 The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects on the water-side of the boiler system.
-
 \section{Case study boiler description \& set-up}
@@
 fuel characteristics and boundary conditions) and the numerical solution strategy.
-
 \subsection{Geometry \& process model set-up} \label{sec_set_up}
@@
 There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$].
-Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.\\
+Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.
+\begin{figure*} [h!]
+\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
+\caption{Boiler geometry and layout}
+\label{fig_geometry}
+\end{figure*}
 
-\hl{The boiler furnace is fed by six mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of six opposing wall mounted swirl burners.
+The boiler furnace is fed by six mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of six opposing wall mounted swirl burners.
 The swirl vanes were not modelled in this study, rather an axial and tangential velocity component were used for the secondary air (SA) inlets with these values being obtained from a detailed burner model supplied by the burner manufacturer, which included the vanes.
 The fuel/PA mixture is injected through the inner annulus of the burner while the SA air is fed through the outer annulus as seen in Fig.
-2.}\\
+\ref{fig_burner_mesh}.
+\newpage
+\begin{figure*}
+\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
+\caption{Burner layout and mesh details}
+\label{fig_burner_mesh}
+\end{figure*}
 
@@
 \end{equation}
-\hl{The overall heat transfer coefficient (U) is subsequently determined using the following expression.}
+The overall heat transfer coefficient (U) is subsequently determined using the following expression.
 \begin{equation}\label{eqn_overall_heat_coeff}
@@
 
-\hl{A 1D process model was used to estimate the furnace, platen and final SH internal heat transfer coefficients and internal temperatures for the low load case.
-For the validation cases the experimental data from site was used to estimate the mean water temperature in the heat exchangers.}\\
+A 1D process model was used to estimate the furnace, platen and final SH internal heat transfer coefficients and internal temperatures for the low load case.
+For the validation cases the experimental data from site was used to estimate the mean water temperature in the heat exchangers.
 
@@
 The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system that includes the downcomers and steam drum.
-As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.\\
+As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.5]{FLOWNEX_SETUP}
+\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
+\label{fig_flownex}
+\end{figure*}
 
@@
 \ref{fig_flownex}.
-The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.\\
+The steam flow boundary values for the RH and EC sections are fixed inlet mass flows and temperatures with the corresponding outlets set to a fixed pressure.
 
-Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}).\\
+Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}).
+\begin{figure*}[h!]
+\centerline{\includegraphics[scale=0.4]{HEAT_EXCHANGER_PROCESS_MODEL}}
+\caption{Heat-exchanger component model}
+\label{fig_heat_exchanger_model}
+\end{figure*}
 
@@
 It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
-\begin{figure*}[h!]
-\centerline{\includegraphics[scale=0.4]{HEAT_EXCHANGER_PROCESS_MODEL}}
-\caption{Heat-exchanger component model}
-\label{fig_heat_exchanger_model}
-\end{figure*}
 
@@
 Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.\\
-
 \begin{table}[h!]
@@
 \label{tbl_fuel}
-\begin{tabularx}{3.25in}{p{1.5in} p{0.8in} l}
+\begin{tabularx}{0.7\textwidth}{p{0.3\textwidth} p{0.2\textwidth} l}
 \hline
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{3.25in}{p{1.4in} p{0.75in} l}
+\begin{tabularx}{0.7\textwidth}{p{0.27\textwidth} p{0.225\textwidth} l}
 \hline
@@
 \hline
-
 \end{tabularx}}
@@
 To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively\\ %.
-
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
@@
 The scalar field equations used a second-order upwind scheme.\\
-
 The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
@@
 The remaining fields were solved till convergence.
-
 \section{Results \& discussion}
@@
 Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
-The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.\\
+The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
+\begin{figure*}[h]
+\centerline{\includegraphics[scale = 0.425]{VALIDATION}}
+\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
+\label{fig_heat_valid}
+\end{figure*}
 
 Figure \ref{fig_heat_valid} shows that the calculated overall heat loads are in good agreement with the measured values where the model results are within the associated uncertainty range in all but one case.
-The simulation systematically under predicts the furnace heat loads, with a maximum percentage error of 2\%, while predominating overpredicting the platen SH loads, with a maximum percentage error of 7\%.\\
+The simulation systematically under predicts the furnace heat loads, with a maximum percentage error of 2\%, while predominating overpredicting the platen SH loads, with a maximum percentage error of 7\%.
 
@@
 The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during full load (100\% MCR) operating conditions.
-The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].\\
-
-\begin{figure*}[h]
-\centerline{\includegraphics[scale = 0.4]{VALIDATION}}
-\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
-\label{fig_heat_valid}
-\end{figure*}
-\begin{figure}[h!]
+The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].
+\begin{figure*}[h!]
 \centering
-\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{COPPM_VALID}}
+\subfigure[]{\includegraphics[width = 0.475\textwidth, height =5cm ]{COPPM_VALID}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{XO2_VALID}}
+\subfigure[]{\includegraphics[width = 0.475\textwidth, height =5cm ]{XO2_VALID}}
 \caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
 \label{fig_probe_valid}
-\end{figure}
+\end{figure*}
+
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
 It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.
-
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
@@
 This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Tab.
-\ref{tbl_process_parameters}.\\
-
+\ref{tbl_process_parameters}.
 \begin{figure*}[h!]
@@
 \end{figure*}
-
 \begin{figure*}[h!]
@@
 \vspace{2mm}
-\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
+\begin{tabularx}{\textwidth}{p{0.35\textwidth} XXXXXX}
 \hline
@@
 \ref{fig_cfd_velo}.
-\hl{With this in mind} a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Fig.
+With this in mind a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Fig.
 \ref{fig_cfd_temp} and Fig.\ref{fig_cfd_velo} respectively.
 With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Fig.
-\ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.\\
-
+\ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.
 \begin{table}[h!]
@@
 \vspace{2mm}
-\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
+\begin{tabularx}{\textwidth}{p{0.3\textwidth} XXXXXX}
 \hline
@@
 \end{table}
-
 \begin{figure*}[h!]
@@
 \end{figure*}
-\newpage
-\hl{The works of Dugum et al}\cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
+
+The works of Dugum et al \cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
 For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
@@
 \end{figure*}
-
 Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Fig.
@@
 \\
-
 \begin{figure*}[h!]
@@
 \end{figure*}
-
 The external tube metal temperatures, shown in Tab.
@@
 For comparison, at 100\% MCR load the maximum and mean temperatures reported for the platen and final SH are 500 \& 446 $[^\circ C]$ and 623 \& 531 $[^\circ C]$ respectively, with the final SH operating in the materials creep range \cite{Laubscher2019b}.
-Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.\\
-\newpage
+Thus, continued operation using the firing arrangement of Cases 2 and 5, could lead to SH failure.
+
 Using the process model of Fig.
@@
 However, with the lack of ATT-RH control, a sudden decrease in steam generation can lead to RH overheating and possible RH failure.
-Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.\\
-
+Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.
 \begin{table}[h!]
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.4\linewidth} XX}
+\begin{tabularx}{0.6\textwidth}{p{0.25\textwidth} XX}
 \hline
@@
 \end{table}
-\newpage
+
 Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
@@
 This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
-\newpage
-
 \section{Conclusions}
@@
 A validation case was first performed for the CFD model, which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
-The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.\\
+The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.
 
@@
 This firing arrangement also results in a higher unburnt carbon percentage at the exit flue-gas stream and therefore the lowest boiler utilization efficiency.
-\\
 
@@
 Higher $X_{CO}$ concentrations are observed near the bottom half of the furnace, along with high temperatures, which can lead to a high risk of fire side corrosion occurring at continuous low-load operation.
-\\
 
@@
 A 4.8\% decrease in unburnt carbon percentage is observed when operating using Case 3 in relation to Case 6.
-The predicted re-heater exit steam temperature of Case 3 is substantially closer to the desired temperature of 535 $[^\circ C]$, thus allowing for better control.\\
+The predicted re-heater exit steam temperature of Case 3 is substantially closer to the desired temperature of 535 $[^\circ C]$, thus allowing for better control.
 

### 2022-02-12 ASME_journal/journals-1.3/journals-1.3/TSEA-21-1636_FINAL_SUBMISSION.tex
Update 12/02/2022

@@
 
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.
+\newpage
 \section{Mathematical model}
@@
 To reduce the computational burden, it was assumed that the various processes were in steady-state.
-The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
+The governing equations for the gas phase are written below in their respective Reynolds averaged forms.
+
 Mass conservation:
+\vspace{-5mm}
 \begin{equation}\label{eqn_RANS_mass}
 \frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
+\vspace{-5mm}
 \end{equation}
+
 Momentum conservation:
+\vspace{-5mm}
 \begin{equation}\label{eqn_momentum}
 \frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
+\vspace{-5mm}
 \end{equation}
+\newpage
 Energy conservation:
+\vspace{-5mm}
 \begin{equation}\label{eqn_energy}
 \frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
+\vspace{-5mm}
 \end{equation}
+
 Species transport:
+\vspace{-5mm}
 \begin{equation}\label{eqn_species}
@@
 \end{equation}
+\vspace{-10mm}
 
 To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
+\vspace{-5mm}
 \begin{equation} \label{eqn_eff_rho}
 	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
+	\vspace{-5mm}
 \end{equation}
@@
 Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
+\vspace{-5mm}
 \begin{gather}
@@
 &R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
-&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
+&A_{vol} = 2\times10^5 [s^{-1}],\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
 \end{split}
 \end{gather}
+\vspace{-10mm}
 
@@
 (\ref{eqn_CO_reaction}).
+\vspace{-5mm}
 \begin{gather}
@@
 \end{gather}
+\vspace{-15mm}
+
 The diffusion and kinetic rates of Eqn.
@@
 (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
+\vspace{-5mm}
 \begin{gather}
@@
 &R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
-&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
+&A_{c} = 0.0053 [kg/m^2sPa],\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
 \end{split}
@@
 \end{gather}
+\vspace{-10mm}
 
@@
 A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
+\vspace{-3mm}
 \subsubsection{Particle modelling}
@@
 \ref{tab_scalars}.
+\vspace{-5mm}
 \begin{table}[h!]
@@
 $\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
-$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
+$\phi_{hp}$&Enthalpy of particle& Eqn. \eqref{eqn_phi_hp}\\
 \hline
 \end{tabularx}
+\vspace{-5mm}
 \end{table}
@@
 The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
+\vspace{-5mm}
 \begin{equation}\label{eqn_phi_hp}
 \frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=\left( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg} \right) \frac{1}{V} 
+\vspace{-5mm}
 \end{equation}
@@
 (\ref{eqn_RTE}).
+\vspace{-3mm}
 \begin{equation}\label{eqn_RTE}
 \frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\vspace{-5mm}
 \end{equation}
@@
 The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
+\vspace{-3mm}
 \begin{equation}
@@
 
+\vspace{-5mm}
 The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al \cite{Smith1982}.
@@
 (\ref{eqn_part_emisp}).
-\begin{gather}
-\alpha_p = \frac{\epsilon_p A_{pn}N_p}{V} \label{eqn_part_abs}\\
-\sigma_p = \frac{(1-\epsilon_p)(1-f_p) A_{pn}N_p}{V} \label{eqn_part_scat} \\
+\vspace{-3mm}
+\begin{equation}
+\alpha_p = \frac{\epsilon_p A_{pn}N_p}{V} \label{eqn_part_abs}
+\vspace{-15mm}
+\end{equation}
+\begin{equation}
+\sigma_p = \frac{(1-\epsilon_p)(1-f_p) A_{pn}N_p}{V} \label{eqn_part_scat}
+\vspace{-15mm}
+\end{equation}
+\begin{equation}
 E_p = \frac{\epsilon_p \sigma_{SB} T_p^4 A_{pn}N_p}{V}\label{eqn_part_emisp}
-\end{gather}
+\vspace{-8mm}
+\end{equation}
 
 It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
+\newpage
 \subsection{Process simulation model}
@@
 (\ref{eqn_mix_rho}) respectively.
-\begin{gather}
-\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
+\vspace{-5mm}
+\begin{equation}
+\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}
+\vspace{-15mm}
+\end{equation}
+\begin{equation}
 \rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
-\end{gather}
-Applying the mixture density the following transport equations are solved per process model component;
+\vspace{-10mm}
+\end{equation}
+%\begin{gather}
+%\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
+%\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
+%\vspace{-15mm}
+%\end{gather}
+
+Applying the mixture density the following transport equations are solved per process model component.
+\vspace{-5mm}
 \begin{equation}\label{eqn_mix_conti}
 \frac{\partial}{\partial t}(\rho_M A)+\frac{\partial}{\partial s}(\rho_MAu) = 0
+\vspace{-15mm}
 \end{equation}
@@
 \frac{1}{A} \frac{\partial}{\partial t}(\rho_M A u)+\frac{1}{A} \frac{\partial}{\partial s}(\rho_M A u^2) = -\frac{\partial p}{\partial s}-\frac{\tau_W P}{A}- \rho_M g \frac{\partial z}{\partial s}
+\vspace{-15mm}
 \end{equation}
 \begin{equation}\label{eqn_mix_energy}
-\begin{split}
-&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\\
-&\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
-\end{split}
+\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
+\vspace{-5mm}
 \end{equation}
@@
 \end{figure*}
-
+\newpage
 The boiler furnace is fed by six mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of six opposing wall mounted swirl burners.
@@
 \ref{fig_burner_mesh}.
-\newpage
-\begin{figure*}
+\begin{figure*}[h!]
 \centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
@@
 
-The CFD wall boundary conditions were modelled using ANSYS Fluent v19.5’s convection boundary condition type, which requires the internal free stream temperature, the internal heat transfer coefficient, wall thicknesses and material conductivities.Being a flux boundary condition the wall heat flux ($\dot{q}_{wall}$) can be calculated using Eqn.
+The CFD wall boundary conditions were modelled using ANSYS Fluent v19.5\textsuperscript{\textregistered}’s convection boundary condition type, which requires the internal free stream temperature, the internal heat transfer coefficient, wall thicknesses and material conductivities.Being a flux boundary condition the wall heat flux ($\dot{q}_{wall}$) can be calculated using Eqn.
 23.
+\vspace{-5mm}
 \begin{equation}\label{eqn_q_flux}
 \dot{q}_{wall} = U_i(T_{wall,i}-T_{water})
+\vspace{-5mm}
 \end{equation}
-The overall heat transfer coefficient (U) is subsequently determined using the following expression.
+
+The overall heat transfer coefficient ($U_i$) is subsequently determined using the following expression.
+\vspace{-10mm}
 \begin{equation}\label{eqn_overall_heat_coeff}
-U_i=\frac{1}{\frac{1}{h_{int}}+\frac{t_{wall}}{\lambda_{wall}}+\frac{t_{ash}}{\lambda_{ash}}}
+U_i=\left(\frac{1}{h_{int}}+\frac{t_{wall}}{\lambda_{wall}}+\frac{t_{ash}}{\lambda_{ash}}\right)^{-1}
+\vspace{-5mm}
 \end{equation}
@@
 For the validation cases the experimental data from site was used to estimate the mean water temperature in the heat exchangers.
-
+\newpage
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.5]{FLOWNEX_SETUP}
+\caption{Process model of boiler set-up including the downstream convective components using Flownex SE\textsuperscript{\textregistered} 2021}
+\label{fig_flownex}
+\end{figure*}
+\vspace{-5mm}
 The process model of the boiler configuration is shown in Fig.
@@
 \begin{figure*}[h!]
-\centering
-\includegraphics[scale=0.5]{FLOWNEX_SETUP}
-\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
-\label{fig_flownex}
+\centerline{\includegraphics[scale=0.45]{HEAT_EXCHANGER_PROCESS_MODEL}}
+\caption{Heat-exchanger component model}
+\label{fig_heat_exchanger_model}
 \end{figure*}
@@
 
-Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}).
-\begin{figure*}[h!]
-\centerline{\includegraphics[scale=0.4]{HEAT_EXCHANGER_PROCESS_MODEL}}
-\caption{Heat-exchanger component model}
-\label{fig_heat_exchanger_model}
-\end{figure*}
-
+Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model.
+This component is used for the heat exchangers downstream of SH3 (refer to Fig.
+\ref{fig_flownex}).
 The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side.
@@
 \subsection{Model inputs}
-Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.\\
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.
 \begin{table}[h!]
@@
 \hline
-\vspace{0pt}
 \end{tabularx}
@@
 For this study six cases are simulated with the following three burner firing configurations being investigated:
-\newpage
 \begin{enumerate}
@@
 \centering
-\caption{Case 1 to 6 model inputs on a per burner basis.}
+\caption{Case 1 to 6 model inputs on a per burner basis}
 \label{tbl_case_inputs}
@@
 \end{tabularx}}
-\vspace{0pt}
 \end{table}
-
+\newpage
 A secondary air flow rate of 5 kg/s is typically fed through the non-firing burners, to ensure sufficient cooling of the burner and mixing of fuel and air in the combustion chamber, with these three cases numbered 1, 2 and 3.
@@
 To ensure that the results are grid size independent, simulations were also performed for mesh sizes of 3.5 million and 10 million cells during the validation study, discusses in Section \ref{sec_model_valid}.
-To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively\\ %.
+To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively.
+
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
@@
 was used to discretize the pressure equation.
-The scalar field equations used a second-order upwind scheme.\\
+The scalar field equations used a second-order upwind scheme.
+
 The spatial discretization for all fields (except pressure) was set to first-order upwind for the first 1000 iterations to ensure a stable solution, after which the discretization order was increased to the above mentioned criteria.
@@
 \end{figure*}
-
+\newpage
 Figure \ref{fig_heat_valid} shows that the calculated overall heat loads are in good agreement with the measured values where the model results are within the associated uncertainty range in all but one case.
@@
 The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].
+\vspace{-3mm}
 \begin{figure*}[h!]
@@
 \end{figure*}
+\vspace{-15mm}
 
@@
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
-The temperature and velocity profiles for the various firing arrangements are shown in Fig.
-\ref{fig_cfd_temp} and Fig.
-\ref{fig_cfd_velo} respectively.
-With the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
-This is further exacerbated when considering Tab.
-\ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
-The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Fig.
-\ref{fig_cfd_temp}).
-This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Tab.
-\ref{tbl_process_parameters}.
 \begin{figure*}[h!]
@@
 \end{figure*}
+The temperature and velocity profiles for the various firing arrangements are shown in Fig.
+\ref{fig_cfd_temp} and Fig.
+\ref{fig_cfd_velo} respectively.
+With the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake.
+This is further exacerbated when considering Tab.
+\ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies.
+The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Fig.
+\ref{fig_cfd_temp}).
+This leads to the highest steam generation rate in the furnace and boiler efficiency as shown in Tab.
+\ref{tbl_process_parameters}.
+
 \begin{figure*}[h!]
@@
 \end{figure*}
+\newpage
+\begin{figure*}[h!]
+\centering
+\includegraphics[width = 5in]{HEATFLUX_KEY} [$W/m^2$]\\
+\subfigure[Case 1]{\includegraphics[width=0.18\textwidth]{BOT_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 2]{\includegraphics[width=0.2\textwidth]{MID_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 3]{\includegraphics[width=0.2\textwidth]{FBRM_HEATFLUX}}\\
+\subfigure[Case 4]{\includegraphics[width=0.18\textwidth]{BOT05_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 5]{\includegraphics[width=0.2\textwidth]{MID05_HEATFLUX}}
+\hspace{10mm}
+\subfigure[Case 6]{\includegraphics[width=0.2\textwidth]{FBRM05_HEATFLUX}}
+\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
+\label{fig_cfd_heat_flux}
+\vspace{-3mm}
+\end{figure*}
+
+Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
+Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{ugum2019}.
+An even distribution of heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
+Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
+This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Fig.
+\ref{fig_cfd_velo}.
+With this in mind a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Fig.
+\ref{fig_cfd_temp} and Fig.\ref{fig_cfd_velo} respectively.
+With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Fig.
+\ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to the corresponding Cases 1, 2 and 3.
+
+The works of Dugum et al \cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
+For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
+Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
+The figures generally highlight the location and distribution of the flame core for each case.
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.
 \begin{table}[h!]
@@
 \end{tabularx}
+\vspace{-15mm}
 \end{table}
-\newpage
-Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
-Both cases 1 and 4 highlight high heat flux zones near the burner inlets which, in the presence of high temperatures and incomplete combustion near these regions, can lead to high-temperature corrosion \cite{ugum2019}.
-An even distribution of heat fluxes is seen in Cases 3 and 6 with minimal localised heat flux concentrations being observed.
-Cases 2 and 5 show that most of the heat is absorbed in the upper half of the boiler with Case 5 showing a higher heat flux on the rear wall.
-This could be due the use of a lower SA flowrate leading to higher velocity profiles developing closer to the rear wall, as seen in Fig.
-\ref{fig_cfd_velo}.
-With this in mind a lower SA flowrate, in general leads to hot gases and velocity profiles impinging closer to the furnace walls, which can be seen in Cases 4, 5 and 6 of Fig.
-\ref{fig_cfd_temp} and Fig.\ref{fig_cfd_velo} respectively.
-With high gas temperatures and high velocity impingement, Cases 4, 5 and 6 (of Fig.
-\ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.
 \begin{table}[h!]
@@
 \end{tabularx}
+\vspace{-15mm}
 \end{table}
-\begin{figure*}[h!]
-\centering
-\includegraphics[width = 5in]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[Case 1]{\includegraphics[width=0.18\textwidth]{BOT_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 2]{\includegraphics[width=0.2\textwidth]{MID_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 3]{\includegraphics[width=0.2\textwidth]{FBRM_HEATFLUX}}\\
-\subfigure[Case 4]{\includegraphics[width=0.18\textwidth]{BOT05_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 5]{\includegraphics[width=0.2\textwidth]{MID05_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 6]{\includegraphics[width=0.2\textwidth]{FBRM05_HEATFLUX}}
-\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
-\label{fig_cfd_heat_flux}
-\end{figure*}
-
-The works of Dugum et al \cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
-For low-load operation this phenomenon becomes important to avoid since combustion instability can lead to these non-ideal circumstances.
-Figure \ref{fig_cfd_coppm} shows the $CO$ molar concentration in the domain located on an iso-surface set 1600 $[K]$.
-The figures generally highlight the location and distribution of the flame core for each case.
-Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.\\
 \begin{figure*}[h!]
@@
 \label{fig_cfd_coppm}
+\vspace{-5mm}
 \end{figure*}
+
 Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Fig.
@@
 It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
-\\
 \begin{figure*}[h!]
 \centering
-\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.45]{SYMMETRY_PROBE_COPPM}}
+\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.47]{SYMMETRY_PROBE_COPPM}}
 \hspace{5mm}
-\subfigure[Offset vertical plot]{\includegraphics[scale = 0.45]{OFFSET_PROBE_COPPM}}
+\subfigure[Offset vertical plot]{\includegraphics[scale = 0.47]{OFFSET_PROBE_COPPM}}
 \hspace{5mm}
@@
 \end{figure*}
+
 The external tube metal temperatures, shown in Tab.
@@
 Fouling thermal resistances of 0.0067 and 0.015 [$m^2K/W$] were used for the platen and final SH respectively.
+\vspace{-5mm}
 \begin{equation}\label{eqn_t_wall}
 T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
+\vspace{-5mm}
 \end{equation}
@@
 \end{tabularx}}
+\vspace{-10mm}
 \end{table}
@@
 Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
-It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$ 10\% being transferred via convection at low-load.
+It can be seen that heat transfer to the furnace and radiant SHs are dominated by radiation, with approximately $\pm$10\% being transferred via convection at low-load.
 Considering the convective pass heat exchangers (RH2 through to the EC, refer to Figure \ref{fig_flownex}) the convective heat transfer becomes more apparent as seen with the reduction in radiative heat transfer percentage.

### 2022-02-14 ASME_journal/journal-1.1 FINAL/JOURNAL_MANUSCRIPT_BRAD_RAWLINS.tex
Update 14/02/2022

--- 2022-02-11 ASME_journal/journals-1.3/journals-1.3/TSEA-21-1636_FINAL_SUBMISSION.tex
@@
 %              Integration Engineering Laboratory                    %
-%              Department of Mechanical and Aerospace Engineering    %
+%              Department of Mechanical and Aeronautical Engineering %
 %              University of California                              %
@@
 % Modified: January  01, 2003 by Geoffrey R. Shiflett                %
-% Modified: July 19, 2009 as a template in a single column for       %
-%           ASME Journals by Harry H. Cheng                          %
 % Use at your own risk, send complaints to /dev/null                 %
@@
 
-%%% use 10pt options with the asme2ej format
-%\documentclass[10pt]{asme2ej}
-\documentclass[11pt,cleanfoot]{asme2ej}
+%%% use twocolumn and 10pt options with the asme2ej format
+\documentclass[twocolumn,10pt]{asme2ej}
 
+\usepackage{graphicx} %% for loading jpg figures
 \usepackage{tabu}
@@
 
-\usepackage{graphicx} %% for loading jpg figures
-\usepackage{epsfig}
-\usepackage{fancyhdr}
-\usepackage{setspace}
-\usepackage{helvet}
-\usepackage[hyphens]{url}
-%\usepackage{hyphens}
-\renewcommand{\familydefault}{\sfdefault}
-\pagestyle{fancy}
-\lhead{{\it Journal of Thermal Science and Engineering Applications}}
-\rhead{}
-\renewcommand{\headrulewidth}{0pt}
-\topmargin 80 pt
-\headheight 14 pt
-\headsep 30 pt
-%\RequirePackage[hyphens]
-\usepackage{hyperref}   % to set up hyperlinks
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue,
-	citecolor=blue,
-	urlcolor=blue,
-}
-\usepackage[square,numbers]{natbib}
-
+\newcommand{\highlight}[1]{%
+  \colorbox{yellow!}{$\displaystyle#1$}}
 %% The class has several options
@@
     }
+
 }
@@
 \maketitle
-\doublespacing
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{nomenclature}
-\begin{multicols}{2}
-\entry{\textbf{\textit{Variables}}}{}
+\entry{}{\textbf{\textit{Variables}}}
 \entry{$A$}{Area [$m^2$]}
@@
 \entry{$E_p$}{Particle emission power [$W/m^3$]}
-\entry{$f_{heat}$}{Surface char oxidation fraction [-]}
-\entry{$f_{p}$}{Forward scattering factor [-]}
+\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
+\entry{$f_{p}$}{Forward scattering factor [$-$]}
 \entry{$G$}{Incident radiation [$W/m^2$]}
@@
 \entry{$m_{vol}$}{Mass of volatiles [$kg$]}
-\entry{$N_{p}$}{Number of particles [-]}
+\entry{$N_{p}$}{Number of particles [$-$]}
 \entry{$P$}{Perimeter [$m$]}
@@
 \entry{$t$}{Time [$s$]}
-\entry{$U_i$}{Overall heat transfer coefficient}
-\entry{}{[$W/m^2K$]}
+\entry{$U_i$}{Over heat transfer coefficient [$W/m^2K$]}
 \entry{$u$}{Velocity [$m/s$]}
@@
 \entry{$Y_k$}{Species mass fraction [$kg/kg$]}
-\entry{$x$}{Quality [-]}
-\entry{\textbf{\textit{Greek Variables}}}{}
+\entry{$x$}{Quality [$-$]}
+\entry{}{\textbf{\textit{Greek Variables}}}
 \entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
-\entry{$\alpha_H$}{Mixture void fraction [-]}
+\entry{$\alpha_H$}{Mixture void fraction [$-$]}
 \entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
-\entry{$\epsilon_p$}{Particle emissivity [-]}
+\entry{$\epsilon_p$}{Particle emissivity [$-$]}
 \entry{$\rho$}{Gas density [$kg/m^3$]}
@@
 \entry{$\rho_p$}{Particle density [$kg/m^3$]}
-\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant}
-\entry{}{[$W/m^2K^4$]}
+\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
 \entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
-\entry{$\phi$}{Scalar variable [-]}
-\entry{\textbf{\textit{Abbreviations}}}{}
+\entry{$\phi$}{Scalar variable [$-$]}
+\entry{}{\textbf{\textit{Abbreviations}}}
 \entry{$MCR$}{Maximum continuous rating}
@@
 \entry{$EC$}{Economiser}
-\end{multicols}
 \end{nomenclature}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 However, to the authors’ knowledge, the integration of a 1-D process model with a detail CFD model has not been used to investigate the steam side operational performance of a CFPP boiler specifically at low-load.
-The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\
+The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.
+
 To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements.
 Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.
+
 \section{Mathematical model}
@@
 To reduce the computational burden, it was assumed that the various processes were in steady-state.
-The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
+The governing equations for the gas phase are written below in their respective Reynolds averaged forms.
 Mass conservation:
@@
 \end{gather}
+
 The diffusion and kinetic rates of Eqn.
@@
 A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
+
 \subsubsection{Particle modelling}
@@
 \ref{tab_scalars}.
+
 \begin{table}[h!]
@@
 \vspace{2mm}     
-\begin{tabularx}{0.8\textwidth}{p{0.1\textwidth} p{0.4\textwidth} l}
+\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
 \hline
@@
 \begin{equation}\label{eqn_phi_hp}
-\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=\left( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg} \right) \frac{1}{V} 
+\begin{split}
+&\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} -\\
+&\frac{dm_{evap}}{dt}h_{fg}) \frac{1}{V} 
+\end{split}
 \end{equation}
@@
 To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.
+
 \subsection{Heat transfer modelling}
@@
 \begin{equation}\label{eqn_RTE}
-\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\begin{split}
+&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
+&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
+\end{split}
 \end{equation}
@@
 It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
+\begin{figure*} 
+\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
+\caption{Boiler geometry and layout}
+\label{fig_geometry}
+\end{figure*}
+\begin{figure*}
+\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
+\caption{Burner layout and mesh details}
+\label{fig_burner_mesh}
+\end{figure*}
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.5]{FLOWNEX_SETUP}
+\caption{Process model of boiler set-up including the downstream convective components using Flownex SE\textsuperscript{\textregistered} 2021}
+\label{fig_flownex}
+\end{figure*}
 \subsection{Process simulation model}
@@
 Applying the mixture density the following transport equations are solved per process model component;
+
 \begin{equation}\label{eqn_mix_conti}
@@
 The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects on the water-side of the boiler system.
+
 \section{Case study boiler description \& set-up}
@@
 fuel characteristics and boundary conditions) and the numerical solution strategy.
+
 \subsection{Geometry \& process model set-up} \label{sec_set_up}
@@
 Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.
-\begin{figure*} [h!]
-\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
-\caption{Boiler geometry and layout}
-\label{fig_geometry}
-\end{figure*}
 
@@
 \ref{fig_burner_mesh}.
-\newpage
-\begin{figure*}
-\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
-\caption{Burner layout and mesh details}
-\label{fig_burner_mesh}
-\end{figure*}
 
-The CFD wall boundary conditions were modelled using ANSYS Fluent v19.5’s convection boundary condition type, which requires the internal free stream temperature, the internal heat transfer coefficient, wall thicknesses and material conductivities.Being a flux boundary condition the wall heat flux ($\dot{q}_{wall}$) can be calculated using Eqn.
-23.
+The CFD wall boundary conditions were modelled using ANSYS Fluent v19.5\textsuperscript{\textregistered}’s convection boundary condition type, which requires the internal free stream temperature, the internal heat transfer coefficient, wall thicknesses and material conductivities.Being a flux boundary condition the wall heat flux ($\dot{q}_{wall}$) can be calculated using Eqn.
+\ref{eqn_q_flux}.
 \begin{equation}\label{eqn_q_flux}
@@
 \begin{equation}\label{eqn_overall_heat_coeff}
-U_i=\frac{1}{\frac{1}{h_{int}}+\frac{t_{wall}}{\lambda_{wall}}+\frac{t_{ash}}{\lambda_{ash}}}
+U_i=\left(\frac{1}{h_{int}}+\frac{t_{wall}}{\lambda_{wall}}+\frac{t_{ash}}{\lambda_{ash}}\right)^{-1}
 \end{equation}
@@
 As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.
-\begin{figure*}[h!]
-\centering
-\includegraphics[scale=0.5]{FLOWNEX_SETUP}
-\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
-\label{fig_flownex}
-\end{figure*}
 
@@
 
-Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}).
+Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model.
+This component is used for the heat exchangers downstream of SH3 (refer to Fig.
+\ref{fig_flownex}).
+The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side.
+The total heat transferred to the water-side control volume can be written as the sum of the absorbed direct radiation and the combined convective and gas radiative heat transfer (i.e.
+$\dot{Q}_{steam}=\dot{Q}_{abs}+\dot{Q}_{cr}$).
+The external heat transfer coefficient, from the flue-gas to the heat-exchanger walls makes use of the Gnielinski correlation \cite{Gnielinski2016} for the various heat-exchanger tube arrangements.
+Figure \ref{fig_heat_exchanger_model} incorporates the direct radiative interactions in each heat-exchanger.
+It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
 \begin{figure*}[h!]
@@
 
-The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side.
-The total heat transferred to the water-side control volume can be written as the sum of the absorbed direct radiation and the combined convective and gas radiative heat transfer (i.e.
-$\dot{Q}_{steam}=\dot{Q}_{abs}+\dot{Q}_{cr}$).
-The external heat transfer coefficient, from the flue-gas to the heat-exchanger walls makes use of the Gnielinski correlation \cite{Gnielinski2016} for the various heat-exchanger tube arrangements.
-Figure \ref{fig_heat_exchanger_model} incorporates the direct radiative interactions in each heat-exchanger.
-It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
+\subsection{Model inputs}
+Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.
 
-\subsection{Model inputs}
-Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.\\
 \begin{table}[h!]
@@
 \label{tbl_fuel}
-\begin{tabularx}{0.7\textwidth}{p{0.3\textwidth} p{0.2\textwidth} l}
+\begin{tabularx}{3.25in}{p{1.5in} p{0.8in} l}
 \hline
@@
 \end{tabularx}
+\vspace{-10mm}
 \end{table}
@@
 For this study six cases are simulated with the following three burner firing configurations being investigated:
-\newpage
+
 \begin{enumerate}
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{0.7\textwidth}{p{0.27\textwidth} p{0.225\textwidth} l}
+\begin{tabularx}{3.25in}{p{1.4in} p{0.75in} l}
 \hline
@@
 \end{tabularx}}
-\vspace{0pt}
+
 \end{table}
@@
 A numerical mesh consisting of approximately 6 million cells was used for the CFD simulations of this current study.
-To ensure that the results are grid size independent, simulations were also performed for mesh sizes of 3.5 million and 10 million cells during the validation study, discusses in Section \ref{sec_model_valid}.
-To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively\\ %.
+To ensure that the results are grid size independent, simulations were also performed for mesh sizes of 3.5 million and 10 million cells during the validation study, discusses in Section 4.1.
+To ensure numerical stability during simulation the aspect ratio and mesh orthogonality quality where kept below 20 and above 0.2 respectively.
+%\ref{sec_model_valid}.
+
 The CFD simulations were performed using ANSYS Fluent v19.5\textsuperscript{\textregistered} pressure-based solver.
@@
 The remaining fields were solved till convergence.
+
 \section{Results \& discussion}
@@
 The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
-\begin{figure*}[h]
-\centerline{\includegraphics[scale = 0.425]{VALIDATION}}
-\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
-\label{fig_heat_valid}
-\end{figure*}
 
@@
 The probe is inserted from the side walls to a depth of 4.5 [$m$], and measurements were taken every 0.5 [$m$].
-\begin{figure*}[h!]
+
+\begin{figure*}[h]
+\centerline{\includegraphics[scale = 0.4]{VALIDATION}}
+\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
+\label{fig_heat_valid}
+\end{figure*}
+\begin{figure}[h!]
 \centering
-\subfigure[]{\includegraphics[width = 0.475\textwidth, height =5cm ]{COPPM_VALID}}
+\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{COPPM_VALID}}
 \hspace{5mm}
-\subfigure[]{\includegraphics[width = 0.475\textwidth, height =5cm ]{XO2_VALID}}
+\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{XO2_VALID}}
 \caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
 \label{fig_probe_valid}
-\end{figure*}
-
+\end{figure}
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
 It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.
+
 \subsection{Simulation results for various burner firing arrangements at 32\% MCR }
@@
 \ref{tbl_process_parameters}.
+
 \begin{figure*}[h!]
@@
 \end{figure*}
+
 \begin{figure*}[h!]
@@
 \vspace{2mm}
-\begin{tabularx}{\textwidth}{p{0.35\textwidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
 \hline
@@
 \ref{fig_cfd_heat_flux}) experience concentrated heat fluxes around the burner inlets in comparison to corresponding Cases 1, 2 and 3.
+
 \begin{table}[h!]
@@
 \vspace{2mm}
-\begin{tabularx}{\textwidth}{p{0.3\textwidth} XXXXXX}
+\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
 \hline
@@
 \end{tabularx}
+\vspace{-10mm}
 \end{table}
+
 \begin{figure*}[h!]
@@
 \end{figure*}
-
+\newpage
 The works of Dugum et al \cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
@@
 The figures generally highlight the location and distribution of the flame core for each case.
-Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.\\
+Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.
 \begin{figure*}[h!]
@@
 \end{figure*}
+
 Investigating the combustion stability for all the cases, the symmetry and offset vertical probe plots (as highlighted in Fig.
@@
 It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
-\\
+
 \begin{figure*}[h!]
@@
 Considering all of the above, Cases 3 and 6 are seen as the best firing arrangements for continuous low-load operation at a load of 32\% MCR.
+
 \begin{table}[h!]
@@
 {\tabulinesep=1.2mm
-\begin{tabularx}{0.6\textwidth}{p{0.25\textwidth} XX}
+\begin{tabularx}{\linewidth}{p{0.4\linewidth} XX}
 \hline
@@
 \end{tabularx}}
+\vspace{-10mm}
 \end{table}
-
+\newpage
 Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
@@
 This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
+\newpage
+
 \section{Conclusions}
@@
 A validation case was first performed for the CFD model, which showed adequate results for heat fluxes to the walls, with a general tendency of the model to under-predict the heat fluxes to the furnace.
-The model also showed sufficient accuracy in determining the combustion characteristics at the 100 \% MCR load.
+The model also showed sufficient accuracy in determining the combustion characteristics at the 100\% MCR load.
 
@@
 Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, Case 3 is considered to be the best operational strategy at this low load for the boiler under investigation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{acknowledgment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2022-03-04 ASME_journal/journal-1.1 FINAL/TEXT_SUBMISSION/TEXT_MANUSCRIPT_BRAD_RAWLINS.tex
update - 04/03/2022

--- 2022-02-14 ASME_journal/journal-1.1 FINAL/JOURNAL_MANUSCRIPT_BRAD_RAWLINS.tex
@@
 %%% use twocolumn and 10pt options with the asme2ej format
-\documentclass[twocolumn,10pt]{asme2ej}
+\documentclass[11pt,cleanfoot]{asme2ej}
 
-\usepackage{graphicx} %% for loading jpg figures
 \usepackage{tabu}
@@
 \usepackage{xcolor}
+\usepackage{enumitem}
 
-\newcommand{\highlight}[1]{%
-  \colorbox{yellow!}{$\displaystyle#1$}}
-%% The class has several options
-%  onecolumn/twocolumn - format for one or two columns per page
-%  10pt/11pt/12pt - use 10, 11, or 12 point font
-%  oneside/twoside - format for oneside/twosided printing
-%  final/draft - format for final/draft copy
-%  cleanfoot - take out copyright info in footer leave page number
-%  cleanhead - take out the conference banner on the title page
-%  titlepage/notitlepage - put in titlepage or leave out titlepage
-%  
-%% The default is oneside, onecolumn, 10pt, final
+\usepackage{graphicx} %% for loading jpg figures
+\usepackage{epsfig}
+\usepackage{fancyhdr}
+\usepackage{setspace}
+\usepackage{helvet}
+\usepackage[hyphens]{url}
+%\usepackage{hyphens}
+\renewcommand{\familydefault}{\sfdefault}
+\pagestyle{fancy}
+\lhead{{\it Journal of Thermal Science and Engineering Applications}}
+\rhead{}
+\renewcommand{\headrulewidth}{0pt}
+\topmargin 80 pt
+\headheight 14 pt
+\headsep 30 pt
+%\RequirePackage[hyphens]
+\usepackage{hyperref}   % to set up hyperlinks
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	citecolor=blue,
+	urlcolor=blue,
+}
+\usepackage[square,numbers]{natbib}
+\addtolength{\jot}{3mm}
 
@@
 \begin{nomenclature}
+\begin{multicols}{2}
 \entry{}{\textbf{\textit{Variables}}}
@@
 \entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
-\entry{$\alpha_H$}{Mixture void fraction [$-$]}
+\entry{$\alpha_H$}{Mixture void fraction [-]}
 \entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
-\entry{$\epsilon_p$}{Particle emissivity [$-$]}
+\entry{$\epsilon_p$}{Particle emissivity [-]}
 \entry{$\rho$}{Gas density [$kg/m^3$]}
@@
 \entry{$EC$}{Economiser}
+\end{multicols}
 \end{nomenclature}
@@
 Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions.
-CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).
+CFD simulations have been successfully used to model a variety of CFPP boiler types \cite{Laubscher2019a, Gu2020} and cover various aspects such as pollution control \cite{Du2017, Fan2001}, gas-solid flow effects \cite{Chen2017} and boiler retrofitting \cite{Gu2020, He2007}.
 
@@
 In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem.
-This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners.
+This model has been successfully used by researchers (\cite{Belosevic2019a, Laubscher2019a, Modlinski2019}), in modelling the effects of coal-fired swirl burners.
 The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.
@@
 &R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
-&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
+&A_{vol} = 2\times10^5 [s^{-1}],\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
 \end{split}
@@
 
-A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.
+A devolatilization temperature of 553 $K$ \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.
 
@@
 
-\begin{table}[h!]
-\centering
-\caption{Scalar field equation descriptions}\label{tab_scalars}  
-\vspace{2mm}     
-\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
-\hline
-Variable &Description& Transport equation \\
-\hline
-$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
-$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
-$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
-$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
-$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
-$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
-\hline
-\end{tabularx}
-\end{table}
-
 The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
 \begin{equation}\label{eqn_phi_hp}
-\begin{split}
-&\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} -\\
-&\frac{dm_{evap}}{dt}h_{fg}) \frac{1}{V} 
-\end{split}
+\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} -\frac{dm_{evap}}{dt}h_{fg}) \frac{1}{V} 
 \end{equation}
@@
 The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$.
-This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}).
+This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach \cite{Benim2005, Vicente2003, Cai2015}.
 The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.
@@
 \begin{equation}\label{eqn_RTE}
-\begin{split}
-&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
-&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
-\end{split}
+\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
 \end{equation}
@@
 It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
-\begin{figure*} 
-\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
-\caption{Boiler geometry and layout}
-\label{fig_geometry}
-\end{figure*}
-\begin{figure*}
-\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
-\caption{Burner layout and mesh details}
-\label{fig_burner_mesh}
-\end{figure*}
-\begin{figure*}[h!]
-\centering
-\includegraphics[scale=0.5]{FLOWNEX_SETUP}
-\caption{Process model of boiler set-up including the downstream convective components using Flownex SE\textsuperscript{\textregistered} 2021}
-\label{fig_flownex}
-\end{figure*}
+
 \subsection{Process simulation model}
@@
 \alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\ 
+\vspace{5mm}
 \rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
@@
 \begin{equation}\label{eqn_mix_energy}
-\begin{split}
-&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\\
-&\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
-\end{split}
+\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
 \end{equation}
@@
 Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the higher heating value (HHV) of the fuel.
-
-\begin{table}[h!]
-\centering
-\caption{Utility boiler fuel characteristics}
-\vspace{2mm}
-\label{tbl_fuel}
-\begin{tabularx}{3.25in}{p{1.5in} p{0.8in} l}
-\hline
-\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
-\hline
-\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
-Carbon & $0.7753$ & $kg/kg_{fuel}$\\
-Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
-Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
-Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
-Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
-\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
-Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
-Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
-Ash & $0.4090$ & $kg/kg_{fuel}$\\
-Moisture & $0.0550$ & $kg/kg_{fuel}$\\
-\hline
-\textbf{Energy content - (DAF)} & \textbf{Value} &\\
-\hline
-Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
-\hline
-\vspace{0pt}
-\end{tabularx}
-\vspace{-10mm}
-\end{table}
 
@@
 \end{enumerate}
-\begin{table}[h!]
-\centering
-\caption{Case 1 to 6 model inputs on a per burner basis.}
-\label{tbl_case_inputs}
-\vspace{2mm}
-{\tabulinesep=1.2mm
-\begin{tabularx}{3.25in}{p{1.4in} p{0.75in} l}
-\hline
-Active burners & \textbf{Cases 1 - 3} & \textbf{Cases 4 - 6}\\
-\hline
-\textbf{Fuel flowrate} [$kg/s$]&3.14  &3.14\\
-\textbf{PA flowrate} [$kg/s$]&4.95  &4.95\\
-\textbf{SA flowrate} [$kg/s$]&14.85  &14.85\\
-\hline
-Non firing burners &  & \\
-\hline
-\textbf{SA flowrate} [$kg/s$]&5.0  &2.5\\
-\hline
-Input air temperatures& &\\
-\hline
-\textbf{PA} [$K$]&373  &373\\
-\textbf{SA} [$K$]&520  &510\\
-\hline
-\textbf{Excess air coefficients} & 1.37 & 1.32\\
-\hline
-\end{tabularx}}
-
-\end{table}
 
@@
 Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy.
-The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
+The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b, Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.
 
@@
 
-\begin{figure*}[h]
-\centerline{\includegraphics[scale = 0.4]{VALIDATION}}
-\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
-\label{fig_heat_valid}
-\end{figure*}
-\begin{figure}[h!]
-\centering
-\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{COPPM_VALID}}
-\hspace{5mm}
-\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{XO2_VALID}}
-\caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
-\label{fig_probe_valid}
-\end{figure}
 Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions.
@@
 
-\begin{figure*}[h!]
-\centering
-\includegraphics[width = 5in]{TEMP_KEY} [$K$]\\
-\subfigure[Case 1]{\includegraphics[width=0.25\textwidth]{BOT_TEMP}}
-\subfigure[Case 2]{\includegraphics[width=0.25\textwidth]{MID_TEMP}}
-\subfigure[Case 3]{\includegraphics[width=0.25\textwidth]{FBRM_TEMP}}\\
-\subfigure[Case 4]{\includegraphics[width=0.25\textwidth]{BOT05_TEMP}}
-\subfigure[Case 5]{\includegraphics[width=0.25\textwidth]{MID05_TEMP}}
-\subfigure[Case 6]{\includegraphics[width=0.25\textwidth]{FBRM05_TEMP}}
-\caption{Temperature fields for Cases 1 through 6 [(a)-(f)]}
-\label{fig_cfd_temp}
-\end{figure*}
-
-\begin{figure*}[h!]
-\centering
-\includegraphics[width = 5in]{VEL_KEY} [$m/s$]\\
-\subfigure[Case 1]{\includegraphics[width=0.25\textwidth]{BOT_VEL}}
-\subfigure[Case 2]{\includegraphics[width=0.25\textwidth]{MID_VEL}}
-\subfigure[Case 3]{\includegraphics[width=0.25\textwidth]{FBRM_VEL}}\\
-\subfigure[Case 4]{\includegraphics[width=0.25\textwidth]{BOT05_VEL}}
-\subfigure[Case 5]{\includegraphics[width=0.25\textwidth]{MID05_VEL}}
-\subfigure[Case 6]{\includegraphics[width=0.25\textwidth]{FBRM05_VEL}}
-\caption{Velocity fields for Cases 1 through 6 [(a)-(f)]}
-\label{fig_cfd_velo}
-\end{figure*}
-\begin{table}[h!]
-\centering
-\caption{Furnace exit conditions and SH wall temperatures}
-\vspace{2mm}
-\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
-\hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
-\hline
-\multicolumn{7}{l}{\textit{Furnace exit}}\\
-\textbf{Exit temperature} [$K$] & 1168 & 1230 & 1215 & 1208 & 1306 & 1298\\
-\textbf{Unburnt carbon} [$(\times 10^{-3})\,\%$] & 1.83 & 1.94 & 1.54 & 1.81 & 1.89 & 1.62\\
-\multicolumn{7}{l}{\textit{Platen SH}}\\
-\textbf{Max wall temperature} [$^{\circ}C$]  &477 & 492 & 481  & 480 & 493 & 490\\
-\textbf{Mean wall temperature} [$^{\circ}C$] &439 & 453 & 446 & 454 & 442 & 451\\
-\multicolumn{7}{l}{\textit{Final SH}}\\
-\textbf{Max wall temperature} [$^{\circ}C$]  & 602 & 624 & 608 & 595 & 626 & 612\\
-\textbf{Mean wall temperature} [$^{\circ}C$] & 520 & 523 & 517 & 512 & 520 & 511\\
-\hline
-\label{tbl_cfd_results}
-\end{tabularx}
-\vspace{-10mm}
-\end{table}
-\newpage
 Figure \ref{fig_cfd_heat_flux} illustrates the heat flux profiles for the simulated cases.
@@
 
-\begin{table}[h!]
-\centering
-\caption{Process model control parameters}
-\vspace{2mm}
-\begin{tabularx}{\linewidth}{p{1in} XXXXXX}
-\hline
-&\multicolumn{6}{c}{Cases}\\
- & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
-\hline
-\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
-\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
-\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
-\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
-\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
-\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
-\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
-\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
-\hline
-\label{tbl_process_parameters}
-\end{tabularx}
-\vspace{-10mm}
-\end{table}
-
-\begin{figure*}[h!]
-\centering
-\includegraphics[width = 5in]{HEATFLUX_KEY} [$W/m^2$]\\
-\subfigure[Case 1]{\includegraphics[width=0.18\textwidth]{BOT_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 2]{\includegraphics[width=0.2\textwidth]{MID_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 3]{\includegraphics[width=0.2\textwidth]{FBRM_HEATFLUX}}\\
-\subfigure[Case 4]{\includegraphics[width=0.18\textwidth]{BOT05_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 5]{\includegraphics[width=0.2\textwidth]{MID05_HEATFLUX}}
-\hspace{10mm}
-\subfigure[Case 6]{\includegraphics[width=0.2\textwidth]{FBRM05_HEATFLUX}}
-\caption{Heat fluxes profiles for Cases 1 through 6 [(a)-(f)]}
-\label{fig_cfd_heat_flux}
-\end{figure*}
-\newpage
 The works of Dugum et al \cite{ugum2019}, highlights the issue of high-temperature corrosion caused by significant levels of $CO$ ($X_{CO}$ 0.01 - 0.1) and no-free $O_2$ near regions of high wall temperatures.
@@
 Cases 1 and 4 illustrate the highest likelihood of high-temperature corrosion occurring near the furnace hopper, due to the high concentration and temperatures in that region.
-\begin{figure*}[h!]
-\centering
-\includegraphics[width = 5in]{CO_MF_KEY} [$X_{CO}$]\\
-\subfigure[Case 1]{	\includegraphics[width=0.16\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
-\hspace{5mm}
-\subfigure[Case 2]{	\includegraphics[width=0.16\textwidth, height = 7cm]{MID_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
-\hspace{5mm}
-\subfigure[Case 3]{	\includegraphics[width=0.16\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
-\subfigure[Case 4]{	\includegraphics[width=0.16\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
-\hspace{5mm}
-\subfigure[Case 5]{	\includegraphics[width=0.16\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
-\hspace{5mm}
-\subfigure[Case 6]{	\includegraphics[width=0.16\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
-				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}
-\caption{CO molar fraction ($X_{CO}$) concentrations for 
-Cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
-\label{fig_cfd_coppm}
-\end{figure*}
 
@@
 It is important to note the effects of a lower SA mass flow rate has on the furnace exit conditions for non-firing burners, which generally leads to a hotter exit gas temperature as seen with Cases 4 to 6.
-
-\begin{figure*}[h!]
-\centering
-\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.45]{SYMMETRY_PROBE_COPPM}}
-\hspace{5mm}
-\subfigure[Offset vertical plot]{\includegraphics[scale = 0.45]{OFFSET_PROBE_COPPM}}
-\hspace{5mm}
-\subfigure[Symmetry vertical plot]{\includegraphics[scale = 0.45]{SYMMETRY_PROBE_XO2}}
-\hspace{5mm}
-\subfigure[Offset vertical plot]{\includegraphics[scale = 0.45]{OFFSET_PROBE_XO2}}
-\caption{$CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines}
-\label{fig_cfd_probe}
-\end{figure*}
 
@@
 
-\begin{table}[h!]
-\centering
-\caption{Radiative heat transfer percentage for Cases 3 and 6}
-\vspace{2mm}
-{\tabulinesep=1.2mm
-\begin{tabularx}{\linewidth}{p{0.4\linewidth} XX}
-\hline
- &\textbf{Case 3}&\textbf{Case 6}\\
-\hline
-Furnace [\%] & 89.2 & 88.9\\
-Platen SH (SH2) [\%] & 92.5& 93.4\\
-Final SH (SH3) [\%] & 93.5& 94.0\\
-RH2 [\%] & 47.6& 52.2\\
-SH1 [\%] & 37.2& 40.7\\
-RH1 [\%] & 18.7& 21.5\\
-EC [\%] & 5.4& 6.5\\
-\hline
-\label{tbl_rad_conv}
-\end{tabularx}}
-\vspace{-10mm}
-\end{table}
-\newpage
 Table \ref{tbl_rad_conv} shows the radiative heat percentage of the total heat input into each heat-exchanger for Cases 3 and 6.
@@
 This will reduce the total amount of flue-gas flowing through the boiler, thereby reducing the convective heat transfer.
-\newpage
 
@@
 Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, Case 3 is considered to be the best operational strategy at this low load for the boiler under investigation.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % to you.
-
+\newpage
 \bibliography{PAPER1_LOW_LOAD}
 
+\newpage
+
+\section{List of tables}
+
+Table 1: Scalar field equation descriptions\\
+
+Table 2: Utility boiler fuel characteristics\\
+
+Table 3: Case 1 to 6 model inputs on a per burner basis\\
+
+Table 4: Furnace exit conditions and SH wall temperatures\\
+
+Table 5: Process model control parameters\\
+
+Table 6: Radiative heat transfer percentage for Cases 3 and 6
+\newpage
+
+\section{List of figures}
+
+\begin{enumerate}[label=\arabic*]
+\item Figure 1: Boiler geometry and layout \label{fig_geometry}\\
+
+\item Figure 2: Burner layout and mesh details \label{fig_burner_mesh}\\
+
+\item Figure 3: Process model of boiler set-up including the downstream convective components using Flownex SE\textsuperscript{\textregistered} 2021 \label{fig_flownex}\\
+
+\item Figure 4: Heat-exchanger component model \label{fig_heat_exchanger_model}\\
+
+\item Figure 5: Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH \label{fig_heat_valid}\\
+\item Figure 6: Measured and predicted $CO_{PPM}$ (a) and $X_{O_{2}}$ (b) concentrations \label{fig_probe_valid}\\
+\item Figure 7: Temperature fields for Cases 1 through 6 [(a)-(f)] \label{fig_cfd_temp}\\
+\item Figure 8: Velocity fields for Cases 1 through 6 [(a)-(f)] \label{fig_cfd_velo}\\
+\item Figure 9: Heat fluxes profiles for Cases 1 through 6 [(a)-(f)] \label{fig_cfd_heat_flux}\\
+\item Figure 10: CO molar fraction ($X_{CO}$) concentrations for Cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K] \label{fig_cfd_coppm}\\
+\item Figure 11: $CO_{PPM}$ [(a) and (b)] and $X_{O_{2}}$ [(c) and (d)] line plots on symmetry and offset vertical probe lines \label{fig_cfd_probe}
+\end{enumerate}
+
+\newpage
+
+\begin{table}[h!]
+\centering
+\caption{Scalar field equation descriptions}\label{tab_scalars}  
+\vspace{2mm}     
+\begin{tabularx}{\textwidth}{p{0.2\textwidth} p{0.4\textwidth} l}
+\hline
+Variable &Description& Transport equation \\
+\hline
+$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
+$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
+$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
+$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
+$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
+$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
+\hline
+\end{tabularx}
+\end{table}
+
+\newpage
+\begin{table*}[h!]
+\centering
+\caption{Utility boiler fuel characteristics}
+\vspace{2mm}
+\label{tbl_fuel}
+\begin{tabularx}{\textwidth}{p{0.3\textwidth} p{0.4\textwidth} l}
+\hline
+\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
+\hline
+\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
+Carbon & $0.7753$ & $kg/kg_{fuel}$\\
+Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
+Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
+Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
+Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
+\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
+Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
+Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
+Ash & $0.4090$ & $kg/kg_{fuel}$\\
+Moisture & $0.0550$ & $kg/kg_{fuel}$\\
+\hline
+\textbf{Energy content - (DAF)} & \textbf{Value} &\\
+\hline
+Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
+\hline
+\vspace{0pt}
+\end{tabularx}
+\vspace{-10mm}
+\end{table*}
+
+\newpage
+\begin{table}[h!]
+\centering
+\caption{Case 1 to 6 model inputs on a per burner basis.}
+\label{tbl_case_inputs}
+\vspace{2mm}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\textwidth}{p{0.3\textwidth} p{0.4\textwidth} l}
+\hline
+Active burners & \textbf{Cases 1 - 3} & \textbf{Cases 4 - 6}\\
+\hline
+\textbf{Fuel flowrate} [$kg/s$]&3.14  &3.14\\
+\textbf{PA flowrate} [$kg/s$]&4.95  &4.95\\
+\textbf{SA flowrate} [$kg/s$]&14.85  &14.85\\
+\hline
+Non firing burners &  & \\
+\hline
+\textbf{SA flowrate} [$kg/s$]&5.0  &2.5\\
+\hline
+Input air temperatures& &\\
+\hline
+\textbf{PA} [$K$]&373  &373\\
+\textbf{SA} [$K$]&520  &510\\
+\hline
+\textbf{Excess air coefficients} & 1.37 & 1.32\\
+\hline
+\end{tabularx}}
+\end{table}
+
+\newpage
+
+\begin{table}[h!]
+\centering
+\caption{Furnace exit conditions and SH wall temperatures}
+\vspace{2mm}
+\begin{tabularx}{\textwidth}{p{0.3\textwidth} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\multicolumn{7}{l}{\textit{Furnace exit}}\\
+\textbf{Exit temperature} [$K$] & 1168 & 1230 & 1215 & 1208 & 1306 & 1298\\
+\textbf{Unburnt carbon} [$(\times 10^{-3})\,\%$] & 1.83 & 1.94 & 1.54 & 1.81 & 1.89 & 1.62\\
+\multicolumn{7}{l}{\textit{Platen SH}}\\
+\textbf{Max wall temperature} [$^{\circ}C$]  &477 & 492 & 481  & 480 & 493 & 490\\
+\textbf{Mean wall temperature} [$^{\circ}C$] &439 & 453 & 446 & 454 & 442 & 451\\
+\multicolumn{7}{l}{\textit{Final SH}}\\
+\textbf{Max wall temperature} [$^{\circ}C$]  & 602 & 624 & 608 & 595 & 626 & 612\\
+\textbf{Mean wall temperature} [$^{\circ}C$] & 520 & 523 & 517 & 512 & 520 & 511\\
+\hline
+\label{tbl_cfd_results}
+\end{tabularx}
+\vspace{-10mm}
+\end{table}
+
+\newpage
+\begin{table}[h!]
+\centering
+\caption{Process model control parameters}
+\vspace{2mm}
+\begin{tabularx}{\textwidth}{p{0.3\textwidth} XXXXXX}
+\hline
+&\multicolumn{6}{c}{Cases}\\
+ & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
+\hline
+\textbf{Main steam flowrate} 	[$kg/s$]		&175.8&172.9&180.5&180.2&179.1&184.1 \\
+\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535& 535 &535&535 &535& 535\\
+\textbf{RH steam flow rate} 	[$kg/s$]		&158.2&155.6&162.5&162.2&161.2&165.6\\
+\textbf{RH steam exit temp} 	[$^{\circ}C$]	&524&527&531&512&510&520\\
+\textbf{Boiler efficiency} 		[$\%$]			&85.3&84.1&87.9	&87.2&85.9&89.1\\
+\textbf{ATT1} 		[$kg/s$]					&10.4&16.9&13.9&7.9&5.5&10.9\\
+\textbf{ATT2} 		[$kg/s$]					&1.7&3.8&4.2&3.8&3.6&4.2\\
+\textbf{ATT-RH} 		[$kg/s$]				&0.0&0.0&0.0&0.0&0.0&0.0\\
+\hline
+\label{tbl_process_parameters}
+\end{tabularx}
+\vspace{-10mm}
+\end{table}
+
+\newpage
+
+\begin{table}[h!]
+\centering
+\caption{Radiative heat transfer percentage for Cases 3 and 6}
+\vspace{2mm}
+{\tabulinesep=1.2mm
+\begin{tabularx}{\linewidth}{p{0.4\linewidth} XX}
+\hline
+ &\textbf{Case 3}&\textbf{Case 6}\\
+\hline
+Furnace [\%] & 89.2 & 88.9\\
+Platen SH (SH2) [\%] & 92.5& 93.4\\
+Final SH (SH3) [\%] & 93.5& 94.0\\
+RH2 [\%] & 47.6& 52.2\\
+SH1 [\%] & 37.2& 40.7\\
+RH1 [\%] & 18.7& 21.5\\
+EC [\%] & 5.4& 6.5\\
+\hline
+\label{tbl_rad_conv}
+\end{tabularx}}
+\vspace{-10mm}
+\end{table}
+
 \end{document}
